### 2018-06-05 paper_prd.tex
init

%-----------------------------------------------------------------------
%
% filename = nube.tex
%
% First version: February 2012
% Last revision: April 2012
%
%-----------------------------------------------------------------------

\documentclass[twocolumn,aps,showpacs,showkeys,prd,superscriptaddress,byrevtex, amsmath]{revtex4-1}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   LOAD PACKAGES   %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{color}
\usepackage{graphicx,subfigure}
\usepackage{units}
\usepackage{slashbox}
\usepackage{aas_macros}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   BEGIN DOCUMENT  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%
%%%   MACROS   %%%
%%%%%%%%%%%%%%%%%%

\renewcommand{\t}{\times}
\newcommand{\sg}[1]{\textcolor{blue}{SG: #1}}

\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

%%%%%%%%%%%%%%%%%
%%%   TITLE   %%%
%%%%%%%%%%%%%%%%%

\title{Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum}

\author{Sergio Gimeno-Soler}
\affiliation{Departamento de
  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}

\author{Jos\'e A. Font}
\affiliation{Departamento de
  Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
\affiliation{Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico 
  Jos\'e Beltr\'an 2, 46980, Paterna (Val\`encia), Spain}

\author{Carlos Herdeiro}
\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
3810-183 Aveiro, Portugal}

\author{Eugen Radu}
\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
3810-183 Aveiro, Portugal}

%%%%%%%%%%%%%%%%
%%%   DATE   %%%
%%%%%%%%%%%%%%%%

\date{\today}

%%%%%%%%%%%%%%%%%%%%
%%%   ABSTRACT   %%%
%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).
\end{abstract}

%%%%%%%%%%%%%%%%
%%%   PACS   %%%
%%%%%%%%%%%%%%%%

\pacs{
95.30.Sf, % relativity and gravitation
04.70.Bw, 
04.40.Nr, 
04.25.dg
}

%%%%%%%%%%%%%%%%%%%%%%
%%%   MAKE TITLE   %%%
%%%%%%%%%%%%%%%%%%%%%%

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%
%%%   INTRODUCTION   %%%
%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{}

\section{Framework}

%%%%%%%%%%%%%%%%%%%%%
%%%   RESULTS   %%%
%%%%%%%%%%%%%%%%%%%%%

We use the stationary and axisymmetric metric ansatz provided by\cite{Herdeiro:2014a}

\begin{equation}
\begin{split}
\mathrm{d}s^2 = e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) + \\ e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 -  e^{2F_0}N\mathrm{d}t^2,
\end{split}
\end{equation}

with $N = 1 - r_H/r$, where $r_H$ is the radius of the event horizon of the BH and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.

This metric is a solution to the Einstein-Klein-Gordon field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi G (T_{\mathrm{SF}})_{ab}$ with

\begin{equation}\label{eq:e-m_scalaf_field}
\begin{split}
(T_{\mathrm{SF}})_{ab} = \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi \\ - g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
\end{split}
\end{equation}

where $\Psi$ is a complex Klein-Gordon field such as $\Psi = \phi(r, \theta) e^\mathrm{i}{m\phi - w t}$ where $w$ is the scalar field frequency and $m$ is the azimuthal harmonic index. Details about the obtention of the solution and the behaviour of the metric functions ${W, F_i}$ are presented in~\cite{Herdeiro:2015b}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig1_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_I_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_I__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig1_II_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_II_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_II__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig1_III_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_III_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_III__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig1_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig1_IV_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig1_IV__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution. From top to bottom the rows correspond to the different models for the KBHsSH (I, II, III and IV). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_I}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig2_V_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig2_V_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig2_V__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig2_VI_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig2_VI_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig2_VI__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig2_VII_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig2_VII_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig2_VII__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution. From top to bottom the rows correspond to the different models for the KBHsSH (V, VI and VII). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_II}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution using perimeteral coordinates. From top to bottom the rows correspond to the different models for the KBHsSH (I, II, III and IV). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_peri_I}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution using perimeteral coordinates. From top to bottom the rows correspond to the different models for the KBHsSH (V, VI, VII). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_peri_II}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
\hspace{-0.2cm}
\caption{Gravitational mass density ($-T^t_t+T^i_i$) distribution for the torus (up) and the scalar field (down). From left to right the columns correspond to different models (I, IV and VII). From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{comparison_mass_density}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
\hspace{-0.2cm}
\\
\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
\hspace{-0.4cm}
\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
\hspace{-0.2cm}
\caption{Gravitational mass density ($-T^t_t+T^i_i$) distribution for the torus (up) and the scalar field (down) using perimeteral coordinates. From left to right the columns correspond to different models (I, IV and VII). From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{comparison_mass_density_peri}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
\hspace{-0.cm}
\\
\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
\hspace{-0.cm}
\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
\hspace{-0.cm}
\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc. In the first row, we show this for all of our KBHsSH models. In the second row, we show this for a sequence of KBHs with increasing spin parameter.}
\label{comparison_HBH_Kerr_dens_enth}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.2]{figures/fig8_HBH.eps}
\hspace{0.5cm}
\includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
\hspace{0.5cm}
\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$). Left panel: KBHsSH models. Right panel: A sequence of KBHs with increasing spin parameter.}
\label{comparison_HBH_Kerr_r_m_max}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution. From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_Kerr}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
\\
\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
\hspace{-0.2cm}
\caption{Rest-mass density distribution using perimeteral coordinates. From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999). From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
\label{models_Kerr_peri}
\end{figure*}

\subsection{Distribution of angular momentum and equations of motion}

We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
\begin{equation}
l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
\end{equation}
where $u^{\mu}$ is the fluid four-velocity.
The relationship between $l$ and $\Omega$ is given by the equations
\begin{equation}
l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
\end{equation}
where we are assuming circular motion, i.e. the four-velocity can be written as
\begin{equation}
u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
\end{equation}

We consider a constant angular momentum distribution $l(r,\theta) = \mathrm{cte}.$. The specific value of the angular momentum is computed as the minimum of the following equation
\begin{equation}\label{eq:mb_ang_mom}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{t\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
\end{equation}
where the plus sign is for prograde orbits and the minus is for retrograde orbits.
This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary, axisymmetric spacetimes. For prograde motion, the function has a minimum outside the event horizon. The location of said minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement at appendix~\ref{ang_mom_appendix}. This choice of angular momentum distribution is motivated by its simplicity (for a first study of thick tori around KBHsSH) and for allowing the presence of a cusp (to allow matter accretion onto the black hole) and a centre.

\subsection{Magnetized disks}
We use the procedure described by~\cite{Montero:2007}, where we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetised perfect fluid, $h$, $\rho$ $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Then, we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.

\begin{equation}\label{eq:l}
\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}.
\end{equation}
To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
\begin{equation}\label{eq:eos_fluid}
p = K \rho^{\Gamma},
\end{equation}
with $K$ and $\Gamma$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogous equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = M \tilde{w}^q,
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = M \mathcal{L}^{q-1} w^q,
\end{equation}
where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
If we define the potential as $W \equiv \ln |u_t|$, then we can integrate the equation~\eqref{eq:diff_ver} as
\begin{equation}\label{eq:final}
W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}w)^{q-1}=0,
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.

We also write the expressions of the total energy density for the torus $\rho_{\mathrm{T}}$:

\begin{equation}\label{eq:torus_energy_density}
\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
\end{equation}

and the total energy density for the scalar field $\rho_{\mathrm{SF}}$:

\begin{equation}\label{eq:SF_energy_density}
\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
\end{equation}

%--------------------------------------------------------------------
\section{Method}

\subsection{Building the disk}

To construct our models we take the following steps:
First, we find the angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the value at the minimum and the location of said minimum outside the event horizon of equation~\eqref{eq:mb_ang_mom}. This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$ and $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$.

In this work, we use $q = \Gamma = 4/3$, the density at the disk centre $\rho_{\mathrm{c}} = 1$ and the angular momentum distribution gives us $W_{\mathrm{in}} = W_{\mathrm{cusp}} = 0$. With this information we can compute all the relevant physical quantities.

\subsection{Numerical method}

%--------------------------------------------------------------------
\section{Results}

As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry. Nevertheless, we show them for the sake of clarity. Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extrating information about the morphology of the disks from the 2-dimensional plots. This idea is discussed in appendix\ref{torus_embedding}.

\begin{table}
\caption{List of models of KBHsSH.}        
\label{models_list}      
\centering          
\begin{tabular}{c c c c  c c c c}
\hline\hline       
 Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
\hline           
I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
 \hline 
II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
 \hline 
III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
 \hline 
IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
 \hline 
V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
 \hline 
VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
 \hline 
VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
\hline      
\end{tabular}
\end{table}

\begin{table}
\caption{Disk parameters and values of their relevant physical magnitudes. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
\label{HBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c  c c c c c c c}
\hline\hline       
 Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
 \hline 
II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
 \hline 
III & $1.06$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
\hline  
IV & $1.16$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
\hline   
V & $1.20$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
\hline 
 &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
\hline   
VI & $1.20$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
\hline 
VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
\hline 
 &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
\hline 
\end{tabular}
\end{table}

\begin{table}
\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
\label{HBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c  c c c c c c c}
\hline\hline       
 $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
 \hline 
 $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
\hline  
$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
 \hline 
 &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
 \hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
 \hline 
$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
\hline 
 &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
\hline 
 &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
\hline   
\end{tabular}
\end{table}

\begin{table}
\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}        
\label{models_spin_vel}      
\centering          
\begin{tabular}{c c c c c}
\hline\hline       
 Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
\hline           
I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
 \hline 
II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
 \hline 
III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
 \hline 
IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
 \hline 
V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
 \hline 
VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
 \hline 
VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
\hline      
\end{tabular}
\end{table}

\begin{figure}
\hspace{-0.3cm}
\includegraphics[scale=0.57]{figures/existence.eps}
\hspace{-0.2cm}
\caption{Location of the models in the domain of existence of KBHsSH solutions. \textbf{update names.}}
\label{existance}
\end{figure}

%--------------------------------------------------------------------
\section{Conclusions}

\begin{acknowledgements}

\end{acknowledgements}

\bibliographystyle{apsrev4-1}
\bibliography{references.bib}

\begin{appendix}
\section{Embedding of the accretion torus in $\mathbb{E}^3$}\label{torus_embedding}
Following the same reasoning as in~\cite{Delgado:2018}, we write the 2-metric for the surface of a torus as 
\begin{equation}\label{eq:torus_prev_metric}
\mathrm{d}\sigma^2 = \frac{e^{2 F_1}}{N}\mathrm{d}r^2+ e^{2 F_1}r^2\mathrm{d}\theta^2+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
\end{equation}
and the condition $r = r(\theta)$ for the surface of the torus. The location of the surface of the torus $r(\theta)$ can be obtained integrating $r' = \frac{\mathrm{d}r}{\mathrm{d}\theta} = -\frac{\partial_{\theta}W}{\partial_{r}W}$ (equation (24) of~\citep{Gimeno-Soler:2017}). Using this, we can write equation~\eqref{eq:torus_prev_metric} as
\begin{equation}\label{eq:torus_metric}
\mathrm{d}\sigma^2 = e^{2 F_1} \mathrm{d}\theta^2\left(\frac{r'^2}{N} +r^2\right)+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
\end{equation}
with the prime $'$ denoting partial differentiation with respect to $\theta$. Then, we try the embedding in $\mathbb{E}^3$ with the Cartesian metric $\mathrm{d}\sigma^2 = \mathrm{d}X^2 + \mathrm{d}Y^2 + \mathrm{d}Z^2$ and the embedding functions:
\begin{equation}
X + \mathrm{i}Y = f(\theta)e^{\mathrm{i}\phi},  \;\;\; Z = g(\theta),
\end{equation}
then
\begin{equation}
f = e^{2 F_2} r^2 \sin^2\theta, \;\;\; f'^2 + g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right),
\end{equation}
so we can write $g'^2$ as
\begin{equation}\label{eq:embedding_existance}
g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right) - e^{2 F_2} (F_2'r \sin \theta + r' \sin \theta + r \cos \theta)^2.
\end{equation}
This result tells us that the r.h.s. of~\eqref{eq:embedding_existance} must be $\geq 0$ in order to the embedding function to exist.
This gives us the following results for the seven different cases of KBHsSH we have:

\section{KBHsSH vs $h = 1$ approximation}\label{komissarov_appendix}

In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \cite{Montero:2007} and \cite{Komissarov:2006}. The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III. This is due to the $h = 1$ approximation breaking down. In the table~\ref{table:pot} we show the correlation between the value of the potential at the centre and the specific enthalpy at the centre. It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$. This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\cite{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).

% \begin{figure*}
% \centering
% \includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig2_III_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig2_III_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig2_III_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Rest-mass density distribution for the model I. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_mag_1}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig3_IV_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig3_IV_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig3_IV_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Rest-mass density distribution for the model II. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_mag_2}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig4_V_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig4_V_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.2]{figures/fig4_V_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Rest-mass density distribution for the model III. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_mag_3}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_III_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_III_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_III_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Radial rest-mass density distribution for the model I at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_radial_1}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_IV_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_IV_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_IV_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Radial rest-mass density distribution for the model II at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_radial_2}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_V_K_3.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_V_K_0.pdf}
% \hspace{-0.2cm}
% \\
% \includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
% \hspace{-0.3cm}
% \includegraphics[scale=0.3]{figures/radial_V_K__3.pdf}
% \hspace{-0.2cm}
% \caption{Radial rest-mass density distribution for the model III at the equatorial plane. From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$). The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
% \label{comparison_alt_radial_3}
% \end{figure*}

\section{Finding $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$}\label{ang_mom_appendix}
Proof.
\end{appendix}

\end{document}

### 2018-06-07 paper_prd.tex
draft updated

@@
 
-\section{}
-
 \section{Framework}
-
-%%%%%%%%%%%%%%%%%%%%%
-%%%   RESULTS   %%%
-%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-where $\Psi$ is a complex Klein-Gordon field such as $\Psi = \phi(r, \theta) e^\mathrm{i}{m\phi - w t}$ where $w$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
+where $\Psi$ is a complex Klein-Gordon field such as $\Psi = \phi(r, \theta) e^{\mathrm{i}m\phi - w t}$ where $w$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
 Details about the obtention of the solution and the behaviour of the metric functions ${W, F_i}$ are presented in~\cite{Herdeiro:2015b}
@@
 \hspace{-0.2cm}
-\caption{Gravitational mass density ($-T^t_t+T^i_i$) distribution for the torus (up) and the scalar field (down).
+\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down).
 From left to right the columns correspond to different models (I, IV and VII).
@@
 \hspace{-0.2cm}
-\caption{Gravitational mass density ($-T^t_t+T^i_i$) distribution for the torus (up) and the scalar field (down) using perimeteral coordinates.
+\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down) using perimeteral coordinates.
 From left to right the columns correspond to different models (I, IV and VII).
@@
 \subsection{Distribution of angular momentum and equations of motion}
-
 We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
@@
 
-\begin{equation}\label{eq:l}
-\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}.
-\end{equation}
 To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
@@
 with $K$ and $\Gamma$ constants.
-Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogous equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
+Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogous equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$
 \begin{equation}\label{eq:eos_mag_tilde}
@@
 We also write the expressions of the total energy density for the torus $\rho_{\mathrm{T}}$:
-
 \begin{equation}\label{eq:torus_energy_density}
@@
 \end{equation}
-
 and the total energy density for the scalar field $\rho_{\mathrm{SF}}$:
-
 \begin{equation}\label{eq:SF_energy_density}
@@
 \end{equation}
+
+In this work, we set the mass of the scalar field $\mu = 1$, the angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EoS to $q = \Gamma = 4/3$, and the density at the disk centre $\rho_{\mathrm{c}} = 1$.
+Then, we leave the magnetization at the center $\beta_{\mathrm{m_c}}$ as a parameter (for each model of KBHSH).
+With this information we can compute all the relevant physical quantities.
 
@@
 First, we find the angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the value at the minimum and the location of said minimum outside the event horizon of equation~\eqref{eq:mb_ang_mom}.
-This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$ and $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$.
-
-In this work, we use $q = \Gamma = 4/3$, the density at the disk centre $\rho_{\mathrm{c}} = 1$ and the angular momentum distribution gives us $W_{\mathrm{in}} = W_{\mathrm{cusp}} = 0$.
-With this information we can compute all the relevant physical quantities.
+This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$ and $W_{\mathrm{in}} = 0$ and then, we can compute the potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
+Considering this, and that we can write the magnetic pressure at the center as
+\begin{equation}
+p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = K/\beta_{\mathrm{m_c}},
+\end{equation}
+where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}$.
+Replacing this into the equation~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
+\begin{equation}\label{eq:K_eq}
+W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
+\end{equation}
+Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}$.
+With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
 
 \subsection{Numerical method}
+We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
+Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
 
@@
 \section{Results}
+In table~\ref{models_list} we show the different KBHsSH models we will use.
+As it can be seen, the models go from a Kerr-like model (almost all the mass and angular momentum are stored in BH) to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
+It is also worth mentioning that, as shown in table~\ref{models_spin_vel} some of the models violate the Kerr bound (in terms of ADM or horizon quantities).
+This is not worrying because, as shown in~\cite{Herdeiro:2015c} the horizon linear velocity $v_{\mathrm{H}}$ never exceed $1$.
+For comparison, we also show the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with horizon linear velocity $v_{\mathrm{H}}$.
+
+In figures~\ref{models_I} and~\ref{models_II} we show the rest-mass density distribution for all our KBHsSH models with 3 different values of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, namely $10^{10}$, $1$ and $10^{-10}$.
+In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimeteral radial coordinate such as $R = e^{F_2} r$.
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+Tables~\ref{HBH_disk_parameters} and~\ref{KBH_disk_parameters} show the relevant physical quantities for both KBHSH and the same KBH cases we presented in the figures.
+First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
+As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1.
+This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$.
+The models V, VI and VII violate that bound.
+This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
+
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (superior half) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for 3 of the models (I, IV and VII) and 2 values of the magnetization parameter at the center ($10^{10}$ and $10^{-10}$).
+In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
+The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+
+The behaviour of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ is shown in figures~\ref{comparison_HBH_Kerr_dens_enth} for the models (I-VII) and for a sequence of increasing spin parameter KBHs, here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
+However, there are differences between the two cases.
+For the enthalpy, the values of $h_{\mathrm{max}}$ reached for the KBHsSH are much higher than those of the KBH case.
+This fact tells us that, while the $w = \rho h \simeq \rho$ approximation (see \cite{Komissarov:2006} and \cite{Gimeno-Soler:2017}) is valid for magnetized flows ($\beta_{\mathrm{m_c}} \sim 1$) for reasonable values of the spin parameter ($a \sim 0.99$ or lower), that is not the case for KBHsSH.
+Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
+
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
+As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.
+
+\sg{Include discussion about radial profiles.}
 
@@
 Nevertheless, we show them for the sake of clarity.
-Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extrating information about the morphology of the disks from the 2-dimensional plots.
-This idea is discussed in appendix\ref{torus_embedding}.
+Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
+This idea is discussed in appendix~\ref{torus_embedding}.
 
@@
 \begin{table}
+\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
+\label{models_spin_vel}      
+\centering          
+\begin{tabular}{c c c c c}
+\hline\hline       
+ Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
+\hline           
+I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
+ \hline 
+II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
+ \hline 
+III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+ \hline 
+IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+ \hline 
+V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+ \hline 
+VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+ \hline 
+VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
+\hline      
+\end{tabular}
+\end{table}
+
+\begin{table*}[t]
 \caption{Disk parameters and values of their relevant physical magnitudes. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table}
-\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
-\label{HBH_disk_parameters}      
+\begin{table*}[t]
+\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
+For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
+\label{KBH_disk_parameters}      
 \centering          
@@
 \end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-\label{models_spin_vel}      
-\centering          
-\begin{tabular}{c c c c c}
-\hline\hline       
- Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-\hline           
-I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
- \hline 
-II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
- \hline 
-III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
- \hline 
-IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
- \hline 
-V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
- \hline 
-VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
- \hline 
-VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-\hline      
-\end{tabular}
-\end{table}
-
-\begin{figure}
-\hspace{-0.3cm}
-\includegraphics[scale=0.57]{figures/existence.eps}
-\hspace{-0.2cm}
-\caption{Location of the models in the domain of existence of KBHsSH solutions. \textbf{update names.}}
-\label{existance}
-\end{figure}
+\end{table*}
 
@@
 \section{Conclusions}
+Future work: Non-constant angular momentum case, Proca hair, shadows of the system HBH+disk.
 
@@
 This result tells us that the r.h.s. of~\eqref{eq:embedding_existance} must be $\geq 0$ in order to the embedding function to exist.
-This gives us the following results for the seven different cases of KBHsSH we have:
 
-\section{KBHsSH vs $h = 1$ approximation}\label{komissarov_appendix}
-
-In the figures \ref{comparison_alt_mag_1}, \ref{comparison_alt_mag_2}, \ref{comparison_alt_mag_3}, \ref{comparison_alt_radial_1}, \ref{comparison_alt_radial_2}, \ref{comparison_alt_radial_3} we show the comparison between the results for KBHsSH using \cite{Montero:2007} and \cite{Komissarov:2006}.
-The figures show good agreement for the highly magnetized case ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$) but not quite for the non-magnetized and mildly magnetized cases, especially for the model III.
-This is due to the $h = 1$ approximation breaking down.
-In the table~\ref{table:pot} we show the correlation between the value of the potential at the centre and the specific enthalpy at the centre.
-It is easy to note that for higher absolute values of $W_{\mathrm{c}}$ we get values of $h_{\mathrm{c}}$ further away from the case $h = 1$.
-This is interesting because these high values of $W_{\mathrm{c}}$ (particularly the one for the model III) is unattaniable for any KBH (as is shown by~\cite{Abramowicz:1978}, the maximum value of $W_{\mathrm{c}}$ for a KBH is $W_{\mathrm{c}} = 0.549$).
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/fig2_III_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig2_III_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig2_III_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig2_III_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig2_III_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig2_III_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Rest-mass density distribution for the model I.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_mag_1}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/fig3_IV_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig3_IV_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig3_IV_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig3_IV_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig3_IV_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig3_IV_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Rest-mass density distribution for the model II.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_mag_2}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/fig4_V_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig4_V_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig4_V_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig4_V_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig4_V_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.2]{figures/fig4_V_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Rest-mass density distribution for the model III.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_mag_3}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.3]{figures/radial_III_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_III_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_III_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_III_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_III_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_III_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Radial rest-mass density distribution for the model I at the equatorial plane.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_radial_1}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.3]{figures/radial_IV_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_IV_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_IV_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_IV_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_IV_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_IV_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Radial rest-mass density distribution for the model II at the equatorial plane.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_radial_2}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.3]{figures/radial_V_HBH_3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_V_K_3.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_V_HBH_0.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_V_K_0.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.3]{figures/radial_V_HBH__3.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.3]{figures/radial_V_K__3.pdf}
-% \hspace{-0.2cm}
-% \caption{Radial rest-mass density distribution for the model III at the equatorial plane.
-From top to bottom the rows correspond to the different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$).
-The left column correspond to the KBHsSH model using~\cite{Montero:2007} and the right column correspond to the~\cite{Komissarov:2006} approximation.}
-% \label{comparison_alt_radial_3}
-% \end{figure*}
+\begin{figure*}
+\centering
+\includegraphics[scale=0.2]{figures/embedding.pdf}
+\hspace{0.5cm}
+\caption{Rest-mass density distribution for model VII with $r_{\mathrm{in}} = 0.08$ and $\beta_{\mathrm{m_c}} = 10^{10}$ (up) and the scalar field amplitude distribution $\phi$ (down).
+The isocontours are blue when the r.h.s.
+of equation~\eqref{eq:embedding_existance} is $\geq 0$ and red when is $\leq 0$.}
+\label{embedding_VII}
+\end{figure*}
 
 \section{Finding $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$}\label{ang_mom_appendix}
-Proof.
+\sg{To do.}
 \end{appendix}

### 2018-06-07 paper_prd.tex
typo corrected

@@
 \begin{equation}\label{eq:mb_ang_mom}
-l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{t\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
+l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
 \end{equation}

### 2018-06-25 paper_prd.tex
style files and typos

@@
 \begin{equation}\label{eq:final}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}w)^{q-1}=0,
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}w)^{q-1}=0,
 \end{equation}
@@
 \end{equation}
-where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}$.
+where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
 Replacing this into the equation~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
@@
 \end{equation}
-Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\gamma -1}$.
+Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
 With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
@@
 The isocontours are blue when the r.h.s.
-of equation~\eqref{eq:embedding_existance} is $\geq 0$ and red when is $\leq 0$.}
+of equation~\eqref{eq:embedding_existance} is $> 0$ and red when is $\leq 0$.}
 \label{embedding_VII}

### 2018-06-27 paper_prd.tex
Work on the introduction. New references added in the .bib file.

@@
 
+%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%
+
+In recent years, new families of stationary, asymptotically flat black holes (BHs) in general relativity, avoiding the so-called ``no hair" theorems, have been obtained.
+In particular, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counter example to the no hair conjecture, in general relativity minimally coupled to simple (bosonic) matter fields obeying all energy conditions.
+The physical conditions and stability properties of these {\it hairy} BHs  (HBHs) have been investigated to assess their potential viability as valid alternatives to astrophysical Kerr BHs.
+On the one hand, HBHs have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017}.
+Moreover, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, for the largest timescale possible (the age of the Universe), rendering hairy BHs as {\it effectively} stable.
+
+In addition, the detection of gravitational waves from binary BHs~\cite{} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
+Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.
+Thick accretion disks (or tori) are common in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts.
+Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks.
+Our procedure, which combines earlier approaches
+by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
+In~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+Our immediate goal in the present work is to assess if and how the accretion disk morphology depends on the type of BH considered, either Kerr BHs of varying spins or Kerr BHs with scalar hair (KBHsSH).
+Moreover, we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case.
+In subsequent investigations, we will analyze the shadows of the equilibrium models of KBHsSH presented in this work as well as in {\it dynamical} situations.
+
+The organization of this paper is as follows:
+
+%HERE
 

### 2018-06-27 paper_prd.tex
Further changes.

@@
 
-In addition, the detection of gravitational waves from binary BHs~\cite{} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
+In addition, the detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
 Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.

### 2018-06-28 paper_prd.tex
Some more work on the paper.

@@
   Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
-  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
+  C/ Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
 
@@
   Astronom\'{\i}a y Astrof\'{\i}sica, Universitat de Val\`encia,
-  Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
+  C/ Dr. Moliner 50, 46100, Burjassot (Val\`encia), Spain}
 \affiliation{Observatori Astron\`omic, Universitat de Val\`encia, C/ Catedr\'atico 
@@
 
-The organization of this paper is as follows:
+The organization of this paper is as follows: Section~\ref{framework} presents  the  analytic  mathematical framework to build non-self-gravitating magnetized discs in the spacetime of KBHsSH.
+Section~\ref{procedure} discusses the corresponding numerical methodology.
+The sequences of equilibrium models are presented and  discussed in Section~\ref{results}.
+Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
 
@@
 
+%%%%%%%%%%%
 \section{Framework}
+\label{framework}
+%%%%%%%%%%%
 
-We use the stationary and axisymmetric metric ansatz provided by\cite{Herdeiro:2014a}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spacetime metric and KBHsSH models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{equation}
-\begin{split}
-\mathrm{d}s^2 = e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) + \\ e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 -  e^{2F_0}N\mathrm{d}t^2,
-\end{split}
-\end{equation}
+The KBHsSH models we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
+The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity.
+KBHsSH solutions are obtained by using the following ansatz for the metric and the scalar field~\cite{Herdeiro:2014a}
+\begin{eqnarray}
+%\begin{split}
+\mathrm{d}s^2 &=& e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) +  e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 
+\nonumber \\ 
+&-&  e^{2F_0}N\mathrm{d}t^2\,,
+\\
+%\end{eqnarray}
+%\begin{eqnarray}
+\Psi &=& \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
+%\end{split}
+\end{eqnarray}
+with $N = 1 - r_H/r$, where $r_H$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
+Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
 
-with $N = 1 - r_H/r$, where $r_H$ is the radius of the event horizon of the BH and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
+The stationary and axisymmetric metric ansatz is a solution to the EKG field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi G (T_{\mathrm{SF}})_{ab}$ with 
+\begin{eqnarray}\label{eq:e-m_scalaf_field}
+(T_{\mathrm{SF}})_{ab} &=& \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi 
+\nonumber \\ 
+&-& g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
+\end{eqnarray}
+where $\mu$ is the mass of the scalar field and $^*$ denotes complex conjugation.
+The interested reader is addressed to~\cite{Herdeiro:2015b} for details on the equations of motion for the scalar field $\Psi$ and the four metric functions ${W, F_i}$, along with their solution.
 
-This metric is a solution to the Einstein-Klein-Gordon field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi G (T_{\mathrm{SF}})_{ab}$ with
+Table~\ref{models_list} lists the seven KBHsSH models we use in this work.
+As it can be seen, the models go from a Kerr-like model (almost all the mass and angular momentum are stored in BH) to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
+It is also worth mentioning that, as shown in table~\ref{models_spin_vel} some of the models violate the Kerr bound (in terms of ADM or horizon quantities).
+This is not worrying because, as shown in~\cite{Herdeiro:2015c} the horizon linear velocity $v_{\mathrm{H}}$ never exceed $1$.
+For comparison, we also show the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with horizon linear velocity $v_{\mathrm{H}}$.
 
-\begin{equation}\label{eq:e-m_scalaf_field}
-\begin{split}
-(T_{\mathrm{SF}})_{ab} = \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi \\ - g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
-\end{split}
-\end{equation}
+%%%%%%%%%%%%%%%%%%%
+\begin{table}
+\caption{List of models of KBHsSH.}        
+\label{models_list}      
+\centering          
+\begin{tabular}{c c c c  c c c c}
+\hline\hline       
+ Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
+\hline           
+I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
+ \hline 
+II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
+ \hline 
+III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
+ \hline 
+IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
+ \hline 
+V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
+ \hline 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
+ \hline 
+VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
+\hline      
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%
 
-where $\Psi$ is a complex Klein-Gordon field such as $\Psi = \phi(r, \theta) e^{\mathrm{i}m\phi - w t}$ where $w$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
-Details about the obtention of the solution and the behaviour of the metric functions ${W, F_i}$ are presented in~\cite{Herdeiro:2015b}
+\begin{table}
+\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
+\label{models_spin_vel}      
+\centering          
+\begin{tabular}{c c c c c}
+\hline\hline       
+ Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
+\hline           
+I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
+ \hline 
+II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
+ \hline 
+III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+ \hline 
+IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+ \hline 
+V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+ \hline 
+VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+ \hline 
+VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
+\hline      
+\end{tabular}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.7]{figures/existence-eps-converted-to.pdf}
+\caption{The figure has to be redone to label the 7 models used in this work.}
+\label{existence}
+\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Distribution of angular momentum and equations of motion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
@@
 
+%%%%%%%%%%%%%%%%
 \subsection{Magnetized disks}
+%%%%%%%%%%%%%%%%
+
 We use the procedure described by~\cite{Montero:2007}, where we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
@@
 
-%--------------------------------------------------------------------
-\section{Method}
+%%%%%%%%%%%%
+\section{Methodology}
+\label{procedure}
+%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%
 \subsection{Building the disk}
+%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%
 \subsection{Numerical method}
+%%%%%%%%%%%%%%%%%
+
 We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
@@
 
-%--------------------------------------------------------------------
+%%%%%%%%%%
 \section{Results}
-In table~\ref{models_list} we show the different KBHsSH models we will use.
+\label{results}
+%%%%%%%%%%
+
+%In table~\ref{models_list} we show the different KBHsSH models we will use.
 As it can be seen, the models go from a Kerr-like model (almost all the mass and angular momentum are stored in BH) to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
@@
 
-\begin{table}
-\caption{List of models of KBHsSH.}        
-\label{models_list}      
-\centering          
-\begin{tabular}{c c c c  c c c c}
-\hline\hline       
- Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
-\hline           
-I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
- \hline 
-II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
- \hline 
-III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
- \hline 
-IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
- \hline 
-V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
- \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
- \hline 
-VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
-\hline      
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-\label{models_spin_vel}      
-\centering          
-\begin{tabular}{c c c c c}
-\hline\hline       
- Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-\hline           
-I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
- \hline 
-II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
- \hline 
-III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
- \hline 
-IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
- \hline 
-V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
- \hline 
-VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
- \hline 
-VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-\hline      
-\end{tabular}
-\end{table}
+%\begin{table}
+%\caption{List of models of KBHsSH.}        
+%\label{models_list}      
+%\centering          
+%\begin{tabular}{c c c c  c c c c}
+%\hline\hline       
+% Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
+%\hline           
+%I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
+% \hline 
+%II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
+% \hline 
+%III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
+% \hline 
+%IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
+% \hline 
+%V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
+% \hline 
+%VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
+% \hline 
+%VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
+%\hline      
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}
+%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
+%\label{models_spin_vel}      
+%\centering          
+%\begin{tabular}{c c c c c}
+%\hline\hline       
+% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
+%\hline           
+%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
+% \hline 
+%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
+% \hline 
+%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+% \hline 
+%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+% \hline 
+%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+% \hline 
+%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+% \hline 
+%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
+%\hline      
+%\end{tabular}
+%\end{table}
 
@@
 
-%--------------------------------------------------------------------
+%%%%%%%%%%%%
 \section{Conclusions}
+\label{conclusions}
+%%%%%%%%%%%%
+
 Future work: Non-constant angular momentum case, Proca hair, shadows of the system HBH+disk.

### 2018-06-28 paper_prd.tex
More work.

@@
 \newcommand{\sg}[1]{\textcolor{blue}{SG: #1}}
+\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
 
@@
 
+%%%%%%%%%%%%%%%%%%%
+\begin{table*}
+\caption{List of models of KBHsSH used in this work.
+From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, and the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$.}
+\label{models_list}      
+\centering          
+\begin{tabular}{c c c c  c c c c   c c c c}
+\hline\hline       
+ Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\
+\hline           
+I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$\\ 
+ \hline 
+II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ \\
+ \hline 
+III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+ \hline 
+IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.100$ & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+ \hline 
+V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+ \hline 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+ \hline 
+VII & $0.975$ & $0.850$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.040$ & $0.8941$ & $6.173$ & $0.0973$ & $0.1928$ \\ 
+\hline      
+\end{tabular}
+\end{table*}
+%%%%%%%%%%%%%%%%%%%
+
 The KBHsSH models we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
@@
 Table~\ref{models_list} lists the seven KBHsSH models we use in this work.
-As it can be seen, the models go from a Kerr-like model (almost all the mass and angular momentum are stored in BH) to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
-It is also worth mentioning that, as shown in table~\ref{models_spin_vel} some of the models violate the Kerr bound (in terms of ADM or horizon quantities).
-This is not worrying because, as shown in~\cite{Herdeiro:2015c} the horizon linear velocity $v_{\mathrm{H}}$ never exceed $1$.
-For comparison, we also show the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with horizon linear velocity $v_{\mathrm{H}}$.
+The models have been selected to span all regions of interest in the parameter space.
+Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
+It is worth mentioning that some of the models violate the Kerr bound (normalized sìn parameter larger than 1) in terms of both ADM or horizon quantities.
+This is not a source of concern because, as shown in~\cite{Herdeiro:2015c} the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
+For comparison, we also show in the last column the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
+\tf{Further description of the table}.
+In addition, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
 
-%%%%%%%%%%%%%%%%%%%
-\begin{table}
-\caption{List of models of KBHsSH.}        
-\label{models_list}      
-\centering          
-\begin{tabular}{c c c c  c c c c}
-\hline\hline       
- Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
-\hline           
-I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
- \hline 
-II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
- \hline 
-III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
- \hline 
-IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
- \hline 
-V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
- \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
- \hline 
-VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
-\hline      
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%
-
-\begin{table}
-\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-\label{models_spin_vel}      
-\centering          
-\begin{tabular}{c c c c c}
-\hline\hline       
- Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-\hline           
-I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
- \hline 
-II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
- \hline 
-III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
- \hline 
-IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
- \hline 
-V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
- \hline 
-VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
- \hline 
-VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-\hline      
-\end{tabular}
-\end{table}
+%\begin{table}
+%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
+%\label{models_spin_vel}      
+%\centering          
+%\begin{tabular}{c c c c c}
+%\hline\hline       
+% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
+%\hline           
+%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
+% \hline 
+%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
+% \hline 
+%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+% \hline 
+%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+% \hline 
+%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+% \hline 
+%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+% \hline 
+%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
+%\hline      
+%\end{tabular}
+%\end{table}
 
@@
 \includegraphics[scale=0.7]{figures/existence-eps-converted-to.pdf}
-\caption{The figure has to be redone to label the 7 models used in this work.}
+\caption{Domain of existence for KBHsSH in an ADM mass versus scalar
+field frequency diagram. \tf{The figure has to be redone to label the 7 models used in this work.}}
 \label{existence}
 \end{figure}
+
+%HERE
 

### 2018-06-28 paper_prd.tex
More

@@
 &-&  e^{2F_0}N\mathrm{d}t^2\,,
-\\
-%\end{eqnarray}
-%\begin{eqnarray}
-\Psi &=& \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
+\label{metric}
+\end{eqnarray}
+\begin{eqnarray}
+\Psi = \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
 %\end{split}
@@
 This is not a source of concern because, as shown in~\cite{Herdeiro:2015c} the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
-For comparison, we also show in the last column the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
-\tf{Further description of the table}.
-In addition, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+For comparison, we also show in the last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
+\tf{Further description of the table.
+Something must be said about the coordinates.}.
+In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
 
@@
 \end{figure}
-
-%HERE
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Distribution of angular momentum and equations of motion}
+\subsection{Distribution of angular momentum in the disk}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We introduce the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
+Equilibrium models of disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric.
+This was the approach followed in~\cite{Gimeno-Soler:2017}.
+For KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
+
+%HERE
+
+We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
 \begin{equation}
@@
 \end{equation}
-where we are assuming circular motion, i.e. the four-velocity can be written as
+where we are assuming circular motion, i.e.~the four-velocity can be written as
 \begin{equation}
@@
 
-We consider a constant angular momentum distribution $l(r,\theta) = \mathrm{cte}.$. The specific value of the angular momentum is computed as the minimum of the following equation
+In this work, for simplicity, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$.
+This is contrary to the approach we followed in~\cite{Gimeno-Soler:2017} where the angular momentum ansatz followed the approach of~\cite{Qian:2009}.
+\tf{We should explain/motivate why we change our approach in this paper.} The specific value of the angular momentum is computed as the minimum of the following equation
 \begin{equation}\label{eq:mb_ang_mom}

### 2018-06-28 paper_prd.tex
Done for today.

@@
 
-In this work, for simplicity, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$.
-This is contrary to the approach we followed in~\cite{Gimeno-Soler:2017} where the angular momentum ansatz followed the approach of~\cite{Qian:2009}.
+In~\cite{Gimeno-Soler:2017} we followed the approach for the angular momentum distribution given by~\cite{Qian:2009}, which is characterized by the parameters, $\beta$, $\gamma$, and $eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}.
+In this work, for simplicity and to reduce the space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in ~\cite{Gimeno-Soler:2017}.
 \tf{We should explain/motivate why we change our approach in this paper.} The specific value of the angular momentum is computed as the minimum of the following equation

### 2018-07-30 paper_prd.tex
fixed table I typos
Some work on the draft.

--- 2018-06-28 paper_prd.tex
@@
 Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.
-Thick accretion disks (or tori) are common in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts.
+Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts.
 Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks.
@@
  \hline 
-II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ \\
+II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.290$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ \\
  \hline 
-III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.432$ & $0.401$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
  \hline 
@@
  \hline 
-V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.781$ & $0.680$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
  \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.781$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
  \hline 
@@
 \end{eqnarray}
-where $\mu$ is the mass of the scalar field and $^*$ denotes complex conjugation.
-The interested reader is addressed to~\cite{Herdeiro:2015b} for details on the equations of motion for the scalar field $\Psi$ and the four metric functions ${W, F_i}$, along with their solution.
+where $\mu$ is the mass of the scalar field and superscript $(^*)$ denotes complex conjugation.
+The interested reader is addressed to~\cite{Herdeiro:2015b} for details on the equations of motion for the scalar field $\Psi$ and the four metric functions ${W, F_0,F_1,F_2}$, along with their solution.
 
@@
 Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
-It is worth mentioning that some of the models violate the Kerr bound (normalized sìn parameter larger than 1) in terms of both ADM or horizon quantities.
+It is worth mentioning that some of the models violate the Kerr bound (normalized spìn parameter larger than 1) in terms of both ADM or horizon quantities.
 This is not a source of concern because, as shown in~\cite{Herdeiro:2015c} the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
@@
 
-Equilibrium models of disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric.
+Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004} and references therein).
 This was the approach followed in~\cite{Gimeno-Soler:2017}.
-For KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
+For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
 
@@
 
-In this work, for simplicity, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$.
-This is contrary to the approach we followed in~\cite{Gimeno-Soler:2017} where the angular momentum ansatz followed the approach of~\cite{Qian:2009}.
+The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
+In this work, for simplicity and to reduce the ample space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
+This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
 \tf{We should explain/motivate why we change our approach in this paper.} The specific value of the angular momentum is computed as the minimum of the following equation
 \begin{equation}\label{eq:mb_ang_mom}
-l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi}\pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
+l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
 \end{equation}
-where the plus sign is for prograde orbits and the minus is for retrograde orbits.
-This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary, axisymmetric spacetimes.
+where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
+This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
 For prograde motion, the function has a minimum outside the event horizon.
-The location of said minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
-We show the proof of this statement at appendix~\ref{ang_mom_appendix}.
-This choice of angular momentum distribution is motivated by its simplicity (for a first study of thick tori around KBHsSH) and for allowing the presence of a cusp (to allow matter accretion onto the black hole) and a centre.
+The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
+We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
+\tf{Is there an Appendix A?}.
 
@@
 
-We use the procedure described by~\cite{Montero:2007}, where we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
+To account for the magnetic flied in the disks we use the procedure described by~\cite{Montero:2007}.
+We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
 $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
@@
 \end{equation}
-is the energy-momentum tensor of a magnetised perfect fluid, $h$, $\rho$ $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
+is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, and  $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
 four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+$b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
 and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
@@
 where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
-If we define the potential as $W \equiv \ln |u_t|$, then we can integrate the equation~\eqref{eq:diff_ver} as
+If we define the potential as $W \equiv \ln |u_t|$, then we can integrate Eq.~\eqref{eq:diff_ver} as
 \begin{equation}\label{eq:final}
@@
 
-We also write the expressions of the total energy density for the torus $\rho_{\mathrm{T}}$:
+In addition, the total energy density for the torus $\rho_{\mathrm{T}}$ is given by
 \begin{equation}\label{eq:torus_energy_density}
@@
 \end{equation}
-and the total energy density for the scalar field $\rho_{\mathrm{SF}}$:
+while the total energy density for the scalar field $\rho_{\mathrm{SF}}$ reads
 \begin{equation}\label{eq:SF_energy_density}
@@
 
-In this work, we set the mass of the scalar field $\mu = 1$, the angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EoS to $q = \Gamma = 4/3$, and the density at the disk centre $\rho_{\mathrm{c}} = 1$.
-Then, we leave the magnetization at the center $\beta_{\mathrm{m_c}}$ as a parameter (for each model of KBHSH).
-With this information we can compute all the relevant physical quantities.
+In this work, we set the mass of the scalar field $\mu = 1$, the angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EoS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
+Thus, we leave the magnetization at the center $\beta_{\mathrm{m_c}}$ as a free parameter for each model of KBHSH.
+With this information we can compute all relevant physical quantities.
 
@@
 %%%%%%%%%%%%%%%%
-\subsection{Building the disk}
+\subsection{Building the disks}
 %%%%%%%%%%%%%%%%
@@
 To construct our models we take the following steps:
-First, we find the angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the value at the minimum and the location of said minimum outside the event horizon of equation~\eqref{eq:mb_ang_mom}.
-This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$ and $W_{\mathrm{in}} = 0$ and then, we can compute the potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
-Considering this, and that we can write the magnetic pressure at the center as
+First, we find the angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the value at the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum outside the event horizon, respectively.
+This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
+Next, we can compute the gravitational potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
+Considering this, and that we can write the magnetic pressure at the centre as
 \begin{equation}
-p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = K/\beta_{\mathrm{m_c}},
+p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
 \end{equation}
 where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
-Replacing this into the equation~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
+\tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
 \begin{equation}\label{eq:K_eq}

### 2018-07-30 paper_prd.tex
Some work on the intro.

@@
 
-In recent years, new families of stationary, asymptotically flat black holes (BHs) in general relativity, avoiding the so-called ``no hair" theorems, have been obtained.
-In particular, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counter example to the no hair conjecture, in general relativity minimally coupled to simple (bosonic) matter fields obeying all energy conditions.
-The physical conditions and stability properties of these {\it hairy} BHs  (HBHs) have been investigated to assess their potential viability as valid alternatives to astrophysical Kerr BHs.
-On the one hand, HBHs have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017}.
-Moreover, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, for the largest timescale possible (the age of the Universe), rendering hairy BHs as {\it effectively} stable.
+In recent years, new families of stationary, asymptotically flat black holes (BHs) in general relativity, avoiding the so-called ``no hair" theorems, have been obtained (see e.g.~\cite{Herdeiro:2015_review} and references therein).
+In particular, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture, resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
+The physical conditions and stability properties of these {\it hairy} BHs  (HBHs) have been investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.
+On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH
+in spherical  symmetry).
+On the other hand, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, rendering HBHs as {\it effectively} stable.
 
-In addition, the detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
+In the observational arena, the LIGO/Virgo detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the exciting prospects of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
 Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.

### 2018-07-31 paper_prd.tex
More work on the draft.

@@
 
-\title{Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum}
+\title{Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks}
 
@@
 \begin{abstract} 
-We present a method to build magnetized constant angular momentum disks around Kerr black holes with scalar hair (KBHsSH).
+Testing the true nature of black holes -- the no-hair hypothesis -- will become increasingly more precise in the next few years as new observational data is collected in both the gravitational wave channel and the electromagnetic channel.
+In this work we consider numerically generated spacetimes of Kerr black holes with synchronised scalar hair and build stationary models of magnetized constant angular momentum thick disks around them.
+We study the dependence of the morphology and properties of the accretion tori on the type of black hole considered, from purely Kerr black holes with varying degrees of  spin parameter to Kerr black holes with scalar hair with different ADM mass and horizon angular velocity.
+\tf{To be completed.}
 \end{abstract}
@@
 
-In recent years, new families of stationary, asymptotically flat black holes (BHs) in general relativity, avoiding the so-called ``no hair" theorems, have been obtained (see e.g.~\cite{Herdeiro:2015_review} and references therein).
-In particular, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture, resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
-The physical conditions and stability properties of these {\it hairy} BHs  (HBHs) have been investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.
-On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH
-in spherical  symmetry).
+In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein).
+Among those, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
+The physical conditions and stability properties of these classes of {\it hairy} BHs  (HBHs) have been recently investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.
+On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH in spherical  symmetry).
 On the other hand, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, rendering HBHs as {\it effectively} stable.
 
-In the observational arena, the LIGO/Virgo detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the exciting prospects of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs.
-Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.
+In the observational arena, the LIGO/Virgo detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the exciting prospects of observing the first image -- the black hole {\it shadow} -- of a BH by the Event Horizon Telescope (EHT)~\cite{Fish:2016} opens the opportunity to test the true nature of BHs -- the no-hair hypothesis -- and, in particular, the astrophysical relevance of HBHs.
+It is not yet known whether the LIGO/Virgo binary BH signals are consistent with alternative scenarios, such as the merger of ultracompact boson stars or non-Kerr BHs, because the latter possibilities remain thus far insufficiently modelled.
+Likewise, Kerr BHs with scalar hair (KBHsSH) can exhibit very distinct shadows from those of (bald) Kerr BHs, as shown by~\cite{Cunha:2015} and~\cite{Vincent:2016} for two different setups for the light source, either a celestial sphere far from the compact object or an emitting torus of matter surrounding the BH, respectively.
+It is therefore an intriguing open possibility if the very long baseline interferometric observations of BH candidates in Sgr A* and M87 envisaged by the EHT may constrain the astrophysical significance of HBHs.
+
+The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}.
+Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein).
+In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}.
+Our procedure, which combines earlier approaches  put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
+In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
+In this investigation we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case, whose sequences have already been computed.
+The dynamical stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
+
+%Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.
 Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts.
 Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks.
-Our procedure, which combines earlier approaches
-by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
-In~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
-Our immediate goal in the present work is to assess if and how the accretion disk morphology depends on the type of BH considered, either Kerr BHs of varying spins or Kerr BHs with scalar hair (KBHsSH).
-Moreover, we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case.
-In subsequent investigations, we will analyze the shadows of the equilibrium models of KBHsSH presented in this work as well as in {\it dynamical} situations.
 
-The organization of this paper is as follows: Section~\ref{framework} presents  the  analytic  mathematical framework to build non-self-gravitating magnetized discs in the spacetime of KBHsSH.
-Section~\ref{procedure} discusses the corresponding numerical methodology.
-The sequences of equilibrium models are presented and  discussed in Section~\ref{results}.
+The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH.
+Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks.
+Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties.
 Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
-
-%HERE
 
@@
 Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
-It is worth mentioning that some of the models violate the Kerr bound (normalized spìn parameter larger than 1) in terms of both ADM or horizon quantities.
-This is not a source of concern because, as shown in~\cite{Herdeiro:2015c} the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
+It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than 1) in terms of both ADM or horizon quantities.
+This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
 For comparison, we also show in the last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
@@
 In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+\tf{This figure has to be redone.}
 

### 2018-08-02 paper_prd.tex
SOme more work on the paper.

@@
 Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
+Geometrized units ($G=c=1$) are used throughout.
 
@@
 \hline           
-I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$\\ 
+I & $0.415$ & $0.172$ & $0.393$ &  $0.150$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$\\ 
  \hline 
@@
 
-The stationary and axisymmetric metric ansatz is a solution to the EKG field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi G (T_{\mathrm{SF}})_{ab}$ with 
+The stationary and axisymmetric metric ansatz is a solution to the EKG field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi (T_{\mathrm{SF}})_{ab}$ with 
 \begin{eqnarray}\label{eq:e-m_scalaf_field}
@@
 The models have been selected to span all regions of interest in the parameter space.
-Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
+Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a hairy Kerr BH with almost all the mass and angular momentum stored in the scalar field.
 It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than 1) in terms of both ADM or horizon quantities.
@@
 \tf{This figure has to be redone.}
-
-%\begin{table}
-%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-%\label{models_spin_vel}      
-%\centering          
-%\begin{tabular}{c c c c c}
-%\hline\hline       
-% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-%\hline           
-%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
-% \hline 
-%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
-% \hline 
-%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
-% \hline 
-%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
-% \hline 
-%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
-% \hline 
-%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
-% \hline 
-%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-%\hline      
-%\end{tabular}
-%\end{table}
 
@@
 \hspace{-0.2cm}
-\caption{Rest-mass density distribution.
-From top to bottom the rows correspond to the different models for the KBHsSH (I, II, III and IV).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\caption{Distribution of the logarithm of the rest-mass density.
+From top to bottom the rows correspond to the first four models of KBHsSH (I, II, III and IV).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
+The range of the colour scale is not the same for all plots.
+\tf{Perhaps it would be good to include in the upper left corner of each plot a legend indicating the model (e.g. Model I) and the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
+}
 \label{models_I}
@@
 \hspace{-0.2cm}
-\caption{Rest-mass density distribution.
-From top to bottom the rows correspond to the different models for the KBHsSH (V, VI and VII).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII). \tf{Same comment as in the previous figure.}}
 \label{models_II}
@@
 
-Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004} and references therein).
-This was the approach followed in~\cite{Gimeno-Soler:2017}.
+Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein).
 For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
@@
 This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
-\tf{We should explain/motivate why we change our approach in this paper.} The specific value of the angular momentum is computed as the minimum of the following equation
+\tf{We should explain/motivate why we change our approach in this paper.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
 \begin{equation}\label{eq:mb_ang_mom}
-l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm\left(\sqrt{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)\sqrt{1+g_{tt}}}{-g_{tt}}
+l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}
 \end{equation}
 where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
-This expression is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
+Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
+Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
 For prograde motion, the function has a minimum outside the event horizon.
@@
 
-To account for the magnetic flied in the disks we use the procedure described by~\cite{Montero:2007}.
+To account for the magnetic flied in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
 We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
@@
 \begin{equation}\label{eq:e-m_tensor}
-T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
+T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
 \end{equation}
-is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, and  $p$ being the fluid specific enthalpy, density and fluid pressure, respectively. 
+is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
+The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
 Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
@@
 \end{equation}
-where $i = r, \theta$. Then, we rewrite this equation in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, to obtain
+where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
 \begin{equation}\label{eq:diff_ver}
-\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
+\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
 \end{equation}
@@
 
-To integrate Eq.~\eqref{eq:diff_ver} we first assume a polytropic equation of state of the form
+To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
 \begin{equation}\label{eq:eos_fluid}
@@
 with $K$ and $\Gamma$ constants.
-Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analogous equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$
-\begin{equation}\label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} = M \tilde{w}^q,
+ By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\widetilde{\rho h} = \mathcal{L} (\rho h)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
+\begin{eqnarray}
+\label{eq:eos_mag_tilde}
+\tilde{p}_{\mathrm{m}} &=& M \widetilde{\rho h}^q,
+\\
+p_{\mathrm{m}} &=& M \mathcal{L}^{q-1} (\rho h)^q,
+\end{eqnarray}
+where $M$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
+\begin{equation}\label{eq:final}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0,
 \end{equation}
-or, in terms of the magnetic pressure $p_{\mathrm{m}}$
-\begin{equation}\label{eq:eos_mag}
-p_{\mathrm{m}} = M \mathcal{L}^{q-1} w^q,
-\end{equation}
-where $w = \rho h$ is the fluid enthaply density, and $M$ and $q$ are constants.
-If we define the potential as $W \equiv \ln |u_t|$, then we can integrate Eq.~\eqref{eq:diff_ver} as
-\begin{equation}\label{eq:final}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}w)^{q-1}=0,
-\end{equation}
-where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
+where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and  $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
 
-In addition, the total energy density for the torus $\rho_{\mathrm{T}}$ is given by
-\begin{equation}\label{eq:torus_energy_density}
-\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
-\end{equation}
-while the total energy density for the scalar field $\rho_{\mathrm{SF}}$ reads
-\begin{equation}\label{eq:SF_energy_density}
-\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
-\end{equation}
+We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
+These are  given by
+\begin{eqnarray}\label{eq:torus_energy_density}
+\rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
+\\
+\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+\end{eqnarray}
 
-In this work, we set the mass of the scalar field $\mu = 1$, the angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EoS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
-Thus, we leave the magnetization at the center $\beta_{\mathrm{m_c}}$ as a free parameter for each model of KBHSH.
+%
+%\begin{equation}\label{eq:torus_energy_density}
+%\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
+%\end{equation}
+%and
+%\begin{equation}\label{eq:SF_energy_density}
+%\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+%\end{equation}
+
+From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
+In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
+Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
 With this information we can compute all relevant physical quantities.
+
+\tf{We should discuss a bit more the reason for this choice.
+If $l_{\rm ms}<l<l_{\rm mb}$ and $r_{\rm mb}<r_{\rm cusp}<r_{\rm ms}$ the disk is closed and has a centre and a cusp.
+If $l=l_{\rm mb}$ and $r_{\rm cusp}=r_{\rm mb}$ the disk has a centre and a cusp, and it is closed at infinity.
+The models we have built are the latter, right?
+I wonder if we should have built models not completely filling their Roche lobe, so that they had a finite size.
+In any case, a comment must be provided here.}
+
+\tf{We also have to emphasize that we do not fix $h=1$.}
 
@@
 
+\tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
+poor now. It needs a lot of rewriting.}
+
 %%%%%%%%%%%%%%%%
@@
 
-To construct our models we take the following steps:
-First, we find the angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the value at the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum outside the event horizon, respectively.
+To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
 This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
-Next, we can compute the gravitational potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
+Next, we can compute the gravitational plus centrifugal potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
 Considering this, and that we can write the magnetic pressure at the centre as
@@
 
-In figures~\ref{models_I} and~\ref{models_II} we show the rest-mass density distribution for all our KBHsSH models with 3 different values of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, namely $10^{10}$, $1$ and $10^{-10}$.
-In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimeteral radial coordinate such as $R = e^{F_2} r$.
-Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+\subsection{2D Morphology}
+
+We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}.
+The radial coordinate in these figures is the standard one of the spherical coordinate system.
+Figures~\ref{models_I} and~\ref{models_II} show the logarithm of the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
+
+The structure of the disks is similar for all values of $\beta_{\mathrm{m_c}}$ with the only quantitative differences being the location of the centre of the disk, which moves closer to the BH as the magnetization increases, and the range of variation of the isodensity contours, whose upper ends become larger with decreasing $\beta_{\mathrm{m_c}}$.
+This behaviour is in complete agreement with that found for KBHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
+For the particular case of Model VII, the maximum of the rest-mass density for the stronlgy magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
+\tf{Can we use the last isodentity contour as a good measure of the size of the disk?}
+
+In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$.
+\tf{We need to justify why we introduce this new radial coordinate.
+What is the benefit?}
+
+%HERE
+
 Tables~\ref{HBH_disk_parameters} and~\ref{KBH_disk_parameters} show the relevant physical quantities for both KBHSH and the same KBH cases we presented in the figures.
@@
 The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+
+\subsection{Radial profiles}
 
@@
 This idea is discussed in appendix~\ref{torus_embedding}.
+
+\subsection{Comparison with KBHs}
+
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
 

### 2018-08-03 paper_prd.tex
Some work on the draft.

@@
 \hspace{-0.2cm}
-\caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to the different models for the KBHsSH (I, II, III and IV).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
 \label{models_peri_I}
@@
 \hspace{-0.2cm}
-\caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to the different models for the KBHsSH (V, VI, VII).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
 \label{models_peri_II}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
-\hspace{-0.2cm}
-\\
-\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down).
-From left to right the columns correspond to different models (I, IV and VII).
-From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{comparison_mass_density}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
-\hspace{-0.2cm}
-\\
-\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Gravitational mass density distribution for the torus $\rho_{\mathrm{T}}$ (up) and the scalar field $\rho_{\mathrm{SF}}$ (down) using perimeteral coordinates.
-From left to right the columns correspond to different models (I, IV and VII).
-From top to bottom, the rows correspond to different calues of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{comparison_mass_density_peri}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
-\hspace{-0.cm}
-\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
-\hspace{-0.cm}
-\\
-\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
-\hspace{-0.cm}
-\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
-\hspace{-0.cm}
-\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
-In the first row, we show this for all of our KBHsSH models.
-In the second row, we show this for a sequence of KBHs with increasing spin parameter.}
-\label{comparison_HBH_Kerr_dens_enth}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.2]{figures/fig8_HBH.eps}
-\hspace{0.5cm}
-\includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
-\hspace{0.5cm}
-\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
-Left panel: KBHsSH models.
-Right panel: A sequence of KBHs with increasing spin parameter.}
-\label{comparison_HBH_Kerr_r_m_max}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
-\hspace{-0.2cm}
-\caption{Rest-mass density distribution.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{models_Kerr}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
-\hspace{-0.2cm}
-\caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{models_Kerr_peri}
 \end{figure*}
@@
 For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
-
-%HERE
 
@@
 
-\tf{We also have to emphasize that we do not fix $h=1$.}
+\tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}
 
@@
 
+\begin{table*}[t]
+\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH.
+For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
+\tf{Are we using the perimetral radial coordinate in this table?}}
+\label{HBH_disk_parameters}      
+\centering          
+\begin{tabular}{c c c c c  c c c c c c c}
+\hline\hline       
+ Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+\hline           
+I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
+ \hline 
+II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
+ \hline 
+III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
+\hline  
+IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
+\hline   
+V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
+\hline 
+ &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
+\hline   
+VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
+\hline 
+VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
+\hline 
+\end{tabular}
+\end{table*}
+
 \subsection{2D Morphology}
@@
 \tf{We need to justify why we introduce this new radial coordinate.
-What is the benefit?}
+What is the benefit?
+Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.}
 
@@
 
-Tables~\ref{HBH_disk_parameters} and~\ref{KBH_disk_parameters} show the relevant physical quantities for both KBHSH and the same KBH cases we presented in the figures.
+Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for our disk models around KBHsSH.
 First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
@@
 
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (superior half) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for 3 of the models (I, IV and VII) and 2 values of the magnetization parameter at the center ($10^{10}$ and $10^{-10}$).
+\begin{figure*}
+\centering
+\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
+From left to right the columns correspond to models I, IV, and VII.
+The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
+\tf{I think there is a lot of vertical space that we do not really need in these plots.
+To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
+I know the plot will not look squared, but that's fine.}
+}
+\label{comparison_mass_density}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
+\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
+\label{comparison_mass_density_peri}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
+\hspace{-0.cm}
+\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
+\hspace{-0.cm}
+\\
+\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
+\hspace{-0.cm}
+\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
+\hspace{-0.cm}
+\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
+In the first row, we show this for all of our KBHsSH models.
+In the second row, we show this for a sequence of KBHs with increasing spin parameter.}
+\label{comparison_HBH_Kerr_dens_enth}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.2]{figures/fig8_HBH.eps}
+\hspace{0.5cm}
+\includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
+\hspace{0.5cm}
+\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
+Left panel: KBHsSH models.
+Right panel: A sequence of KBHs with increasing spin parameter.}
+\label{comparison_HBH_Kerr_r_m_max}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution using perimeteral coordinates.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr_peri}
+\end{figure*}
+
+\begin{table*}[t]
+\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
+For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
+\label{KBH_disk_parameters}      
+\centering          
+\begin{tabular}{c c c c c  c c c c c c c}
+\hline\hline       
+ $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+\hline           
+$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
+ \hline 
+ $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
+\hline  
+$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
+ \hline 
+$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
+\hline   
+\end{tabular}
+\end{table*}
+
+Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}
+
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
+\tf{Describe this figure.}
+
 In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
 The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+\tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}
+
+\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
+Is this correct?
+Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field?
+Is this a valid approximation because we are in the test-fluid regime?
+What did~\cite{Vincent:2016} do?}
+
+\subsection{Comparison with KBHs}
+
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+
+As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
+Nevertheless, we show them for the sake of clarity.
+Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
+This idea is discussed in appendix~\ref{torus_embedding}.
 
@@
 \sg{Include discussion about radial profiles.}
-
-As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
-Nevertheless, we show them for the sake of clarity.
-Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
-This idea is discussed in appendix~\ref{torus_embedding}.
-
-\subsection{Comparison with KBHs}
-
-Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
 
@@
 %\end{table}
-
-\begin{table*}[t]
-\caption{Disk parameters and values of their relevant physical magnitudes. For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$}        
-\label{HBH_disk_parameters}      
-\centering          
-\begin{tabular}{c c c c c  c c c c c c c}
-\hline\hline       
- Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
-\hline           
-I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
- \hline 
-II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
- \hline 
-III & $1.06$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
-\hline  
-IV & $1.16$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
-\hline   
-V & $1.20$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
-\hline 
- &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
-\hline   
-VI & $1.20$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
-\hline 
-VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
-\hline 
- &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
-\hline 
-\end{tabular}
-\end{table*}
-
-\begin{table*}[t]
-\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
-For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
-\label{KBH_disk_parameters}      
-\centering          
-\begin{tabular}{c c c c c  c c c c c c c}
-\hline\hline       
- $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
-\hline           
-$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
- \hline 
- $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
-\hline  
-$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
- \hline 
-$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
-\hline   
-\end{tabular}
-\end{table*}
 

### 2018-08-07 paper_prd.tex
A bit of work.

@@
 
-\subsection{Radial profiles}
+%%%%%%%%%%%%%%%%%%
+\subsection{Magnetization profiles}
+%%%%%%%%%%%%%%%%%%
 
-The behaviour of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ is shown in figures~\ref{comparison_HBH_Kerr_dens_enth} for the models (I-VII) and for a sequence of increasing spin parameter KBHs, here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
+The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
+\tf{Maybe there is an excessive number of cases for KBHs.
+Maybe it's enough to only include the four cases we have in Table III.
+We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9.
+This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
 However, there are differences between the two cases.

### 2018-09-12 paper_prd.tex
answering some questions

--- 2018-08-02 paper_prd.tex
@@
 This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
-\tf{We should explain/motivate why we change our approach in this paper.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
+\tf{We should explain/motivate why we change our approach in this paper.}\sg{We limit this study to the constant angular momentum case to limit the parameter space, as the main aim of this paper is to study the dependence of the characteristics of magnetised discs with respect to the KBHSH spacetime.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
 \begin{equation}\label{eq:mb_ang_mom}
@@
 
-To account for the magnetic flied in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
+To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
 We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
@@
 with $K$ and $\Gamma$ constants.
- By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\widetilde{\rho h} = \mathcal{L} (\rho h)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
+ By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$, $w = \rho h$ and $\tilde{w} = \mathcal{L} (w)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
 \begin{eqnarray}
 \label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} &=& M \widetilde{\rho h}^q,
+\tilde{p}_{\mathrm{m}} &=& M \tilde{w}^q,
 \\
@@
 From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
-Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
+In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
 With this information we can compute all relevant physical quantities.
@@
 In any case, a comment must be provided here.}
+\sg{We choose this value for the angular momentum and the inner radius of the disc to allow discs with a cusp and a centre that also are marginally stable (a small perturbation can trigger accretion into the black hole).
+Also, the thermodynamical quantities reach its maximum for this particular choice of angular momentum and inner radius of the disc (as they are related to the total potential well $|\Delta W|$).
+This also means that the resulting discs will be semi-infinite (they are closed at infinity), this is not a source of concern, as the external layers of the disc have extremely low density.
+(not sure about the relevance of the last part...)}
 
@@
 poor now. It needs a lot of rewriting.}
+\sg{I have serious doubts about this section, as I am not really certain that we need to provide an explanation for some specific parts (that are pretty obvious anyway) Perhaps I should go into detail for the numerical part?
+(e.g.
+that Eq.~\eqref{eq:final} is a trascendental equation and we are bound to solve it numerically with the bisection method for each cell of our numerical grid)}
 
-%%%%%%%%%%%%%%%%
-\subsection{Building the disks}
-%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%
+% \subsection{Building the disks}
+% %%%%%%%%%%%%%%%%
 
-To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
+% To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
 This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
@@
 Considering this, and that we can write the magnetic pressure at the centre as
-\begin{equation}
-p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
-\end{equation}
-where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
+% \begin{equation}
+% p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
+% \end{equation}
+% where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
 \tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
-\begin{equation}\label{eq:K_eq}
-W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
-\end{equation}
-Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
+% \begin{equation}\label{eq:K_eq}
+% W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
+% \end{equation}
+% Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
 With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
 
-%%%%%%%%%%%%%%%%%
-\subsection{Numerical method}
-%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%
+% \subsection{Numerical method}
+% %%%%%%%%%%%%%%%%%
 
-We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
-Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
+% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
+Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
 
@@
 \begin{appendix}
-\section{Embedding of the accretion torus in $\mathbb{E}^3$}\label{torus_embedding}
-Following the same reasoning as in~\cite{Delgado:2018}, we write the 2-metric for the surface of a torus as 
-\begin{equation}\label{eq:torus_prev_metric}
-\mathrm{d}\sigma^2 = \frac{e^{2 F_1}}{N}\mathrm{d}r^2+ e^{2 F_1}r^2\mathrm{d}\theta^2+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
-\end{equation}
-and the condition $r = r(\theta)$ for the surface of the torus.
+% \section{Embedding of the accretion torus in $\mathbb{E}^3$}\label{torus_embedding}
+% Following the same reasoning as in~\cite{Delgado:2018}, we write the 2-metric for the surface of a torus as 
+% \begin{equation}\label{eq:torus_prev_metric}
+% \mathrm{d}\sigma^2 = \frac{e^{2 F_1}}{N}\mathrm{d}r^2+ e^{2 F_1}r^2\mathrm{d}\theta^2+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
+% \end{equation}
+% and the condition $r = r(\theta)$ for the surface of the torus.
 The location of the surface of the torus $r(\theta)$ can be obtained integrating $r' = \frac{\mathrm{d}r}{\mathrm{d}\theta} = -\frac{\partial_{\theta}W}{\partial_{r}W}$ (equation (24) of~\citep{Gimeno-Soler:2017}).
 Using this, we can write equation~\eqref{eq:torus_prev_metric} as
-\begin{equation}\label{eq:torus_metric}
-\mathrm{d}\sigma^2 = e^{2 F_1} \mathrm{d}\theta^2\left(\frac{r'^2}{N} +r^2\right)+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
-\end{equation}
-with the prime $'$ denoting partial differentiation with respect to $\theta$.
+% \begin{equation}\label{eq:torus_metric}
+% \mathrm{d}\sigma^2 = e^{2 F_1} \mathrm{d}\theta^2\left(\frac{r'^2}{N} +r^2\right)+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
+% \end{equation}
+% with the prime $'$ denoting partial differentiation with respect to $\theta$.
 Then, we try the embedding in $\mathbb{E}^3$ with the Cartesian metric $\mathrm{d}\sigma^2 = \mathrm{d}X^2 + \mathrm{d}Y^2 + \mathrm{d}Z^2$ and the embedding functions:
-\begin{equation}
-X + \mathrm{i}Y = f(\theta)e^{\mathrm{i}\phi},  \;\;\; Z = g(\theta),
-\end{equation}
-then
-\begin{equation}
-f = e^{2 F_2} r^2 \sin^2\theta, \;\;\; f'^2 + g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right),
-\end{equation}
-so we can write $g'^2$ as
-\begin{equation}\label{eq:embedding_existance}
-g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right) - e^{2 F_2} (F_2'r \sin \theta + r' \sin \theta + r \cos \theta)^2.
-\end{equation}
-This result tells us that the r.h.s. of~\eqref{eq:embedding_existance} must be $\geq 0$ in order to the embedding function to exist.
+% \begin{equation}
+% X + \mathrm{i}Y = f(\theta)e^{\mathrm{i}\phi},  \;\;\; Z = g(\theta),
+% \end{equation}
+% then
+% \begin{equation}
+% f = e^{2 F_2} r^2 \sin^2\theta, \;\;\; f'^2 + g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right),
+% \end{equation}
+% so we can write $g'^2$ as
+% \begin{equation}\label{eq:embedding_existance}
+% g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right) - e^{2 F_2} (F_2'r \sin \theta + r' \sin \theta + r \cos \theta)^2.
+% \end{equation}
+% This result tells us that the r.h.s. of~\eqref{eq:embedding_existance} must be $\geq 0$ in order to the embedding function to exist.
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.2]{figures/embedding.pdf}
-\hspace{0.5cm}
-\caption{Rest-mass density distribution for model VII with $r_{\mathrm{in}} = 0.08$ and $\beta_{\mathrm{m_c}} = 10^{10}$ (up) and the scalar field amplitude distribution $\phi$ (down).
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.2]{figures/embedding.pdf}
+% \hspace{0.5cm}
+% \caption{Rest-mass density distribution for model VII with $r_{\mathrm{in}} = 0.08$ and $\beta_{\mathrm{m_c}} = 10^{10}$ (up) and the scalar field amplitude distribution $\phi$ (down).
 The isocontours are blue when the r.h.s.
 of equation~\eqref{eq:embedding_existance} is $> 0$ and red when is $\leq 0$.}
-\label{embedding_VII}
-\end{figure*}
+% \label{embedding_VII}
+% \end{figure*}
 
 \section{Finding $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$}\label{ang_mom_appendix}
-\sg{To do.}
+\sg{I figured this out, but now I am not really sure if this is interesting enough to be an appendix by itself. Maybe more like a comment in the main text.}
 \end{appendix}

### 2018-09-12 paper_prd.tex
answering some questions

@@
 
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (superior half) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for 3 of the models (I, IV and VII) and 2 values of the magnetization parameter at the center ($10^{10}$ and $10^{-10}$).
+\begin{figure*}
+\centering
+\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
+From left to right the columns correspond to models I, IV, and VII.
+The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
+\tf{I think there is a lot of vertical space that we do not really need in these plots.
+To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
+I know the plot will not look squared, but that's fine.}
+}
+\label{comparison_mass_density}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
+\hspace{-0.4cm}
+\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
+\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
+\label{comparison_mass_density_peri}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
+\hspace{-0.cm}
+\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
+\hspace{-0.cm}
+\\
+\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
+\hspace{-0.cm}
+\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
+\hspace{-0.cm}
+\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
+In the first row, we show this for all of our KBHsSH models.
+In the second row, we show this for a sequence of KBHs with increasing spin parameter.}
+\label{comparison_HBH_Kerr_dens_enth}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.2]{figures/fig8_HBH.eps}
+\hspace{0.5cm}
+\includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
+\hspace{0.5cm}
+\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
+Left panel: KBHsSH models.
+Right panel: A sequence of KBHs with increasing spin parameter.}
+\label{comparison_HBH_Kerr_r_m_max}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution using perimeteral coordinates.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr_peri}
+\end{figure*}
+
+\begin{table*}[t]
+\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
+For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
+\label{KBH_disk_parameters}      
+\centering          
+\begin{tabular}{c c c c c  c c c c c c c}
+\hline\hline       
+ $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+\hline           
+$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
+ \hline 
+ $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
+\hline  
+$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
+ \hline 
+ &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
+ \hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
+ \hline 
+$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
+\hline   
+\end{tabular}
+\end{table*}
+
+Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}
+
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
+\tf{Describe this figure.}
+
 In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
 The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+\tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}
 
-\subsection{Radial profiles}
+\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
+Is this correct?
+Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field?
+Is this a valid approximation because we are in the test-fluid regime?
+What did~\cite{Vincent:2016} do?}
 
-The behaviour of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ is shown in figures~\ref{comparison_HBH_Kerr_dens_enth} for the models (I-VII) and for a sequence of increasing spin parameter KBHs, here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
+\subsection{Comparison with KBHs}
+
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+
+As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
+Nevertheless, we show them for the sake of clarity.
+Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
+This idea is discussed in appendix~\ref{torus_embedding}.
+
+%%%%%%%%%%%%%%%%%%
+\subsection{Magnetization profiles}
+%%%%%%%%%%%%%%%%%%
+
+The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
+\tf{Maybe there is an excessive number of cases for KBHs.
+Maybe it's enough to only include the four cases we have in Table III.
+We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9.
+This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
 However, there are differences between the two cases.

### 2018-11-06 paper_prd.tex
work on the draft, new figures

@@
 \hspace{-0.2cm}
-\caption{Distribution of the logarithm of the rest-mass density.
+\caption{Distribution of the rest-mass density.
 From top to bottom the rows correspond to the first four models of KBHsSH (I, II, III and IV).
@@
 The range of the colour scale is not the same for all plots.
-\tf{Perhaps it would be good to include in the upper left corner of each plot a legend indicating the model (e.g. Model I) and the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}
+\tf{Perhaps it would be good to include in the upper left corner of each plot a legend indicating the model (e.g. Model I) and the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}\sg{Done.}
 }
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII). \tf{Same comment as in the previous figure.}}
+\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII). \tf{Same comment as in the previous figure.}\sg{Done.}}
 \label{models_II}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
+\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}\sg{Done.}}
 \label{models_peri_I}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}}
+\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}\sg{Done.}}
 \label{models_peri_II}
@@
 We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
-\tf{Is there an Appendix A?}.
+\tf{Is there an Appendix A?}.\sg{Yes.
+Please, read Appendix A}.
 
@@
 To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
-We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
+First, we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
 $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
@@
 \begin{equation}\label{eq:diff_ver}
-\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
+\partial_i(|\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
 \end{equation}
@@
 \\
-\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{-2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
 \end{eqnarray}
-
+Using these expressions, we can compute the total gravitational mass of the torus and the scalar field as the following expression
+\begin{equation}\label{eq:mass_integral}
+\mathcal{M} = \int  \rho \sqrt{-g}\mathrm{d}^3x\,
+\end{equation}
+where $g$ is the determinant of the metric tensor.
 %
@@
 
+\tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$.
+This is an important difference with respect to the work of~\cite{Vincent:2016}.} \sg{As a concluding remark, it is worth to note that we are taking a different approach to construct the magnetised discs than the standard one~\citep{Komissarov:2006} (this approach was also taken by~\cite{Vincent:2016} for discs around the same kind of KBHsSH we have in this work).
+As it is noted in~\cite{Gimeno-Soler:2017}, this approach considers implicitly assumes that the specific enthalpy is close to $1$ ($w = \rho h \simeq \rho$).
+This means that the polytropic equation Eq.~\eqref{eq:eos_fluid} can be written as $p = K w^{\Gamma}$ (see Eq.~(27) of~\cite{Komissarov:2006}).
+To better understand the differences between this two approaches, we can consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
+For the non-magnetised case, we can rewrite Eq.~\eqref{eq:final} in the limiting case of $\beta_{\mathrm{m_c}} \rightarrow \infty$ ($M \rightarrow 0$) as
+\begin{equation}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) = 0.
+\end{equation}
+Then, we can solve this equation for the specific enthalpy $h$
+\begin{equation}\label{eq:rel_non_mag_enth}
+h = e^{W_{\mathrm{in}} - W}.
+\end{equation}
+Now, we want to obtain an analogous equation for the $h \simeq 1$ case.
+We start by considering Eq.~(20) of~\cite{Gimeno-Soler:2017} and taking the limit $\beta_{\mathrm{m_c}} \rightarrow \infty$ (in this equation, this means $K_{\mathrm{m}} \rightarrow 0$), to obtain
+\begin{equation}
+W - W_{\mathrm{in}} + \frac{\Gamma K}{\Gamma +1}w^{\Gamma -1}.
+\end{equation}
+If we consider the $h \simeq 1$ approximmation, we can use the definition of $h$ and solve the equation to arrive at
+\begin{equation}\label{eq:non_rel_non_mag_enth}
+h = 1 + (W_{\mathrm{in}} - W).
+\end{equation}
+If we compare both results, we can see that Eq.~\eqref{eq:non_rel_non_mag_enth} is the first order Taylor series expansion of Eq.~\eqref{eq:rel_non_mag_enth} for a sufficiently small value of $W_{\mathrm{in}} - W$.
+For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
+This yields the same result for both equations
+\begin{equation}
+W - W_{\mathrm{in}} + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0.
+\end{equation}
+In addition, we could consider the expression for the specific enthalpy in terms of the density $h = 1 + \frac{K\Gamma\rho^{\Gamma-1}}{\Gamma - 1}$ to 
+see that we will have $h \rightarrow 1$. This shows that, for the extremely magnetised limit, this two approaches coincide.
+In conclusion, taking into account this two limits of both approaches we can discuss the range of validity of the $h \simeq 1$ approximmation: As magnetised discs exist between the two considered cases, for discs with a sufficiently small value of the potential well $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$, we can use the $h \simeq 1$ approximmation without fear.
+On the other hand, if the value of $\Delta W$ is large enough, the approximmation could fail even for fairly small magnetised discs.}
+%%%%%%%%%%%%
+\section{Methodology}
+\label{procedure}
+%%%%%%%%%%%%
+\sg{This whole section is rewritten.}
+
+\tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
+poor now. It needs a lot of rewriting.}
+\sg{I have serious doubts about this section, as I am not really certain that we need to provide an explanation for some specific parts (that are pretty obvious anyway) Perhaps I should go into detail for the numerical part?
+(e.g.
+that Eq.~\eqref{eq:final} is a trascendental equation and we are bound to solve it numerically with the bisection method for each cell of our numerical grid)}
+
 From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
-With this information we can compute all relevant physical quantities.
-
+In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
+Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
+With this information we can compute all relevant physical quantities.\sg{I have moved this paragraph from the above section to this one as I find it fits more naturally here.}
 \tf{We should discuss a bit more the reason for this choice.
@@
 (not sure about the relevance of the last part...)}
-
-\tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}
-
-%%%%%%%%%%%%
-\section{Methodology}
-\label{procedure}
-%%%%%%%%%%%%
-
-\tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
-poor now. It needs a lot of rewriting.}
-\sg{I have serious doubts about this section, as I am not really certain that we need to provide an explanation for some specific parts (that are pretty obvious anyway) Perhaps I should go into detail for the numerical part?
-(e.g.
-that Eq.~\eqref{eq:final} is a trascendental equation and we are bound to solve it numerically with the bisection method for each cell of our numerical grid)}
+In particular, this choice of specific angular momentum distribution and inner radius of the disc is taken to allow discs with a cusp and a centre that also are marginally stable (a small perturbation can trigger accretion into the black hole).
+In addition, the thermodynamical quantities reach their maximum for this particular choice of parameters (as they are related to the total potential well $|\Delta W|$) \sg{I am not sure if this needs further explanation}.) This also means that the resulting discs will be semi-infinite (they are closed at infinity) but this is not a source of concern, as the external layers of the disc have extremely low density and, at some point, the value will be lower than the density of the atmosphere.
+
+Before starting to build the disc, it is important to note that we need a sufficiently fine numerical grid in order to fully capture the behaviour of the physical magnitudes at the inner region of the disc.
+For that reason, we use a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$.
+This means a radial resolution of $\simeq 0.001$ at the location of the disc centre.
+\sg{This is a rough approximmation, as this exact number depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.
+Nevertheless, the value of the resolution is much better at the cusp, specially if the disk is very close to the horizon (for instance in the $a = 0.9999$ Kerr case).
+Maybe we should clarify this, as these high spin cases need a very high radial resolution.
+Also, it may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots).
+But I think this should go in the results section.} \sg{I am not sure if we have to tell something about the \it{real} initial data} (i.e.
+the data provided by Carlos).
+Next, we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively.
+Once we have that, we can compute the total potential distribution as
+\begin{equation}
+W(r,\theta) \equiv \ln |u_t| = \frac{1}{2} \ln \left| \frac{g_{t\phi}^2-g_{tt}g_{\phi\phi}}{g_{\phi\phi}+2g_{t\phi}l+g_{tt}l^2} \right|.
+\end{equation}
+With the total potential distribution, we can compute the location of the cusp $r_{\mathrm{cusp}}$ and the centre $r_{\mathrm{c}}$ as the extrema (maximum and minimum respectively) of the total potential in the equatorial plane.
+Also, we set $r_{\mathrm{in}} = r_{\mathrm{cusp}}$.
+For our choice of angular momentum distribution, this also means $W_{\mathrm{in}} = 0$.
+Having now the total potential distribution and the characteristic radii of the disc, we can start to compute the thermodynamical quantities in the disc.
+First of all, we compute the polytropic constant $K$ evaluating Eq.~\eqref{eq:final} at the centre
+\begin{equation}\label{eq:to_solve_K}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) + \frac{q}{q-1} \frac{K\rho_{\mathrm{c}}^{\Gamma}}{\beta_{\mathrm{m_c}} (\rho_{\mathrm{c}} + \frac{K\Gamma\rho_{\mathrm{c}}^{\Gamma}}{\Gamma-1})} =0\,
+\end{equation}
+where we have used the definition of magnetic pressure and the definition of the magnetisation parameter $\beta$.
+Using its corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $M$.
+With both $K$ and $M$ obtained, we can now compute the thermodynamical quantities in all our numerical domain.
+For points with $W(r, \theta) > 0$ we set $\rho = p = p_{\mathrm{m}} = 0$ and for points with $W_{\mathrm{c}} < W(r, \theta) < 0$, we write Eq.~\eqref{eq:final} as
+\begin{equation}\label{eq:to_solve_rho}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}(\rho + \frac{K\Gamma \rho^{\Gamma}}{\Gamma - 1}))^{q-1}=0,\,
+\end{equation}
+to compute the rest-mass density $\rho$ of said point.
+Then, we can use again Eqs.~\eqref{eq:eos_fluid} and~\eqref{eq:eos_mag_tilde} and the definition of the specific enthalpy to compute the distribution of $p$, $p_{\mathrm{m}}$ and $h$.
+
+It is relevant to note that Eqs.~\eqref{eq:to_solve_K} and~\eqref{eq:to_solve_rho} are trascendental equations and that, particularly Eq.~\eqref{eq:to_solve_rho} must be solved at each point of our numerical grid.
+To solve these equations we use the bisection method.
+To ensure the accuracy of our computations (particularly the accuracy of the maximum and central quantities we report) we choose our grid to have a difference between two adjacent points of $\Delta r (r \simeq r_{\mathrm{c}}) \simeq 0.001$ in the equatorial plane.
 
@@
 For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
-\tf{Are we using the perimetral radial coordinate in this table?}}
+\tf{Are we using the perimetral radial coordinate in this table?}\sg{Yes.}}
 \label{HBH_disk_parameters}      
@@
 
+\begin{figure*}
+\centering
+\includegraphics[scale=0.38]{figures/radial_log_rho_model_I.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.38]{figures/radial_log_rho_model_IV.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.38]{figures/radial_log_rho_model_VII.pdf}
+\hspace{-0.6cm}
+\caption{Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
+In each panel there are .
+Left panel: Model I.
+Central panel: Model IV.
+Right panel: Model VII.}
+\label{radial_profiles_HBH}
+\end{figure*}
+
 \subsection{2D Morphology}
@@
 The radial coordinate in these figures is the standard one of the spherical coordinate system.
-Figures~\ref{models_I} and~\ref{models_II} show the logarithm of the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
+Figures~\ref{models_I} and~\ref{models_II} show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
 
@@
 This behaviour is in complete agreement with that found for KBHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
-For the particular case of Model VII, the maximum of the rest-mass density for the stronlgy magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
-\tf{Can we use the last isodentity contour as a good measure of the size of the disk?}
+For the particular case of Model VII, the maximum of the rest-mass density for the strongly magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
+\tf{Can we use the last isodentity contour as a good measure of the size of the disk?} \sg{In figure~\ref{radial_profiles_HBH}, we can visualise the radial extent for the models I, IV and VII with three different values of the magnetisation ($10^{10}$, $1$, and $10^{-10}$).
+As it can be seen, model I discs are significantly bigger than their model IV and VII counterparts.
+Also, it is important to note the presence of a thicker region of high density in the model VII non-magnetised case (the mildly-magnetised case also has it, but to a lesser extent).
+This could be related to the existence of an extra gravitational well that overlaps with the disc (as it can be seen in the right panel of figure~\ref{comparison_mass_density}).}
 
@@
 What is the benefit?
-Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.}
-
-%HERE
+Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.} \sg{Discuss.
+I find that the 2D morphology in perimeteral coordintes might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$.
+I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass).
+I suppose this could help us to compare different models.
+In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).}
 
@@
 The models V, VI and VII violate that bound.
-This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
+This is related, as we see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
+\sg{The maximum value of these quantities increases with the total potential well $\Delta W$, irrespective of the value of the magnetisation.}
 
@@
 To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
-I know the plot will not look squared, but that's fine.}
+I know the plot will not look squared, but that's fine.}\sg{Done.}
 }
@@
 \caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
-\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
+\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
 \label{comparison_mass_density_peri}
@@
 \hspace{0.5cm}
-\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
+\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)(($R_{\mathrm{mag}, \mathrm{max}} - R_{\mathrm{c}})/ R_{\mathrm{c}}$).
 Left panel: KBHsSH models.
@@
 
-Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}
-
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
+\begin{table}
+\caption{Angular velocity at the centre for the different models computed.
+In the first column, we present the angular velocity at the disc centre for the different KBHsSH models.
+In the second column, we present the angular velocity at the disc centre for a KBH with the same ADM quantities.\sg{to fill with the Kerr case values.}}
+\label{angular_velocity_table}      
+\centering          
+\begin{tabular}{c c c }
+\hline\hline       
+ Model & $\Omega_{\mathrm{c}}$ & $\Omega_{\mathrm{ADM_c}}$ \\ 
+\hline           
+I & $0.493$ & $-$ \\ 
+ \hline 
+II & $0.424$ & $--$ \\
+ \hline 
+III & $0.521$ & $-$ \\ 
+ \hline 
+IV & $0.427$ & $-$ \\ 
+ \hline 
+V & $0.394$ & $-$ \\ 
+ \hline 
+VI & $0.350$ & $-$ \\ 
+ \hline 
+VII & $0.330$ & $-$ \\ 
+\hline      
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+In the first column, we present the value of the central density for the different KBHsSH models.
+In the second column, we present the central density for a KBH with the same ADM quantities.\sg{To fill with the Kerr case values.}}
+\label{central_density_table}      
+\centering          
+\begin{tabular}{c c c c }
+\hline\hline       
+ Model & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{ADM_c}}$ \\ 
+\hline           
+I & $10^{10}$ & $0.002051$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.00434$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.00531$ & $-$ \\ 
+ \hline 
+II & $10^{10}$ & $0.00150$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.00427$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.00582$ & $-$ \\ 
+ \hline 
+III & $10^{10}$ & $0.00304$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.00840$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.0108$ & $-$ \\ 
+ \hline 
+IV & $10^{10}$ & $0.00407$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.00897$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.0110$ & $-$ \\ 
+ \hline 
+V & $10^{10}$ & $0.00577$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.0104$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.0121$ & $-$ \\ 
+ \hline 
+VI & $10^{10}$ & $0.00762$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.0116$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.0131$ & $-$ \\ 
+ \hline 
+VII & $10^{10}$ & $0.0129$ & $-$ \\ 
+ \hline 
+ & $1$ & $0.0162$ & $-$ \\ 
+ \hline 
+ & $10^{-10}$ & $0.01701$ & $-$ \\ 
+ \hline     
+\end{tabular}
+\end{table}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \subsection{Distribution of angular momentum in the disk}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein).
+For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
+
+% We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
+% \begin{equation}
+% l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
+% \end{equation}
+% where $u^{\mu}$ is the fluid four-velocity.
+% The relationship between $l$ and $\Omega$ is given by the equations
+% \begin{equation}
+% l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
+% \end{equation}
+% where we are assuming circular motion, i.e.~the four-velocity can be written as
+% \begin{equation}
+% u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
+% \end{equation}
+
+% The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
+In this work, for simplicity and to reduce the ample space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
+This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
+\tf{We should explain/motivate why we change our approach in this paper.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
+% \begin{equation}\label{eq:mb_ang_mom}
+% l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}
+% \end{equation}
+% where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
+Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
+% Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
+For prograde motion, the function has a minimum outside the event horizon.
+The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
+We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
+\tf{Is there an Appendix A?}.
+
+% %%%%%%%%%%%%%%%%
+% \subsection{Magnetized disks}
+% %%%%%%%%%%%%%%%%
+
+% To account for the magnetic flied in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
+We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
+% $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
+% where $\nabla_{\mu}$ is the covariant derivative and
+% \begin{equation}\label{eq:e-m_tensor}
+% T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
+% \end{equation}
+% is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
+The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
+% Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
+% four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
+% $b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+% and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
+Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
+% \begin{equation}
+% (\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
+% \end{equation}
+% where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
+% \begin{equation}\label{eq:diff_ver}
+% \partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
+% \end{equation}
+% where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
+
+% To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
+% \begin{equation}\label{eq:eos_fluid}
+% p = K \rho^{\Gamma},
+% \end{equation}
+% with $K$ and $\Gamma$ constants.
+%  By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\widetilde{\rho h} = \mathcal{L} (\rho h)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
+% \begin{eqnarray}
+% \label{eq:eos_mag_tilde}
+% \tilde{p}_{\mathrm{m}} &=& M \widetilde{\rho h}^q,
+% \\
+% p_{\mathrm{m}} &=& M \mathcal{L}^{q-1} (\rho h)^q,
+% \end{eqnarray}
+% where $M$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
+% \begin{equation}\label{eq:final}
+% W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0,
+% \end{equation}
+% where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and  $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
+
+% We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
+These are  given by
+% \begin{eqnarray}\label{eq:torus_energy_density}
+% \rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
+% \\
+% \rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+% \end{eqnarray}
+
+% %
+% %\begin{equation}\label{eq:torus_energy_density}
+% %\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
+% %\end{equation}
+% %and
+% %\begin{equation}\label{eq:SF_energy_density}
+% %\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+% %\end{equation}
+
+% From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
+In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
+Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
+With this information we can compute all relevant physical quantities.
+
+% \tf{We should discuss a bit more the reason for this choice.
+If $l_{\rm ms}<l<l_{\rm mb}$ and $r_{\rm mb}<r_{\rm cusp}<r_{\rm ms}$ the disk is closed and has a centre and a cusp.
+If $l=l_{\rm mb}$ and $r_{\rm cusp}=r_{\rm mb}$ the disk has a centre and a cusp, and it is closed at infinity.
+The models we have built are the latter, right?
+I wonder if we should have built models not completely filling their Roche lobe, so that they had a finite size.
+In any case, a comment must be provided here.}
+
+% \tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}
+
+% %%%%%%%%%%%%
+% \section{Methodology}
+% \label{procedure}
+% %%%%%%%%%%%%
+
+% \tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
+% poor now. It needs a lot of rewriting.}
+
+% %%%%%%%%%%%%%%%%
+% \subsection{Building the disks}
+% %%%%%%%%%%%%%%%%
+
+% To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
+This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
+Next, we can compute the gravitational plus centrifugal potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
+Considering this, and that we can write the magnetic pressure at the centre as
+% \begin{equation}
+% p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
+% \end{equation}
+% where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
+\tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
+% \begin{equation}\label{eq:K_eq}
+% W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
+% \end{equation}
+% Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
+With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
+
+% %%%%%%%%%%%%%%%%%
+% \subsection{Numerical method}
+% %%%%%%%%%%%%%%%%%
+
+% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
+Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
+
+% Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}
+
+% <<<<<<< HEAD
+% In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
 \tf{Describe this figure.}
 
-In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
+% In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
 The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
@@
 
-\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
+% \tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
 Is this correct?
@@
 
-\subsection{Comparison with KBHs}
-
-Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
-
-As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
+% \subsection{Comparison with KBHs}
+
+% Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+
+% As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
 Nevertheless, we show them for the sake of clarity.
@@
 
-%%%%%%%%%%%%%%%%%%
-\subsection{Magnetization profiles}
-%%%%%%%%%%%%%%%%%%
-
-The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+% %%%%%%%%%%%%%%%%%%
+% \subsection{Magnetization profiles}
+% %%%%%%%%%%%%%%%%%%
+
+% The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
 The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
@@
 
-Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+% Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
 The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
@@
 
-\sg{Include discussion about radial profiles.}
+% \sg{Include discussion about radial profiles.}
 
@@
 
+% \begin{table*}[t]
+% \caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH.
+For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
+\tf{Are we using the perimetral radial coordinate in this table?}}
+% \label{HBH_disk_parameters}      
+% \centering          
+% \begin{tabular}{c c c c c  c c c c c c c}
+% \hline\hline       
+%  Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+% \hline           
+% I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
+%  \hline 
+% II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
+%  \hline 
+% III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
+% \hline  
+% IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
+% \hline 
+%  &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
+% \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
+% \hline   
+% V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
+% \hline 
+%  &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
+% \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
+% \hline   
+% VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
+% \hline 
+%  &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
+% \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
+% \hline 
+% VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
+% \hline 
+%  &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
+% \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
+% \hline 
+% \end{tabular}
+% \end{table*}
+
+% \subsection{2D Morphology}
+
+% We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}.
+The radial coordinate in these figures is the standard one of the spherical coordinate system.
+% Figures~\ref{models_I} and~\ref{models_II} show the logarithm of the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
+
+% The structure of the disks is similar for all values of $\beta_{\mathrm{m_c}}$ with the only quantitative differences being the location of the centre of the disk, which moves closer to the BH as the magnetization increases, and the range of variation of the isodensity contours, whose upper ends become larger with decreasing $\beta_{\mathrm{m_c}}$.
+This behaviour is in complete agreement with that found for KBHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
+For the particular case of Model VII, the maximum of the rest-mass density for the stronlgy magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
+\tf{Can we use the last isodentity contour as a good measure of the size of the disk?}
+
+% In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$.
+\tf{We need to justify why we introduce this new radial coordinate.
+What is the benefit?
+Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.}
+
+% Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for our disk models around KBHsSH.
+First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
+As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1.
+This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$.
+The models V, VI and VII violate that bound.
+This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
+% \hspace{-0.2cm}
+% \\
+% \includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
+% \hspace{-0.2cm}
+% \caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
+From left to right the columns correspond to models I, IV, and VII.
+The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
+% \tf{I think there is a lot of vertical space that we do not really need in these plots.
+To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
+I know the plot will not look squared, but that's fine.}
+% }
+% \label{comparison_mass_density}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
+% \hspace{-0.4cm}
+% \includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
+% \hspace{-0.4cm}
+% \includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
+% \hspace{-0.2cm}
+% \\
+% \includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
+% \hspace{-0.4cm}
+% \includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
+% \hspace{-0.4cm}
+% \includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
+% \hspace{-0.2cm}
+% \caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
+\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
+% \label{comparison_mass_density_peri}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
+% \hspace{-0.cm}
+% \includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
+% \hspace{-0.cm}
+% \\
+% \includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
+% \hspace{-0.cm}
+% \includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
+% \hspace{-0.cm}
+% \caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
+In the first row, we show this for all of our KBHsSH models.
+In the second row, we show this for a sequence of KBHs with increasing spin parameter.\sg{fixed cases and labels.}}
+% \label{comparison_HBH_Kerr_dens_enth}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.2]{figures/fig8_HBH.eps}
+% \hspace{0.5cm}
+% \includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
+% \hspace{0.5cm}
+% \caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
+Left panel: KBHsSH models.
+Right panel: A sequence of KBHs with increasing spin parameter.\sg{fixed cases and labels.}}
+% \label{comparison_HBH_Kerr_r_m_max}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
+% \hspace{-0.2cm}
+% \caption{Rest-mass density distribution.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+% \label{models_Kerr}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
+% \\
+% \includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
+% \hspace{-0.3cm}
+% \includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
+% \hspace{-0.2cm}
+% \includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
+% \hspace{-0.2cm}
+% \caption{Rest-mass density distribution using perimeteral coordinates.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+% \label{models_Kerr_peri}
+% \end{figure*}
+
+% \begin{table*}[t]
+% \caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
+For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
+% \label{KBH_disk_parameters}      
+% \centering          
+% \begin{tabular}{c c c c c  c c c c c c c}
+% \hline\hline       
+%  $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+% \hline           
+% $0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
+%  \hline 
+%  $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
+% \hline  
+% $0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
+%  \hline 
+%  &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
+%  \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
+%  \hline 
+% $0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
+% \hline 
+%  &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
+% \hline 
+%  &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
+% \hline   
+% \end{tabular}
+% \end{table*}
+
+Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH.
+\sg{As in the KBHsSH case, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $\Delta W$ (in this case this also means increasing value of $a$).
+Also, it can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.} \tf{Describe.}
+
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
+\tf{Describe this figure.} \sg{Not sure if we need to describe both figures separately.
+Maybe we only need one of them.}
+
+In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
+The plots show that \sg{, for the non-magnetised cases,} the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+\tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}\sg{This trend disappears with increasing magnetisation, as the disc moves closer to the horizon.}
+
+\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
+Is this correct?
+Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field?
+Is this a valid approximation because we are in the test-fluid regime?
+What did~\cite{Vincent:2016} do?}
+\sg{They do the same as us.
+As we are considering the scalar field part of the spacetime (there is no interaction between the scalar field and the matter other than gravity) and we are in the test-fluid approximmation I think this is correct.}
+
+\subsection{Comparison with KBHs}
+
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+
+\sg{I am thinking about merging this section with the others.}
+
+\sg{Compare the radial profiles.}
+\sg{Describe and compare the angular velocity at the centre.}
+
+% As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
+Nevertheless, we show them for the sake of clarity.
+Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
+This idea is discussed in appendix~\ref{torus_embedding}.
+
+%%%%%%%%%%%%%%%%%%
+\subsection{Magnetization profiles}
+%%%%%%%%%%%%%%%%%%
+
+The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
+\tf{Maybe there is an excessive number of cases for KBHs.
+Maybe it's enough to only include the four cases we have in Table III.
+We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9.
+This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
+However, there are differences between the two cases.
+For the enthalpy, the values of $h_{\mathrm{max}}$ reached for the KBHsSH are much higher than those of the KBH case.
+This fact tells us that, while the $w = \rho h \simeq \rho$ approximation (see \cite{Komissarov:2006} and \cite{Gimeno-Soler:2017}) is valid for magnetized flows ($\beta_{\mathrm{m_c}} \sim 1$) for reasonable values of the spin parameter ($a \sim 0.99$ or lower), that is not the case for KBHsSH.
+Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
+
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
+As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.
+\sg{At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
+As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximmation to be valid in the non-magnetised regime.
+Now we can see that, in the KBHsSH case, this approximmation is not valid even for mildly-magnetised discs.}
+
+%%%%%%%%%%%%%%%%%%
+\subsection{Torus mass}
+%%%%%%%%%%%%%%%%%%
+
+\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the discs.
+For this case only, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+This is in agreement with the torus masses found as the final state of binary neutron stars mergers}
+
+\sg{I think here we should go further and do the following: First, choose a suitable maximum ADM mass for the KBHsSH (Eq~(I.1) of~\cite{Herdeiro:2016}), this implies a choice of scalar field mass $\mu$.
+This maximum mass should be such as our models ADM mass would be $\sim 2.5 M_{\odot}$.
+Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetisations and their Kerr ADM equivalents).
+Finally, we compute the cgs central densities with the formula (From the book of Rezzolla \emph{Relativistic Hydrodynamics})}
+\begin{equation}
+\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}
+\end{equation}
+\sg{and compare the central densities (or maximum) with known values.}
+
+%\begin{table}
+%\caption{List of models of KBHsSH.}        
+%\label{models_list}      
+%\centering          
+%\begin{tabular}{c c c c  c c c c}
+%\hline\hline       
+% Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
+%\hline           
+%I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
+% \hline 
+%II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
+% \hline 
+%III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
+% \hline 
+%IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
+% \hline 
+%V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
+% \hline 
+%VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
+% \hline 
+%VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
+%\hline      
+%\end{tabular}
+%\end{table}
+%
+%\begin{table}
+%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
+%\label{models_spin_vel}      
+%\centering          
+%\begin{tabular}{c c c c c}
+%\hline\hline       
+% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
+%\hline           
+%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
+% \hline 
+%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
+% \hline 
+%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
+% \hline 
+%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
+% \hline 
+%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
+% \hline 
+%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
+% \hline 
+%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
+%\hline      
+%\end{tabular}
+%\end{table}
+
 %%%%%%%%%%%%
@@
 \sg{I figured this out, but now I am not really sure if this is interesting enough to be an appendix by itself. Maybe more like a comment in the main text.}
+We start by considering the lagrangian of a stationary and axisymmetric spacetime
+\begin{equation}
+L = \frac{1}{2}\left(g_{tt} (\dot{t})^2 + 2 g_{t\phi} \dot{t}\dot{\phi} + g_{rr} (\dot{r})^2 + g_{\theta\theta} (\dot{\theta})^2 + g_{\phi\phi} (\dot{\phi})^2\right)\,
+\end{equation}
+where $\dot{x^{\alpha}} = \mathrm{d}x^{\alpha}/\mathrm{d}\lambda$ denotes the partial derivative of the coordinates with respect to an affine parameter $\lambda$.
+We can note that we have two cyclic coordinates ($t$ and $\phi$).
+Then, the canonically conjugate momentum of each coordinate is conserved, namely
+\begin{eqnarray}\label{eq:momenta}
+p_t = \frac{\partial L}{\partial \dot{t}} = -E
+\\
+p_{\phi} = \frac{\partial L}{\partial \dot{\phi}} = L\,
+\end{eqnarray}
+where we identify the constants of motion as the energy and angular momentum of a test particle.
+
+If we assume motion in the equatiorial plane (i.e.~$\theta = \pi/2$, $\dot{\theta} = 0$) we can write the relativistic four-momentum (of a massive particle) normalisation as
+\begin{equation}\label{eq:momenta_normalisation}
+p_{t}p^t + p_{r}p^r + p_{\phi}p^{\phi} = -m^2\,
+\end{equation}
+where $m$ is the mass of a test particle.
+Using the defintions of the energy and angular momentum of the particle and taking into account that $p^{\alpha} = \dot{x^{\alpha}}$, we can rewrite the above equation as
+\begin{equation}
+-E \dot{t} + L \dot{\phi} + g_{rr} \dot{r}^2 = -m^2.
+\end{equation}
+Now, we can find the expressions for the contravariant momenta $p^{t}$ and $p^{\phi}$ from $p_{\alpha} = g_{\alpha \beta}p^{\beta}$
+\begin{eqnarray}
+p^{t} = \frac{g_{\phi\phi}E + g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}
+\\
+p^{\phi} = -\frac{g_{tt}L+g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\,
+\end{eqnarray}
+now, we can replace these expressions into Eq.~\eqref{eq:momenta_normalisation} and write the expressión for the radial velocity $\dot{r}$
+\begin{equation}\label{eq:radial_velocity}
+\dot{r} = \left(-m^2+\frac{g_{\phi\phi}E^2+2 g_{t\phi}LE+g_{tt}L^2}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\right)^{\frac{1}{2}}.
+\end{equation}
+We want to consider circular orbits, so the radial velocity must be $\dot{r} = 0$. Then, we arrive at
+\begin{equation}
+g_{t\phi}^2-g_{tt}g_{\phi\phi} = g_{\phi\phi}e^2+2 g_{t\phi}le+g_{tt}l^2\,
+\end{equation}
+where we have introduced the specific energy per unit mass ($e = E/m$) and the specific angular momentum per unit mass ($l = L/m$).
+Additionally, we are interested in bound orbits.
+Specifically, we want marginally bound orbits ($e=1$).
+Taking this into account, we get the following expression for the specific angular momentum
+\begin{equation}\label{eq:bound_ang_mom}
+l^{\pm}_{\mathrm{b}} = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,
+\end{equation}
+which corresponds to Eq.~\eqref{eq:mb_ang_mom}.
+It is well-known that in black hole spacetimes there is an innermost circular marginally bound orbit for test particles.
+Naturally, a marginally bound particle at the innermost circular orbit has to have the smallest possible value of the specific angular momentum (i.e.~a minimum of Eq.~\eqref{eq:bound_ang_mom}).
+The radial location of said minimum is, obviously, the innermost circular marginally bound radius $r_{\mathrm{mb}}$.
 \end{appendix}

### 2018-11-06 paper_prd.tex
reference and comment on the original grid

@@
 For that reason, we use a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$.
-This means a radial resolution of $\simeq 0.001$ at the location of the disc centre.
+This grid is an interpolated version of the original data, obtained as a result by~\cite{Herdeiro:2015b}.
+The original grid is a uniform grid ($x$, $\theta$) (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$\footnote{Some samples are presented in~\cite{grav_web}}.
+To obtain our grid, we use the coordinate change provided in~\cite{grav_web} and interpolate the initial grid with order 3 splines.
 \sg{This is a rough approximmation, as this exact number depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.

### 2018-11-07 paper_prd.tex
Some work.

@@
 In this investigation we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case, whose sequences have already been computed.
-The dynamical stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
+The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
 
@@
 
-The KBHsSH models we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
+The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
 The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity.
@@
 \end{eqnarray}
-with $N = 1 - r_H/r$, where $r_H$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
+with $N = 1 - r_{\rm H}/r$, where $r_{\rm H}$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
 Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
@@
 Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a hairy Kerr BH with almost all the mass and angular momentum stored in the scalar field.
-It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than 1) in terms of both ADM or horizon quantities.
-This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds $1$.
+It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than unity) in terms of both ADM or horizon quantities.
+This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds the speed of light.
 For comparison, we also show in the last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.

### 2018-11-07 paper_prd.tex
More work.

@@
 From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
-The range of the colour scale is not the same for all plots.
-\tf{Perhaps it would be good to include in the upper left corner of each plot a legend indicating the model (e.g. Model I) and the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$.}\sg{Done.}
-}
+Note that the range of the colour scale is not the same for all plots.}
 \label{models_I}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII). \tf{Same comment as in the previous figure.}\sg{Done.}}
+\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII).}
 \label{models_II}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}\sg{Done.}}
+\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$.}
 \label{models_peri_I}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$. \tf{Same comment as in the previous figure.}\sg{Done.}}
+\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$.}
 \label{models_peri_II}
@@
 The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
-In this work, for simplicity and to reduce the ample space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
+In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
 This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
-\tf{We should explain/motivate why we change our approach in this paper.}\sg{We limit this study to the constant angular momentum case to limit the parameter space, as the main aim of this paper is to study the dependence of the characteristics of magnetised discs with respect to the KBHSH spacetime.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
+Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
 \begin{equation}\label{eq:mb_ang_mom}
-l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}
+l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,,
 \end{equation}
@@
 We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
-\tf{Is there an Appendix A?}.\sg{Yes.
-Please, read Appendix A}.
 
@@
 \label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} &=& M \tilde{w}^q,
-\\
-p_{\mathrm{m}} &=& M \mathcal{L}^{q-1} (\rho h)^q,
+\tilde{p}_{\mathrm{m}} &=& K_{\rm m} \tilde{w}^q,
+\\
+p_{\mathrm{m}} &=& K_{\rm m} \mathcal{L}^{q-1} (\rho h)^q,
 \end{eqnarray}
-where $M$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
+where $K_{\rm m}$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
 \begin{equation}\label{eq:final}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0,
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0,
 \end{equation}
@@
 \begin{equation}\label{eq:mass_integral}
-\mathcal{M} = \int  \rho \sqrt{-g}\mathrm{d}^3x\,
-\end{equation}
-where $g$ is the determinant of the metric tensor.
-%
-%\begin{equation}\label{eq:torus_energy_density}
-%\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
-%\end{equation}
-%and
-%\begin{equation}\label{eq:SF_energy_density}
-%\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
-%\end{equation}
-
-\tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$.
-This is an important difference with respect to the work of~\cite{Vincent:2016}.} \sg{As a concluding remark, it is worth to note that we are taking a different approach to construct the magnetised discs than the standard one~\citep{Komissarov:2006} (this approach was also taken by~\cite{Vincent:2016} for discs around the same kind of KBHsSH we have in this work).
-As it is noted in~\cite{Gimeno-Soler:2017}, this approach considers implicitly assumes that the specific enthalpy is close to $1$ ($w = \rho h \simeq \rho$).
-This means that the polytropic equation Eq.~\eqref{eq:eos_fluid} can be written as $p = K w^{\Gamma}$ (see Eq.~(27) of~\cite{Komissarov:2006}).
-To better understand the differences between this two approaches, we can consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
-For the non-magnetised case, we can rewrite Eq.~\eqref{eq:final} in the limiting case of $\beta_{\mathrm{m_c}} \rightarrow \infty$ ($M \rightarrow 0$) as
+\mathcal{M} = \int  \rho \sqrt{-g}\,\mathrm{d}^3x\,,
+\end{equation}
+where $g$ is the determinant of the metric tensor and $\rho\equiv \rho_{\mathrm{T}}, \rho_{\mathrm{SF}}$.
+
+In this work we take an approach to construct the magnetized disks different to the one proposed by~\citep{Komissarov:2006} and used by~\cite{Vincent:2016} for building disks around KBHsSH.
+As noted by~\cite{Gimeno-Soler:2017}, the approach of~\citep{Komissarov:2006} implicitly assumes that the specific enthalpy of the fluid is close to unity ($w = \rho h \simeq \rho$).
+This means that the polytropic EOS Eq.~\eqref{eq:eos_fluid} can be written as $p = K w^{\Gamma}$ (see Eq.~(27) of~\cite{Komissarov:2006}).
+We do not make this assumption here.
+To better understand the differences between these two approaches, we consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
+
+For the former, we can rewrite Eq.~\eqref{eq:final} in the limiting case of $\beta_{\mathrm{m_c}} \rightarrow \infty$ ($K_{\rm m} \rightarrow 0$) as
 \begin{equation}
@@
 \end{equation}
-Then, we can solve this equation for the specific enthalpy $h$
+Then, we can solve this equation for the specific enthalpy
 \begin{equation}\label{eq:rel_non_mag_enth}
@@
 \end{equation}
-If we compare both results, we can see that Eq.~\eqref{eq:non_rel_non_mag_enth} is the first order Taylor series expansion of Eq.~\eqref{eq:rel_non_mag_enth} for a sufficiently small value of $W_{\mathrm{in}} - W$.
-For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
+If we compare both results, we can see that Eq.~\eqref{eq:non_rel_non_mag_enth} is the first-order Taylor series expansion of Eq.~\eqref{eq:rel_non_mag_enth} for a sufficiently small value of $W_{\mathrm{in}} - W$.
+
+For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time around we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
 This yields the same result for both equations
 \begin{equation}
-W - W_{\mathrm{in}} + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0.
+W - W_{\mathrm{in}} + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0.
 \end{equation}
 In addition, we could consider the expression for the specific enthalpy in terms of the density $h = 1 + \frac{K\Gamma\rho^{\Gamma-1}}{\Gamma - 1}$ to 
-see that we will have $h \rightarrow 1$. This shows that, for the extremely magnetised limit, this two approaches coincide.
-In conclusion, taking into account this two limits of both approaches we can discuss the range of validity of the $h \simeq 1$ approximmation: As magnetised discs exist between the two considered cases, for discs with a sufficiently small value of the potential well $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$, we can use the $h \simeq 1$ approximmation without fear.
-On the other hand, if the value of $\Delta W$ is large enough, the approximmation could fail even for fairly small magnetised discs.}
+see that we will have $h \rightarrow 1$. This shows that, for the extremely magnetised limit, the two approaches coincide.
+
+Taking into account these two limits we can obtain the range of validity of the $h \simeq 1$ approximation: As magnetised disks exist between the two considered cases, for disks with a sufficiently small value of the potential well, $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$, the $h \simeq 1$ approximation is valid.
+On the contrary, if the value of $\Delta W$ is large enough, the approximation does not hold even for disks with a fairly low value of magnetisation.
+
 %%%%%%%%%%%%
@@
 
-From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
-Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
-With this information we can compute all relevant physical quantities.\sg{I have moved this paragraph from the above section to this one as I find it fits more naturally here.}
-\tf{We should discuss a bit more the reason for this choice.
-If $l_{\rm ms}<l<l_{\rm mb}$ and $r_{\rm mb}<r_{\rm cusp}<r_{\rm ms}$ the disk is closed and has a centre and a cusp.
-If $l=l_{\rm mb}$ and $r_{\rm cusp}=r_{\rm mb}$ the disk has a centre and a cusp, and it is closed at infinity.
-The models we have built are the latter, right?
-I wonder if we should have built models not completely filling their Roche lobe, so that they had a finite size.
-In any case, a comment must be provided here.}
-\sg{We choose this value for the angular momentum and the inner radius of the disc to allow discs with a cusp and a centre that also are marginally stable (a small perturbation can trigger accretion into the black hole).
-Also, the thermodynamical quantities reach its maximum for this particular choice of angular momentum and inner radius of the disc (as they are related to the total potential well $|\Delta W|$).
-This also means that the resulting discs will be semi-infinite (they are closed at infinity), this is not a source of concern, as the external layers of the disc have extremely low density.
-(not sure about the relevance of the last part...)}
-In particular, this choice of specific angular momentum distribution and inner radius of the disc is taken to allow discs with a cusp and a centre that also are marginally stable (a small perturbation can trigger accretion into the black hole).
-In addition, the thermodynamical quantities reach their maximum for this particular choice of parameters (as they are related to the total potential well $|\Delta W|$) \sg{I am not sure if this needs further explanation}.) This also means that the resulting discs will be semi-infinite (they are closed at infinity) but this is not a source of concern, as the external layers of the disc have extremely low density and, at some point, the value will be lower than the density of the atmosphere.
-
-Before starting to build the disc, it is important to note that we need a sufficiently fine numerical grid in order to fully capture the behaviour of the physical magnitudes at the inner region of the disc.
-For that reason, we use a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$.
-This grid is an interpolated version of the original data, obtained as a result by~\cite{Herdeiro:2015b}.
-The original grid is a uniform grid ($x$, $\theta$) (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$\footnote{Some samples are presented in~\cite{grav_web}}.
-To obtain our grid, we use the coordinate change provided in~\cite{grav_web} and interpolate the initial grid with order 3 splines.
-\sg{This is a rough approximmation, as this exact number depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.
-Nevertheless, the value of the resolution is much better at the cusp, specially if the disk is very close to the horizon (for instance in the $a = 0.9999$ Kerr case).
-Maybe we should clarify this, as these high spin cases need a very high radial resolution.
-Also, it may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots).
-But I think this should go in the results section.} \sg{I am not sure if we have to tell something about the \it{real} initial data} (i.e.
-the data provided by Carlos).
+We now turn to describe the numerical methodology to build the disks.
+From the discussion in the preceding section it becomes apparent that the number of parameters defining the disk models is fairly large.
+In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
+Thus, we leave the magnetization at the centre, $\beta_{\mathrm{m_c}}$, as the only free parameter for each model of KBHsSH.
+With this information we can compute all relevant physical quantities.
+
+In particular, our choice of specific angular momentum and inner radius is made to allow disks to have a cusp and a centre.
+These disks are marginally stable, as they completely fill their Roche lobe, and a small perturbation can trigger accretion onto the BH.
+In addition, the thermodynamical quantities of the disks reach their maxima for this particular choice of parameters, as they are related to the total potential well $|\Delta W|$.
+Our choice also implies that the resulting disks will be semi-infinite (they are closed at infinity) but this is not a source of concern, as the external layers of the disk have extremely low density.
+
+Before building the models, it is important to note that we need a sufficiently fine numerical grid to fully capture the behaviour of the physical magnitudes at the innermost regions of the disk.
+For this reason, we use a non-uniform $(r, \theta)$ grid with a typical domain given by $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$.
+Those numbers are lower limits as they depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.
+The spacetime metric data on this grid is interpolated from the original data obtained by~\cite{Herdeiro:2015b}.
+The original grid in~\cite{Herdeiro:2015b} is a uniform ($x$, $\theta$) grid (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$\footnote{Some samples are presented in~\cite{grav_web}}.
+To obtain our grid, we use the coordinate transformation provided in~\cite{grav_web} and interpolate the initial grid using cubic splines interpolation.
+An example of our grid is shown in Fig.~XXX.
+\tf{We will include this figure if it could be done and were meaningful.} \tf{Maybe we could also provide the number of the domain and number of points we need for our most extreme case with $a = 0.9999$.}
+
+\sg{It may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots).
+But I think this should go in the results section.} \tf{I agree with mentioning this in the results section.}
+
 Next, we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively.

### 2018-11-07 paper_prd.tex
More work.

@@
 \centering
+\includegraphics[scale=0.37]{figures/radial_log_rho_model_I.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.37]{figures/radial_log_rho_model_IV.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.37]{figures/radial_log_rho_model_VII.pdf}
+\hspace{-0.6cm}
+\caption{Size of the disks.
+Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
+From left to right we show model I, IV, and VII, respectively.}
+\label{radial_profiles_HBH}
+\end{figure*}
+
+\begin{figure*}
+\centering
 \includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
@@
 %%%%%%%%%%%%
-\sg{This whole section is rewritten.}
-
-\tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
-poor now. It needs a lot of rewriting.}
-\sg{I have serious doubts about this section, as I am not really certain that we need to provide an explanation for some specific parts (that are pretty obvious anyway) Perhaps I should go into detail for the numerical part?
-(e.g.
-that Eq.~\eqref{eq:final} is a trascendental equation and we are bound to solve it numerically with the bisection method for each cell of our numerical grid)}
 
@@
 Before building the models, it is important to note that we need a sufficiently fine numerical grid to fully capture the behaviour of the physical magnitudes at the innermost regions of the disk.
-For this reason, we use a non-uniform $(r, \theta)$ grid with a typical domain given by $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_{\theta} = 2500 \times 300$.
-Those numbers are lower limits as they depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.
+For this reason, we use a non-uniform $(r, \theta)$ grid with a typical domain given by $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a typical number of points $N_r \times N_{\theta} = 2500 \times 300$.
+Those numbers are only representative as the actual numbers depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model.
 The spacetime metric data on this grid is interpolated from the original data obtained by~\cite{Herdeiro:2015b}.
-The original grid in~\cite{Herdeiro:2015b} is a uniform ($x$, $\theta$) grid (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$\footnote{Some samples are presented in~\cite{grav_web}}.
+The original grid in~\cite{Herdeiro:2015b} is a uniform ($x$, $\theta$) grid (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$~\footnote{Some samples are presented in~\cite{grav_web}}.
 To obtain our grid, we use the coordinate transformation provided in~\cite{grav_web} and interpolate the initial grid using cubic splines interpolation.
@@
 
-Next, we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively.
-Once we have that, we can compute the total potential distribution as
+To build the disks we first need to find $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$ as the minimum of Eq.~\eqref{eq:mb_ang_mom} and the location of said minimum in terms of the radial coordinate respectively.
+Once this is done, we can compute the total potential distribution as
 \begin{equation}
@@
 For our choice of angular momentum distribution, this also means $W_{\mathrm{in}} = 0$.
-Having now the total potential distribution and the characteristic radii of the disc, we can start to compute the thermodynamical quantities in the disc.
-First of all, we compute the polytropic constant $K$ evaluating Eq.~\eqref{eq:final} at the centre
-\begin{equation}\label{eq:to_solve_K}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) + \frac{q}{q-1} \frac{K\rho_{\mathrm{c}}^{\Gamma}}{\beta_{\mathrm{m_c}} (\rho_{\mathrm{c}} + \frac{K\Gamma\rho_{\mathrm{c}}^{\Gamma}}{\Gamma-1})} =0\,
-\end{equation}
+Having the total potential distribution and the characteristic radii of the disk, we can start to compute the thermodynamical quantities in the disk.
+First of all, we compute the polytropic constant $K$ by evaluating Eq.~\eqref{eq:final} at the centre
+%\begin{equation}
+\begin{multline}
+\label{eq:to_solve_K}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) 
+\\
++ \frac{q}{q-1} \frac{K\rho_{\mathrm{c}}^{\Gamma}}{\beta_{\mathrm{m_c}} \left(\rho_{\mathrm{c}} + \frac{K\Gamma\rho_{\mathrm{c}}^{\Gamma}}{\Gamma-1}\right)} =0\,,
+\end{multline}
+%\end{equation}
 where we have used the definition of magnetic pressure and the definition of the magnetisation parameter $\beta$.
-Using its corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $M$.
-With both $K$ and $M$ obtained, we can now compute the thermodynamical quantities in all our numerical domain.
+Using their corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $K_{\rm m}$.
+With both $K$ and $K_{\rm m}$ obtained, we can now compute the thermodynamical quantities in all our numerical domain.
 For points with $W(r, \theta) > 0$ we set $\rho = p = p_{\mathrm{m}} = 0$ and for points with $W_{\mathrm{c}} < W(r, \theta) < 0$, we write Eq.~\eqref{eq:final} as
-\begin{equation}\label{eq:to_solve_rho}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}(\rho + \frac{K\Gamma \rho^{\Gamma}}{\Gamma - 1}))^{q-1}=0,\,
-\end{equation}
+%\begin{equation}
+\begin{multline}
+\label{eq:to_solve_rho}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) 
+\\
++ \frac{q}{q-1}K_{\rm m}\left(\mathcal{L}\left(\rho + \frac{K\Gamma \rho^{\Gamma}}{\Gamma - 1}\right)\right)^{q-1}=0\,,
+\end{multline}
+%\end{equation}
 to compute the rest-mass density $\rho$ of said point.
@@
 
-It is relevant to note that Eqs.~\eqref{eq:to_solve_K} and~\eqref{eq:to_solve_rho} are trascendental equations and that, particularly Eq.~\eqref{eq:to_solve_rho} must be solved at each point of our numerical grid.
+It is relevant to note that Eqs.~\eqref{eq:to_solve_K} and~\eqref{eq:to_solve_rho} are trascendental equations and that Eq.~\eqref{eq:to_solve_rho} in particular must be solved at each point of our numerical grid.
 To solve these equations we use the bisection method.
 To ensure the accuracy of our computations (particularly the accuracy of the maximum and central quantities we report) we choose our grid to have a difference between two adjacent points of $\Delta r (r \simeq r_{\mathrm{c}}) \simeq 0.001$ in the equatorial plane.
-
-% %%%%%%%%%%%%%%%%
-% \subsection{Building the disks}
-% %%%%%%%%%%%%%%%%
-
-% To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
-This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
-Next, we can compute the gravitational plus centrifugal potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
-Considering this, and that we can write the magnetic pressure at the centre as
-% \begin{equation}
-% p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
-% \end{equation}
-% where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
-\tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
-% \begin{equation}\label{eq:K_eq}
-% W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
-% \end{equation}
-% Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
-With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
 
@@
 
-%In table~\ref{models_list} we show the different KBHsSH models we will use.
-As it can be seen, the models go from a Kerr-like model (almost all the mass and angular momentum are stored in BH) to a KBHSH with almost all the mass and angular momentum stored in the scalar field.
-It is also worth mentioning that, as shown in table~\ref{models_spin_vel} some of the models violate the Kerr bound (in terms of ADM or horizon quantities).
-This is not worrying because, as shown in~\cite{Herdeiro:2015c} the horizon linear velocity $v_{\mathrm{H}}$ never exceed $1$.
-For comparison, we also show the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with horizon linear velocity $v_{\mathrm{H}}$.
-
 \begin{table*}[t]
-\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH.
-For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
-\tf{Are we using the perimetral radial coordinate in this table?}\sg{Yes.}}
+\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH. For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.}       
 \label{HBH_disk_parameters}      
@@
 \hline           
-I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
+I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.00$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
- \hline 
-II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
+ \hline 
+II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.00$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
- \hline 
-III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
+ \hline 
+III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.00$ & $1.09 \times 10^{-1}$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
-\hline  
-IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
-\hline   
-V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
-\hline 
- &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
-\hline   
-VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
-\hline 
-VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
-\hline 
- &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
+\hline  
+IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.72$ & $1.00$ & $1.82\times 10^{-1}$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.38$ & $1.37$ & $1.29 \times 10^{-1}$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
+\hline   
+V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.00$ & $2.46 \times 10^{-1}$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
+\hline 
+ &  &  &  &  & $1$ & $1.51$ & $1.40$ & $1.78 \times 10^{-1}$ & $0.132$ & $0.78$ & $0.87$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $4.26$ & $1.18 \times 10^{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
+\hline   
+VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.00$ & $3.24 \times 10^{-1}$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.66$ & $1.39$ & $2.28 \times 10^{-1}$ & $0.169$ & $0.72$ & $0.86$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
+\hline 
+VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.00$ & $6.10 \times 10^{-1}$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $2.25$ & $1.64$ & $5.10 \times 10^{-1}$ & $0.322$ & $0.43$ & $0.62$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
 \hline 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.38]{figures/radial_log_rho_model_I.pdf}
-\hspace{-0.6cm}
-\includegraphics[scale=0.38]{figures/radial_log_rho_model_IV.pdf}
-\hspace{-0.6cm}
-\includegraphics[scale=0.38]{figures/radial_log_rho_model_VII.pdf}
-\hspace{-0.6cm}
-\caption{Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
-In each panel there are .
-Left panel: Model I.
-Central panel: Model IV.
-Right panel: Model VII.}
-\label{radial_profiles_HBH}
-\end{figure*}
-
+%%%%%%%%%%%%%%%
 \subsection{2D Morphology}
+%%%%%%%%%%%%%%%
 
 We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}.
-The radial coordinate in these figures is the standard one of the spherical coordinate system.
+The radial coordinate employed in these figures is the standard one of the spherical coordinate system.
 Figures~\ref{models_I} and~\ref{models_II} show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
@@
 For the particular case of Model VII, the maximum of the rest-mass density for the strongly magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
-\tf{Can we use the last isodentity contour as a good measure of the size of the disk?} \sg{In figure~\ref{radial_profiles_HBH}, we can visualise the radial extent for the models I, IV and VII with three different values of the magnetisation ($10^{10}$, $1$, and $10^{-10}$).
-As it can be seen, model I discs are significantly bigger than their model IV and VII counterparts.
-Also, it is important to note the presence of a thicker region of high density in the model VII non-magnetised case (the mildly-magnetised case also has it, but to a lesser extent).
-This could be related to the existence of an extra gravitational well that overlaps with the disc (as it can be seen in the right panel of figure~\ref{comparison_mass_density}).}
-
-In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$.
+
+The size of the disks can be best quantified by plotting the radial profiles of the rest-mass density on the equatorial plane.
+This is shown in Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetisation parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
+From this figure we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller they become.
+We also note the presence of an extended region of high density in the unmagnetized model VII  (the mildly-magnetised case also shows this feature but to a lesser extent).
+This could be related to the existence of an extra gravitational well due to the scalar field distribution that overlaps with the matter distribution of the disk (as can be seen in the right panel of Fig.~\ref{comparison_mass_density} below).
+
+In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the Boyer-Lindquist radial coordinate according to $R = e^{F_2} r$.
 \tf{We need to justify why we introduce this new radial coordinate.
@@
 I suppose this could help us to compare different models.
-In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).}
-
-Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for our disk models around KBHsSH.
+In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you then please include some of this information in this paragraph?}
+
+Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for all of our disk models around KBHsSH.
 First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
@@
 
-Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH.
-\sg{As in the KBHsSH case, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $\Delta W$ (in this case this also means increasing value of $a$).
-Also, it can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.} \tf{Describe.}
-
 In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
@@
 
+%%%%%%%%%%%%%%%%%%%
 \subsection{Comparison with KBHs}
+%%%%%%%%%%%%%%%%%%%
+
+Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH.
+\sg{As in the KBHsSH case, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $\Delta W$ (in this case this also means increasing value of $a$).
+Also, it can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.} \tf{Describe.}
 

### 2018-11-07 paper_prd.tex
More work on the draft.

@@
 Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
+We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
 
@@
 \end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Distribution of angular momentum in the disk}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein).
+For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
+
+We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
+\begin{equation}
+l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
+\end{equation}
+where $u^{\mu}$ is the fluid four-velocity.
+The relationship between $l$ and $\Omega$ is given by the equations
+\begin{equation}
+l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
+\end{equation}
+where we are assuming circular motion, i.e.~the four-velocity can be written as
+\begin{equation}
+u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
+\end{equation}
+
+The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
+In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
+This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
+Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
+\begin{equation}\label{eq:mb_ang_mom}
+l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,,
+\end{equation}
+where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
+Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
+Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
+For prograde motion, the function has a minimum outside the event horizon.
+The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
+We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
+
+%%%%%%%%%%%%%%%%
+\subsection{Magnetized disks}
+%%%%%%%%%%%%%%%%
+
+To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
+First, we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
+$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
+where $\nabla_{\mu}$ is the covariant derivative and
+\begin{equation}\label{eq:e-m_tensor}
+T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
+\end{equation}
+is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
+The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
+Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
+four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
+$b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
+and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
+Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
+\begin{equation}
+(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
+\end{equation}
+where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
+\begin{equation}\label{eq:diff_ver}
+\partial_i(|\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
+\end{equation}
+where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
+
+To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
+\begin{equation}\label{eq:eos_fluid}
+p = K \rho^{\Gamma},
+\end{equation}
+with $K$ and $\Gamma$ constants.
+ By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$, $w = \rho h$ and $\tilde{w} = \mathcal{L} (w)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
+\begin{eqnarray}
+\label{eq:eos_mag_tilde}
+\tilde{p}_{\mathrm{m}} &=& K_{\rm m} \tilde{w}^q,
+\\
+p_{\mathrm{m}} &=& K_{\rm m} \mathcal{L}^{q-1} (\rho h)^q,
+\end{eqnarray}
+where $K_{\rm m}$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
+\begin{equation}\label{eq:final}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0,
+\end{equation}
+where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
+
+We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
+These are given by
+\begin{eqnarray}\label{eq:torus_energy_density}
+\rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
+\\
+\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{-2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+\end{eqnarray}
+Using these expressions, we can compute the total gravitational mass of the torus and the scalar field as the following expression
+\begin{equation}\label{eq:mass_integral}
+\mathcal{M} = \int  \rho \sqrt{-g}\,\mathrm{d}^3x\,,
+\end{equation}
+where $g$ is the determinant of the metric tensor and $\rho\equiv \rho_{\mathrm{T}}, \rho_{\mathrm{SF}}$.
+
+In this work we take an approach to construct the magnetized disks different to the one proposed by~\citep{Komissarov:2006} and used by~\cite{Vincent:2016} for building disks around KBHsSH.
+As noted by~\cite{Gimeno-Soler:2017}, the approach of~\citep{Komissarov:2006} implicitly assumes that the specific enthalpy of the fluid is close to unity ($w = \rho h \simeq \rho$).
+This means that the polytropic EOS Eq.~\eqref{eq:eos_fluid} can be written as $p = K w^{\Gamma}$ (see Eq.~(27) of~\cite{Komissarov:2006}).
+We do not make this assumption here.
+To better understand the differences between these two approaches, we consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
+
+For the former, we can rewrite Eq.~\eqref{eq:final} in the limiting case of $\beta_{\mathrm{m_c}} \rightarrow \infty$ ($K_{\rm m} \rightarrow 0$) as
+\begin{equation}
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) = 0.
+\end{equation}
+Then, we can solve this equation for the specific enthalpy
+\begin{equation}\label{eq:rel_non_mag_enth}
+h = e^{W_{\mathrm{in}} - W}.
+\end{equation}
+Now, we want to obtain an analogous equation for the $h \simeq 1$ case.
+We start by considering Eq.~(20) of~\cite{Gimeno-Soler:2017} and taking the limit $\beta_{\mathrm{m_c}} \rightarrow \infty$ (in this equation, this means $K_{\mathrm{m}} \rightarrow 0$), to obtain
+\begin{equation}
+W - W_{\mathrm{in}} + \frac{\Gamma K}{\Gamma +1}w^{\Gamma -1}.
+\end{equation}
+If we consider the $h \simeq 1$ approximmation, we can use the definition of $h$ and solve the equation to arrive at
+\begin{equation}\label{eq:non_rel_non_mag_enth}
+h = 1 + (W_{\mathrm{in}} - W).
+\end{equation}
+If we compare both results, we can see that Eq.~\eqref{eq:non_rel_non_mag_enth} is the first-order Taylor series expansion of Eq.~\eqref{eq:rel_non_mag_enth} for a sufficiently small value of $W_{\mathrm{in}} - W$.
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
-\hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$.}
-\label{models_peri_I}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$.}
-\label{models_peri_II}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Distribution of angular momentum in the disk}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein).
-For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
-
-We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
-\begin{equation}
-l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
-\end{equation}
-where $u^{\mu}$ is the fluid four-velocity.
-The relationship between $l$ and $\Omega$ is given by the equations
-\begin{equation}
-l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
-\end{equation}
-where we are assuming circular motion, i.e.~the four-velocity can be written as
-\begin{equation}
-u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
-\end{equation}
-
-The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
-In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
-This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
-Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
-\begin{equation}\label{eq:mb_ang_mom}
-l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,,
-\end{equation}
-where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
-Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
-Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
-For prograde motion, the function has a minimum outside the event horizon.
-The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
-We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
-
-%%%%%%%%%%%%%%%%
-\subsection{Magnetized disks}
-%%%%%%%%%%%%%%%%
-
-To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
-First, we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
-$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
-where $\nabla_{\mu}$ is the covariant derivative and
-\begin{equation}\label{eq:e-m_tensor}
-T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
-\end{equation}
-is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
-The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
-Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
-four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-$b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
-and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
-Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
-\begin{equation}
-(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
-\end{equation}
-where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
-\begin{equation}\label{eq:diff_ver}
-\partial_i(|\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
-\end{equation}
-where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
-
-To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
-\begin{equation}\label{eq:eos_fluid}
-p = K \rho^{\Gamma},
-\end{equation}
-with $K$ and $\Gamma$ constants.
- By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$, $w = \rho h$ and $\tilde{w} = \mathcal{L} (w)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
-\begin{eqnarray}
-\label{eq:eos_mag_tilde}
-\tilde{p}_{\mathrm{m}} &=& K_{\rm m} \tilde{w}^q,
-\\
-p_{\mathrm{m}} &=& K_{\rm m} \mathcal{L}^{q-1} (\rho h)^q,
-\end{eqnarray}
-where $K_{\rm m}$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
-\begin{equation}\label{eq:final}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0,
-\end{equation}
-where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
-
-We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
-These are given by
-\begin{eqnarray}\label{eq:torus_energy_density}
-\rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
-\\
-\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{-2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
-\end{eqnarray}
-Using these expressions, we can compute the total gravitational mass of the torus and the scalar field as the following expression
-\begin{equation}\label{eq:mass_integral}
-\mathcal{M} = \int  \rho \sqrt{-g}\,\mathrm{d}^3x\,,
-\end{equation}
-where $g$ is the determinant of the metric tensor and $\rho\equiv \rho_{\mathrm{T}}, \rho_{\mathrm{SF}}$.
-
-In this work we take an approach to construct the magnetized disks different to the one proposed by~\citep{Komissarov:2006} and used by~\cite{Vincent:2016} for building disks around KBHsSH.
-As noted by~\cite{Gimeno-Soler:2017}, the approach of~\citep{Komissarov:2006} implicitly assumes that the specific enthalpy of the fluid is close to unity ($w = \rho h \simeq \rho$).
-This means that the polytropic EOS Eq.~\eqref{eq:eos_fluid} can be written as $p = K w^{\Gamma}$ (see Eq.~(27) of~\cite{Komissarov:2006}).
-We do not make this assumption here.
-To better understand the differences between these two approaches, we consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
-
-For the former, we can rewrite Eq.~\eqref{eq:final} in the limiting case of $\beta_{\mathrm{m_c}} \rightarrow \infty$ ($K_{\rm m} \rightarrow 0$) as
-\begin{equation}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) = 0.
-\end{equation}
-Then, we can solve this equation for the specific enthalpy
-\begin{equation}\label{eq:rel_non_mag_enth}
-h = e^{W_{\mathrm{in}} - W}.
-\end{equation}
-Now, we want to obtain an analogous equation for the $h \simeq 1$ case.
-We start by considering Eq.~(20) of~\cite{Gimeno-Soler:2017} and taking the limit $\beta_{\mathrm{m_c}} \rightarrow \infty$ (in this equation, this means $K_{\mathrm{m}} \rightarrow 0$), to obtain
-\begin{equation}
-W - W_{\mathrm{in}} + \frac{\Gamma K}{\Gamma +1}w^{\Gamma -1}.
-\end{equation}
-If we consider the $h \simeq 1$ approximmation, we can use the definition of $h$ and solve the equation to arrive at
-\begin{equation}\label{eq:non_rel_non_mag_enth}
-h = 1 + (W_{\mathrm{in}} - W).
-\end{equation}
-If we compare both results, we can see that Eq.~\eqref{eq:non_rel_non_mag_enth} is the first-order Taylor series expansion of Eq.~\eqref{eq:rel_non_mag_enth} for a sufficiently small value of $W_{\mathrm{in}} - W$.
-
 For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time around we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
@@
 On the contrary, if the value of $\Delta W$ is large enough, the approximation does not hold even for disks with a fairly low value of magnetisation.
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
+\hspace{-0.2cm}
+\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$.}
+\label{models_peri_I}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$.}
+\label{models_peri_II}
+\end{figure*}
 
@@
 
-% %%%%%%%%%%%%%%%%%
-% \subsection{Numerical method}
-% %%%%%%%%%%%%%%%%%
-
-% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
-Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
-
 %%%%%%%%%%
@@
 Figures~\ref{models_I} and~\ref{models_II} show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.1267]{figures/fig5_I_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.1267]{figures/fig5_VII_10.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.1267]{figures/fig5_I__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.1267]{figures/fig5_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
+From left to right the columns correspond to models I, IV, and VII.
+The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).}
+\label{comparison_mass_density}
+\end{figure*}
 
@@
 
-In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the Boyer-Lindquist radial coordinate according to $R = e^{F_2} r$.
-\tf{We need to justify why we introduce this new radial coordinate.
-What is the benefit?
-Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.} \sg{Discuss.
-I find that the 2D morphology in perimeteral coordintes might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$.
+In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the radial coordinate $r$ according to $R = e^{F_2} r$.
+This perimetral coordinate represents the proper length along the azimuthal direction, which constitutes a geometrically meaningful direction since it runs along the orbits of the azimuthal Killing vector field.
+Therefore, the proper size of a full $\phi$ orbit is given by $2\pi R$, i.e.~$R$ is the perimetral radius.
+The most salient feature of the morphologies shown in Figs.~\ref{models_peri_I} and~\ref{models_peri_II}, when comparing to those displayed in Figs.~\ref{models_I} and~\ref{models_II}, is the deformation of the disks in their innermost regions.
+In general, the deformations become larger the higher the BH spin and the closer the disk is to the horizon.
+Model III is the one showing the largest deformation, as $R_{\rm in}-R_{\rm H}$ attains the smallest value for this model.
+\tf{Check.} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate.
+While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimetral coordinate $R$ is not always so.
+Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III.
+\tf{Check.}
+
+\sg{Discuss.
+I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$.
 I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass).
 I suppose this could help us to compare different models.
-In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you then please include some of this information in this paragraph?}
+In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you please include some of this information in here?}
 
 Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for all of our disk models around KBHsSH.
-First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
-As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1.
+It is worth mentioning that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
+As shown in~\cite{Abramowicz:1978}, constant angular momentum disks arround Kerr BHs exhibit a maximum for $|\Delta W|$ when the spin parameter $a\rightarrow 1$.
 This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$.
-The models V, VI and VII violate that bound.
-This is related, as we see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
-\sg{The maximum value of these quantities increases with the total potential well $\Delta W$, irrespective of the value of the magnetisation.}
+Models V, VI, and VII of our sample violate that bound.
+As a result, the maximum values of the fluid quantities for disks around KBHsSH are significantly larger than in the Kerr BH case.
+In both cases, these values increase as $|\Delta W|$ increases, irrespective of the magnetisation, as shown in Table~\ref{HBH_disk_parameters}.
+
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
+%\hspace{-0.4cm}
+%\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
+%\hspace{-0.4cm}
+%\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
+%\hspace{-0.2cm}
+%\\
+%\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
+%\hspace{-0.4cm}
+%\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
+%\hspace{-0.4cm}
+%\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
+%\hspace{-0.2cm}
+%\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
+\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
+%\label{comparison_mass_density_peri}
+%\end{figure*}
 
@@
 \centering
-\includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
-\hspace{-0.2cm}
-\\
-\includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
-From left to right the columns correspond to models I, IV, and VII.
-The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
-\tf{I think there is a lot of vertical space that we do not really need in these plots.
-To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
-I know the plot will not look squared, but that's fine.}\sg{Done.}
-}
-\label{comparison_mass_density}
+\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr}
 \end{figure*}
@@
 \centering
-\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
-\hspace{-0.2cm}
-\\
-\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
-\hspace{-0.4cm}
-\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
-\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
-\label{comparison_mass_density_peri}
+\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
+\hspace{-0.2cm}
+\caption{Rest-mass density distribution using perimeteral coordinates.
+From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
+\label{models_Kerr_peri}
 \end{figure*}
@@
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
-\hspace{-0.2cm}
-\caption{Rest-mass density distribution.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{models_Kerr}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
-\hspace{-0.2cm}
-\caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-\label{models_Kerr_peri}
-\end{figure*}
-
 \begin{table*}[t]
@@
 
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \subsection{Distribution of angular momentum in the disk}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Equilibrium models of thick disks around Kerr BHs are built assuming that the spacetime metric and the fluid fields are stationary and  axisymmetric (see, e.g.~\cite{Font:2002,Daigne:2004,Gimeno-Soler:2017} and references therein).
-For disks around KBHsSH we can follow the same approach as the metric ansatz given by Eq.~(\ref{metric}) is stationary and axisymmetric.
-
-% We start by introducing the specific angular momentum $l$ and the angular velocity $\Omega$ employing the standard definitions,
-% \begin{equation}
-% l = - \frac{u_{\phi}}{u_t}, \;\;\; \Omega = \frac{u^{\phi}}{u^t},
-% \end{equation}
-% where $u^{\mu}$ is the fluid four-velocity.
-% The relationship between $l$ and $\Omega$ is given by the equations
-% \begin{equation}
-% l = - \frac{\Omega g_{\phi\phi} + g_{t\phi}}{\Omega g_{t\phi} + g_{tt}}, \;\;\; \Omega = - \frac{l g_{tt} + g_{t\phi}}{l g_{t\phi} + g_{\phi\phi}},
-% \end{equation}
-% where we are assuming circular motion, i.e.~the four-velocity can be written as
-% \begin{equation}
-% u^{\mu} = (u^t, 0, 0, u^{\phi})\,.
-% \end{equation}
-
-% The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}).
-In this work, for simplicity and to reduce the ample space of parameters, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
-This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
-\tf{We should explain/motivate why we change our approach in this paper.} Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
-% \begin{equation}\label{eq:mb_ang_mom}
-% l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}
-% \end{equation}
-% where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
-Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
-% Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime.
-For prograde motion, the function has a minimum outside the event horizon.
-The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
-We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
-\tf{Is there an Appendix A?}.
-
-% %%%%%%%%%%%%%%%%
-% \subsection{Magnetized disks}
-% %%%%%%%%%%%%%%%%
-
-% To account for the magnetic flied in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}.
-We write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and
-% $\nabla_{\mu} (\rho u^{\mu}) = 0$, 
-% where $\nabla_{\mu}$ is the covariant derivative and
-% \begin{equation}\label{eq:e-m_tensor}
-% T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
-% \end{equation}
-% is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
-The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
-% Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
-% four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
-% $b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
-% and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow.
-Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
-% \begin{equation}
-% (\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
-% \end{equation}
-% where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
-% \begin{equation}\label{eq:diff_ver}
-% \partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
-% \end{equation}
-% where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
-
-% To integrate Eq.~\eqref{eq:diff_ver} we need to assume an equation of state (EOS). We assume a polytropic EOS of the form
-% \begin{equation}\label{eq:eos_fluid}
-% p = K \rho^{\Gamma},
-% \end{equation}
-% with $K$ and $\Gamma$ constants.
-%  By introducing the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\widetilde{\rho h} = \mathcal{L} (\rho h)$, we can write equations equivalent to Eq.~\eqref{eq:eos_fluid} for both $\tilde{p}_{\mathrm{m}}$ and $p_{\mathrm{m}}$
-% \begin{eqnarray}
-% \label{eq:eos_mag_tilde}
-% \tilde{p}_{\mathrm{m}} &=& M \widetilde{\rho h}^q,
-% \\
-% p_{\mathrm{m}} &=& M \mathcal{L}^{q-1} (\rho h)^q,
-% \end{eqnarray}
-% where $M$ and $q$ are constants. Then we can integrate Eq.~\eqref{eq:diff_ver} as
-% \begin{equation}\label{eq:final}
-% W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}M(\mathcal{L}\rho h)^{q-1}=0,
-% \end{equation}
-% where $W \equiv \ln |u_t|$ stands for the (gravitational plus centrifugal) potential and  $W_{\mathrm{in}}$ is the potential at the inner edge of the disk.
-
-% We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
-These are  given by
-% \begin{eqnarray}\label{eq:torus_energy_density}
-% \rho_{\mathrm{T}} &=&  \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
-% \\
-% \rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
-% \end{eqnarray}
-
-% %
-% %\begin{equation}\label{eq:torus_energy_density}
-% %\rho_{\mathrm{T}} = -T^t_t + T^i_i = \frac{\rho h (g_{\phi\phi} - g_{tt} l^2)}{g_{\phi\phi} + 2 g_{t\phi} l + g_{tt} l^2} + 2 (p + p_{\mathrm{m}}),
-% %\end{equation}
-% %and
-% %\begin{equation}\label{eq:SF_energy_density}
-% %\rho_{\mathrm{SF}} = -(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i = 2 \left(\frac{2 e^{2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
-% %\end{equation}
-
-% From the previous discussion it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field $\mu = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$, the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, and the density at the centre of the disk $\rho_{\mathrm{c}} = 1$.
-Thus, we leave the magnetization at the centre $\beta_{\mathrm{m_c}}$ as the only free parameter for each model of KBHsSH.
-With this information we can compute all relevant physical quantities.
-
-% \tf{We should discuss a bit more the reason for this choice.
-If $l_{\rm ms}<l<l_{\rm mb}$ and $r_{\rm mb}<r_{\rm cusp}<r_{\rm ms}$ the disk is closed and has a centre and a cusp.
-If $l=l_{\rm mb}$ and $r_{\rm cusp}=r_{\rm mb}$ the disk has a centre and a cusp, and it is closed at infinity.
-The models we have built are the latter, right?
-I wonder if we should have built models not completely filling their Roche lobe, so that they had a finite size.
-In any case, a comment must be provided here.}
-
-% \tf{We also have to emphasize somewhere in the paper that we do not fix $h=1$. This is an important difference with respect to the work of~\cite{Vincent:2016}.}
-
-% %%%%%%%%%%%%
-% \section{Methodology}
-% \label{procedure}
-% %%%%%%%%%%%%
-
-% \tf{Probably we do not need to have two subsections in this section, but just one. The description of the methodology is very
-% poor now. It needs a lot of rewriting.}
-
-% %%%%%%%%%%%%%%%%
-% \subsection{Building the disks}
-% %%%%%%%%%%%%%%%%
-
-% To construct our models we first find the specific angular momentum $l$ and the radius of the cusp $r_{\mathrm{cusp}}$ as the minimum value of Eq.~\eqref{eq:mb_ang_mom} and the radial location of said minimum outside the event horizon, respectively.
-This choice of angular momentum implies $r_{\mathrm{cusp}} = r_{\mathrm{mb}}$, $l = l_{\mathrm{K}}(r_{\mathrm{mb}})$, and $W_{\mathrm{in}} = 0$.
-Next, we can compute the gravitational plus centrifugal potential distribution as $W(r, \theta) \equiv \ln |u_t|$.
-Considering this, and that we can write the magnetic pressure at the centre as
-% \begin{equation}
-% p_{\mathrm{m_c}} = M \mathcal{L}^{q-1} \left(1 + \frac{\Gamma K}{\Gamma +1}\right)^q = \frac{K}{\beta_{\mathrm{m_c}}},
-% \end{equation}
-% where we have taken into account that $\rho_{\mathrm{c}} = 1$, that the pressure at the center is $p_{\mathrm{c}} = K$ and the specific enthalpy can be written as $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
-\tf{The previous sentence reads a bit strange.} Replacing this into Eq.~\eqref{eq:final} we arrive at an equation for the polytropic constant $K$
-% \begin{equation}\label{eq:K_eq}
-% W_{\mathrm{c}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\right) + \frac{q}{q-1}\frac{K/\beta_{\mathrm{m_c}}}{1 + \frac{\Gamma K}{\Gamma +1}} = 0.
-% \end{equation}
-% Once we have $K$, it is easy to find $p_{\mathrm{m}}$, $M$ and $h_{\mathrm{c}}$ with the definition of the magnetization parameter at the center $\beta_{\mathrm{m_c}}$, the equation~\eqref{eq:eos_mag} and $h = 1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}$.
-With this, we already have all we need in order to compute all the relevant physical quantities inside the disk.
-
-% %%%%%%%%%%%%%%%%%
-% \subsection{Numerical method}
-% %%%%%%%%%%%%%%%%%
-
-% We start from a uniform numerical grid $(X, \theta)$ (with $x$ being a compactified radial coordinate such as $X = x/(1+x)$ and $x = \sqrt{r^2 - r_{\mathrm{H}}^2}$) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_X \times N_\theta = 251 \times 30$.
-Then, we transform and interpolate the grid to end with a non-uniform grid $(r, \theta)$ with a domain $[r_{\mathrm{H}}, 199.2] \times [0, pi/2]$ and a number of points $N_r \times N_\theta = 2500 \times 300$, this is the grid we use for our computations.
-
-% Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH. \tf{Describe.}
-
-% <<<<<<< HEAD
-% In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
-\tf{Describe this figure.}
-
-% In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
-The plots show that the maximum of the total energy density of the disk $\rho_{\mathrm{t}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
-\tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}
-
-% \tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
-Is this correct?
-Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field?
-Is this a valid approximation because we are in the test-fluid regime?
-What did~\cite{Vincent:2016} do?}
-
-% \subsection{Comparison with KBHs}
-
-% Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetisation parameter at the center ($10^{10}$, top row, and $10^{-10}$, bottom row).
+This figure shows that, for non-magnetised disks, the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+This trend disappears with increasing magnetisation, as the disk moves closer to the horizon in such case.
+
+%%%%%%%%%%%%%%%%%%%%%
+\subsection{Comparison with Kerr BHs}
+%%%%%%%%%%%%%%%%%%%%%
+
+For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+Our numerical approach can handle BH spins as large as $|a-1|=10^{-10}$ \tf{Check} but such extreme cases do not add further relevant information to our discussion.
+Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
+As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$.
+It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.
+\tf{Describe further the table and the figures}.
+\tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.}
+
+Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+
+\sg{Compare the radial profiles.}
+\sg{Describe and compare the angular velocity at the centre.}
 
@@
 
-% %%%%%%%%%%%%%%%%%%
-% \subsection{Magnetization profiles}
-% %%%%%%%%%%%%%%%%%%
-
-% The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+%%%%%%%%%%%%%%%%%%
+\subsection{Magnetization profiles}
+%%%%%%%%%%%%%%%%%%
+
+The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
 The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
@@
 
-% Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
 The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
 As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.
-
-% \sg{Include discussion about radial profiles.}
+\sg{At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
+As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximmation to be valid in the non-magnetised regime.
+Now we can see that, in the KBHsSH case, this approximmation is not valid even for mildly-magnetised discs.}
+
+%%%%%%%%%%%%%%%%%%
+\subsection{Torus mass}
+%%%%%%%%%%%%%%%%%%
+
+\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the discs.
+For this case only, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+This is in agreement with the torus masses found as the final state of binary neutron stars mergers}
+
+\sg{I think here we should go further and do the following: First, choose a suitable maximum ADM mass for the KBHsSH (Eq~(I.1) of~\cite{Herdeiro:2016}), this implies a choice of scalar field mass $\mu$.
+This maximum mass should be such as our models ADM mass would be $\sim 2.5 M_{\odot}$.
+Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetisations and their Kerr ADM equivalents).
+Finally, we compute the cgs central densities with the formula (From the book of Rezzolla \emph{Relativistic Hydrodynamics})}
+\begin{equation}
+\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}
+\end{equation}
+\sg{and compare the central densities (or maximum) with known values.}
 
@@
 
-% \begin{table*}[t]
-% \caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH.
-For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
-\tf{Are we using the perimetral radial coordinate in this table?}}
-% \label{HBH_disk_parameters}      
-% \centering          
-% \begin{tabular}{c c c c c  c c c c c c c}
-% \hline\hline       
-%  Model & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
-% \hline           
-% I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.0$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\ 
-%  \hline 
-% II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.0$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\ 
-%  \hline 
-% III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.0$ & $0.109$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
-% \hline  
-% IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.723$ & $1.0$ & $0.182$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\ 
-% \hline 
-%  &  &  &  &  & $1$ & $1.38$ & $1.37$ & $0.129$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\ 
-% \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
-% \hline   
-% V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.0$ & $0.246$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\ 
-% \hline 
-%  &  &  &  &  & $1$ & $1.51$ & $1.40$ & $0.178$ & $0.132$ & $0.78$ & $0.87$ \\ 
-% \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $4.26$ & $1.18 \times 10{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
-% \hline   
-% VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.0$ & $0.324$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\ 
-% \hline 
-%  &  &  &  &  & $1$ & $1.66$ & $1.39$ & $0.228$ & $0.169$ & $0.72$ & $0.86$ \\ 
-% \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
-% \hline 
-% VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.0$ & $0.610$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
-% \hline 
-%  &  &  &  &  & $1$ & $2.25$ & $1.64$ & $0.510$ & $0.322$ & $0.43$ & $0.62$\\ 
-% \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
-% \hline 
-% \end{tabular}
-% \end{table*}
-
-% \subsection{2D Morphology}
-
-% We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}.
-The radial coordinate in these figures is the standard one of the spherical coordinate system.
-% Figures~\ref{models_I} and~\ref{models_II} show the logarithm of the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
-
-% The structure of the disks is similar for all values of $\beta_{\mathrm{m_c}}$ with the only quantitative differences being the location of the centre of the disk, which moves closer to the BH as the magnetization increases, and the range of variation of the isodensity contours, whose upper ends become larger with decreasing $\beta_{\mathrm{m_c}}$.
-This behaviour is in complete agreement with that found for KBHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
-For the particular case of Model VII, the maximum of the rest-mass density for the stronlgy magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
-\tf{Can we use the last isodentity contour as a good measure of the size of the disk?}
-
-% In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same models, but using a perimetral radial coordinate such as $R = e^{F_2} r$.
-\tf{We need to justify why we introduce this new radial coordinate.
-What is the benefit?
-Please include an explanation and also describe briefly the differences/similarities between these two figures and the first two.}
-
-% Table~\ref{HBH_disk_parameters} reports the relevant physical quantities for our disk models around KBHsSH.
-First of all, it is worth to mention that KBHsSH can violate the Kerr bound for the potential $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$.
-As shown in~\cite{Abramowicz:1978}, constant angular momentum disks exhibit a maximum for $|\Delta W|$ when the spin parameter $a$ approaches 1.
-This value is $\Delta W_{\mathrm{max}} = -\frac{1}{2} \ln 3 \simeq -0.549$.
-The models V, VI and VII violate that bound.
-This is related, as we will see, with the maximum value of the specific enthalpy, pressure and magnetic pressure.
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.12]{figures/fig5_I_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.12]{figures/fig5_VII_10.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.12]{figures/fig5_I__10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.12]{figures/fig5_VII__10.pdf}
-% \hspace{-0.2cm}
-% \caption{Energy density distribution for the torus $\rho_{\mathrm{T}}$ (upper half of the images) and for the scalar field $\rho_{\mathrm{SF}}$ (lower half).
-From left to right the columns correspond to models I, IV, and VII.
-The top row corresponds to non-magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$) and the bottom row to strongly magnetized models ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
-% \tf{I think there is a lot of vertical space that we do not really need in these plots.
-To save some space, as we have many figures, I suggest to plot the vertical axis in shorter ranges, say $[-0.75,0.75]$ for model I, $[-0.5,0.5]$ for model IV, and $[-0.35,0.35]$ for model VII (and keeping the horizontal axis as it is now).
-I know the plot will not look squared, but that's fine.}
-% }
-% \label{comparison_mass_density}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
-% \hspace{-0.4cm}
-% \includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
-% \hspace{-0.4cm}
-% \includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
-% \hspace{-0.2cm}
-% \\
-% \includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
-% \hspace{-0.4cm}
-% \includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
-% \hspace{-0.4cm}
-% \includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
-% \hspace{-0.2cm}
-% \caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
-\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.}}
-% \label{comparison_mass_density_peri}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
-% \hspace{-0.cm}
-% \includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
-% \hspace{-0.cm}
-% \\
-% \includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
-% \hspace{-0.cm}
-% \includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
-% \hspace{-0.cm}
-% \caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
-In the first row, we show this for all of our KBHsSH models.
-In the second row, we show this for a sequence of KBHs with increasing spin parameter.\sg{fixed cases and labels.}}
-% \label{comparison_HBH_Kerr_dens_enth}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/fig8_HBH.eps}
-% \hspace{0.5cm}
-% \includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
-% \hspace{0.5cm}
-% \caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)($R_{\mathrm{mag}, \mathrm{max}} / R_{\mathrm{c}}$).
-Left panel: KBHsSH models.
-Right panel: A sequence of KBHs with increasing spin parameter.\sg{fixed cases and labels.}}
-% \label{comparison_HBH_Kerr_r_m_max}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
-% \hspace{-0.2cm}
-% \caption{Rest-mass density distribution.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-% \label{models_Kerr}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
-% \\
-% \includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
-% \hspace{-0.3cm}
-% \includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
-% \hspace{-0.2cm}
-% \includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
-% \hspace{-0.2cm}
-% \caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
-% \label{models_Kerr_peri}
-% \end{figure*}
-
-% \begin{table*}[t]
-% \caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
-For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
-% \label{KBH_disk_parameters}      
-% \centering          
-% \begin{tabular}{c c c c c  c c c c c c c}
-% \hline\hline       
-%  $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
-% \hline           
-% $0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
-%  \hline 
-%  $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
-% \hline  
-% $0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
-%  \hline 
-%  &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
-%  \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
-%  \hline 
-% $0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
-% \hline 
-%  &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
-% \hline 
-%  &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
-% \hline   
-% \end{tabular}
-% \end{table*}
-
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and 2 values of the magnetization parameter at the center ($10^{10}$, left panel, and $10^{-10}$, right panel).
-\tf{Describe this figure.} \sg{Not sure if we need to describe both figures separately.
-Maybe we only need one of them.}
-
-In figure~\ref{comparison_mass_density_peri}, we show the same, but using the perimeteral coordinate we defined earlier.
-The plots show that \sg{, for the non-magnetised cases,} the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
-\tf{This trend is only satisfied for the unmagnetized models (top row) but not for the strongly magnetized models.}\sg{This trend disappears with increasing magnetisation, as the disc moves closer to the horizon.}
-
-\tf{One question: in our approach we are building the disks using the stress-energy tensor of the fluid only.
-Is this correct?
-Shouldn't we consider the entire stress-energy tensor from the fluid and the scalar field?
-Is this a valid approximation because we are in the test-fluid regime?
-What did~\cite{Vincent:2016} do?}
-\sg{They do the same as us.
-As we are considering the scalar field part of the spacetime (there is no interaction between the scalar field and the matter other than gravity) and we are in the test-fluid approximmation I think this is correct.}
-
-%%%%%%%%%%%%%%%%%%%
-\subsection{Comparison with KBHs}
-%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{KBH_disk_parameters} reports the relevant physical quantities for the disks built around KBH.
-\sg{As in the KBHsSH case, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $\Delta W$ (in this case this also means increasing value of $a$).
-Also, it can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.} \tf{Describe.}
-
-Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
-
-\sg{I am thinking about merging this section with the others.}
-
-\sg{Compare the radial profiles.}
-\sg{Describe and compare the angular velocity at the centre.}
-
-% As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
-Nevertheless, we show them for the sake of clarity.
-Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
-This idea is discussed in appendix~\ref{torus_embedding}.
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Magnetization profiles}
-%%%%%%%%%%%%%%%%%%
-
-The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
-The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
-\tf{Maybe there is an excessive number of cases for KBHs.
-Maybe it's enough to only include the four cases we have in Table III.
-We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9.
-This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
-However, there are differences between the two cases.
-For the enthalpy, the values of $h_{\mathrm{max}}$ reached for the KBHsSH are much higher than those of the KBH case.
-This fact tells us that, while the $w = \rho h \simeq \rho$ approximation (see \cite{Komissarov:2006} and \cite{Gimeno-Soler:2017}) is valid for magnetized flows ($\beta_{\mathrm{m_c}} \sim 1$) for reasonable values of the spin parameter ($a \sim 0.99$ or lower), that is not the case for KBHsSH.
-Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
-
-Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
-The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
-As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.
-\sg{At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
-As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximmation to be valid in the non-magnetised regime.
-Now we can see that, in the KBHsSH case, this approximmation is not valid even for mildly-magnetised discs.}
-
-%%%%%%%%%%%%%%%%%%
-\subsection{Torus mass}
-%%%%%%%%%%%%%%%%%%
-
-\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the discs.
-For this case only, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
-This is in agreement with the torus masses found as the final state of binary neutron stars mergers}
-
-\sg{I think here we should go further and do the following: First, choose a suitable maximum ADM mass for the KBHsSH (Eq~(I.1) of~\cite{Herdeiro:2016}), this implies a choice of scalar field mass $\mu$.
-This maximum mass should be such as our models ADM mass would be $\sim 2.5 M_{\odot}$.
-Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetisations and their Kerr ADM equivalents).
-Finally, we compute the cgs central densities with the formula (From the book of Rezzolla \emph{Relativistic Hydrodynamics})}
-\begin{equation}
-\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}
-\end{equation}
-\sg{and compare the central densities (or maximum) with known values.}
-
-%\begin{table}
-%\caption{List of models of KBHsSH.}        
-%\label{models_list}      
-%\centering          
-%\begin{tabular}{c c c c  c c c c}
-%\hline\hline       
-% Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
-%\hline           
-%I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
-% \hline 
-%II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
-% \hline 
-%III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
-% \hline 
-%IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
-% \hline 
-%V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
-% \hline 
-%VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
-% \hline 
-%VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
-%\hline      
-%\end{tabular}
-%\end{table}
-%
-%\begin{table}
-%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-%\label{models_spin_vel}      
-%\centering          
-%\begin{tabular}{c c c c c}
-%\hline\hline       
-% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-%\hline           
-%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
-% \hline 
-%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
-% \hline 
-%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
-% \hline 
-%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
-% \hline 
-%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
-% \hline 
-%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
-% \hline 
-%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-%\hline      
-%\end{tabular}
-%\end{table}
-
 %%%%%%%%%%%%

### 2018-11-08 paper_prd.tex
added sphericity
More work.

@@
 \hspace{-0.cm}
-\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disc.
+\caption{Effects of the magnetization on the values for the maximum density (left) and enthalpy (right) of the disks.
 In the first row, we show this for all of our KBHsSH models.
-In the second row, we show this for a sequence of KBHs with increasing spin parameter.}
+In the second row, we show this for a sequence of Kerr BHs with increasing spin parameter.
+\tf{Using yellow is a bad choice as it cannot be seen, especially on print.
+Please change the colour of the yellow dots to some other colour or symbol.}}
 \label{comparison_HBH_Kerr_dens_enth}
@@
 Left panel: KBHsSH models.
-Right panel: A sequence of KBHs with increasing spin parameter.}
+Right panel: A sequence of KBHs with increasing spin parameter.
+\tf{Change the $r$ to $R$ in the vertical labels.}}
 \label{comparison_HBH_Kerr_r_m_max}
@@
 %%%%%%%%%%%%%%%%%%
-\subsection{Magnetization profiles}
+\subsection{Magnetisation profiles}
 %%%%%%%%%%%%%%%%%%
@@
 The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
-The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to a sequence of KBHs with increasing spin parameter.
-\tf{Maybe there is an excessive number of cases for KBHs.
-Maybe it's enough to only include the four cases we have in Table III.
-We could always indicate in the main text the values that are reached for an extreme value of $a$ with seven 9.
-This will also simplify the presentation of this figure, where I don't like very much having lines and dots.} Here we can see that, for both cases, an increase in $|\Delta W|$ implies higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
-However, there are differences between the two cases.
-For the enthalpy, the values of $h_{\mathrm{max}}$ reached for the KBHsSH are much higher than those of the KBH case.
-This fact tells us that, while the $w = \rho h \simeq \rho$ approximation (see \cite{Komissarov:2006} and \cite{Gimeno-Soler:2017}) is valid for magnetized flows ($\beta_{\mathrm{m_c}} \sim 1$) for reasonable values of the spin parameter ($a \sim 0.99$ or lower), that is not the case for KBHsSH.
-Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
-
-Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the variation of the quotient of the perimeteral radius of the magnetic pressure maximum by the perimeteral radius of the disk center $R_{\mathrm{m, max}}/R_{\mathrm{c}}$ with the decimal logarithm of the magnetization parameter at the disk center $\log_{10} \beta_{\mathrm{m_c}}$ for the same KBHsSH and KBH cases as in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to our sequence of Kerr BHs with increasing spin parameter.
+For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetisation) and also higher values for $\rho_{\mathrm{max}}$ (high magnetisation).
+However, there are quantitative differences between the two cases.
+For the enthalpy, the values of $h_{\mathrm{max}}$ reached for disks around KBHsSH are much higher than those of the Kerr BH case.
+This implies that, while the $w = \rho h \simeq \rho$ approximation (employed in~\cite{Komissarov:2006,Gimeno-Soler:2017}) is valid for magnetized disks ($\beta_{\mathrm{m_c}} \sim 1$) around Kerr BHs for values of the spin parameter as high as $a \sim 0.99$, that is not the case for disks around KBHsSH.
+We note that for the most extreme spin value we can build, $a=XXX$, the maximum enthalpy is $h_{\rm max}=XXX$.
+\tf{Complete.}
+%Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
+
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimetral radius of the magnetic pressure maximum and the perimetral radius of the disk center, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the center of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
+The curves plotted vorrespond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.
 The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.

### 2018-11-08 paper_prd.tex
corrected typo at table I
More work.

@@
 \caption{List of models of KBHsSH used in this work.
-From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, and the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$.}
+From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, and the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$.
+\tf{Mention the last column.}}
 \label{models_list}      
 \centering          
-\begin{tabular}{c c c c  c c c c   c c c c}
+\begin{tabular}{c c c c  c c c c   c c c c c}
 \hline\hline       
- Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\
-\hline           
-I & $0.415$ & $0.172$ & $0.393$ &  $0.150$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$\\ 
- \hline 
-II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.290$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ \\
- \hline 
-III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.432$ & $0.401$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
- \hline 
-IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.100$ & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
- \hline 
-V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.781$ & $0.680$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
- \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.781$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
- \hline 
-VII & $0.975$ & $0.850$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.040$ & $0.8941$ & $6.173$ & $0.0973$ & $0.1928$ \\ 
+ Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ & $\mathfrak{s}$\\
+\hline           
+I & $0.415$ & $0.172$ & $0.393$ &  $0.150$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$ & $1.404$\\ 
+ \hline 
+II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.290$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ & $1.352$ \\
+ \hline 
+III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.432$ & $0.401$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ & $1.489$ \\ 
+ \hline 
+IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.100$ & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ & $1.425$ \\ 
+ \hline 
+V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.781$ & $0.680$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ & $1.357$ \\ 
+ \hline 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.781$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
+ \hline 
+VII & $0.975$ & $0.850$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.040$ & $0.8941$ & $6.173$ & $0.0973$ & $0.1928$ & $1.039$ \\ 
 \hline      
@@
 Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimetral radius of the magnetic pressure maximum and the perimetral radius of the disk center, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the center of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
-The curves plotted vorrespond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.
+The curves plotted correspond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.
 The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.

### 2018-11-08 paper_prd.tex
More work. Sergio, you should take over now.

@@
  \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.781$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
  \hline 
@@
 \centering
-\includegraphics[scale=0.2]{figures/fig8_HBH.eps}
+\includegraphics[width=0.4\textwidth]{figures/fig8_HBH.eps}
 \hspace{0.5cm}
-\includegraphics[scale=0.2]{figures/fig8_Kerr.eps}
+\includegraphics[width=0.4\textwidth]{figures/fig8_Kerr.eps}
 \hspace{0.5cm}
-\caption{Effects of the magnetization on the (perimeteral) location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre)(($R_{\mathrm{mag}, \mathrm{max}} - R_{\mathrm{c}})/ R_{\mathrm{c}}$).
+\caption{Effects of the magnetization on the perimeteral location of the magnetic pressure maximum (divided by the the perimeteral radius of the centre), $R_{\mathrm{mag}, \mathrm{max}} - R_{\mathrm{c}})/ R_{\mathrm{c}}$).
 Left panel: KBHsSH models.
@@
 The curves plotted correspond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.
-The inset shows a region around $\beta_{\mathrm{m_c}} = 3$ and $R_{\mathrm{m, max}}/R_{\mathrm{c}} = 1$, this is because for disks with $h = 1$, $R_{\mathrm{m, max}} = R_{\mathrm{c}}$ if $\beta_{\mathrm{m_c}} = 1 / \Gamma - 1$.
-As we can easily see, this condition is also fulfilled for the Kerr case, even $h \neq 1$ (with a slight deviation for very high spin parameter cases), but not quite for the KBHsSH cases.
-\sg{At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
-As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximmation to be valid in the non-magnetised regime.
-Now we can see that, in the KBHsSH case, this approximmation is not valid even for mildly-magnetised discs.}
+For all cases, the radial location of the magnetic pressure maximum decreases with decreasing $\beta_{\mathrm{m_c}}$.
+In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / \Gamma - 1=3$.
+This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, as can be seen in the inset of the right panel of Fig.~\ref{comparison_HBH_Kerr_r_m_max}.
+However, this condition is not fulfilled for disks built around KBHsSH (see inset in the left panel).
+At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
+As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximation to be valid in the non-magnetised regime.
+Now we can see that, in the KBHsSH case, this approximation is not valid even for mildly-magnetised discs.
 

### 2018-11-09 paper_prd.tex
corrected typos at equations
Completed a first version of the abstract.

@@
 Testing the true nature of black holes -- the no-hair hypothesis -- will become increasingly more precise in the next few years as new observational data is collected in both the gravitational wave channel and the electromagnetic channel.
-In this work we consider numerically generated spacetimes of Kerr black holes with synchronised scalar hair and build stationary models of magnetized constant angular momentum thick disks around them.
-We study the dependence of the morphology and properties of the accretion tori on the type of black hole considered, from purely Kerr black holes with varying degrees of  spin parameter to Kerr black holes with scalar hair with different ADM mass and horizon angular velocity.
-\tf{To be completed.}
+In this paper we consider numerically generated spacetimes of Kerr black holes with synchronised scalar hair and build stationary models of magnetized thick disks (or tori)  around them.
+Our approach assumes that the disks are not self-gravitating, they obey a polytropic equation of state, the distribution of their specific angular momentum is constant, and they are marginally stable, i.e.~the disks completely fill their Roche lobe.
+Moreover, contrary to existing approaches in the literature, our models are thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
+We study the dependence of the morphology and properties of the accretion tori on the type of black hole considered, from purely Kerr black holes with varying degrees of spin parameter, namely from a Schwarzschild black hole to a nearly extremal Kerr case,  to Kerr black holes with scalar hair with different ADM mass and horizon angular velocity.
+Comparisons between the disk properties for both types of black holes are presented.
+The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
 \end{abstract}

### 2018-11-10 paper_prd.tex
Some work on the conclusions.

@@
 Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
-In this investigation we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case, whose sequences have already been computed.
+In this investigation we focus on disks with a constant distribution of specific angular momentum.
+In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz78} (but see also~\cite{Fishbone76}).
+In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
 The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
@@
 
+\tf{Sergio please finish this section.}
+
 \sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the discs.
@@
 
-%\begin{table}
-%\caption{List of models of KBHsSH.}        
-%\label{models_list}      
-%\centering          
-%\begin{tabular}{c c c c  c c c c}
-%\hline\hline       
-% Model & $M_{\mathrm{ADM}}$ & $J_{\mathrm{ADM}}$ & $M_{\mathrm{H}}$ &  $J_{\mathrm{H}}$ & $M_{\mathrm{SF}}$ & $J_{\mathrm{SF}}$ & $r_{\mathrm{H}}$ \\ 
-%\hline           
-%I & $0.415$ & $0.172$ & $0.393$ &  $0.15$  & $0.022$ & $0.022$ & $0.2$\\ 
-% \hline 
-%II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.063$ & $0.282$ & $0.221$ \\
-% \hline 
-%III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.573$ & $0.432$ & $0.111$ \\ 
-% \hline 
-%IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.1$ \\ 
-% \hline 
-%V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.757$ & $0.781$ & $0.091$ \\ 
-% \hline 
-%VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.781$ & $0.088$ \\ 
-% \hline 
-%VII & $0.975$ & $0.85$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.04$ \\ 
-%\hline      
-%\end{tabular}
-%\end{table}
-%
-%\begin{table}
-%\caption{Values of the normalized spin parameter for the ADM quantities ($a_{\mathrm{ADM}}$), for the BH horizon quantities ($a_{\mathrm{H}}$), the horizon linear velocity ($v_{\mathrm{H}}$) and the spin parameter corresponding to a KBH with a linear velocity equal to $v_{\mathrm{H}}$, ($a_{\mathrm{H_{eq}}}$).}
-%\label{models_spin_vel}      
-%\centering          
-%\begin{tabular}{c c c c c}
-%\hline\hline       
-% Model & $a_{\mathrm{ADM}}$ & $a_{\mathrm{H}}$ & $v_{\mathrm{H}}$ & $a_{\mathrm{H_{eq}}}$ \\ 
-%\hline           
-%I & $0.9987$ & $0.9712$ & $0.7685$ & $0.9663$ \\ 
-% \hline 
-%II & $1.014$ & $0.3760$ & $0.6802$ & $0.9301$ \\
-% \hline 
-%III & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ \\ 
-% \hline 
-%IV & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ \\ 
-% \hline 
-%V & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ \\ 
-% \hline 
-%VI & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ \\ 
-% \hline 
-%VII & $0.8941$ & $6.173$ & $0.09732$ & $0.1928$ \\ 
-%\hline      
-%\end{tabular}
-%\end{table}
-
 %%%%%%%%%%%%
@@
 
+Testing the no-hair hypothesis of BHs will become increasingly more precise in the next few years as new observational data is collected in both the gravitational wave channel and in the electromagnetic channel.
+Astrophysical BHs are commonly surrounded by accretion disks, both at stellar-mass scales or at supermassive scales.
+In the former case,  stellar-mass BHs surrounded by thick discs (or tori) are broadly accepted as natural end results of catastrophic events involving compact objects, namely binary neutron star mergers and black hole neutron star mergers.
+These systems are traditionally described using the paradigmatic BHs of general relativity, where the spacetime metric is given by the Kerr metric solely described by the BH mass and spin.
+Upcoming observational campaigns may, however, provide data to discriminate those canonical BH solutions from exotic alternatives as, e.g., those in which the BHs are endowed with scalar or vector (Proca) hair, recently obtained by XXX.
+
+In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronised scalar hair and have built stationary models of magnetized thick disks (or tori)  around them.
+Those disks are assumed to be not self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
+In addition, and for simplicity purpose, the distribution of the specific angular momentum in the disks has been assumed to be constant.
+The models have been constructed building on existing approaches presented by~\cite{Komissarov:2006} and~\cite{Gimeno-Soler:2017}.
+An important generalization of this work compared to the methodology presented in previous works has to do with the fluid model: while the mater EOS is still rather simplistic (a polytropic EOS) the models are thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
+That leads to interesting differences with respect to the findings reported in~\cite{Gimeno-Soler:2017} for the purely Kerr BH case.
+
+%HERE
+
+We have studied the dependence of the morphology and properties of the accretion tori on the type of black hole considered, from purely Kerr black holes with varying degrees of spin parameter, namely from a Schwarzschild black hole to a nearly extremal Kerr case,  to Kerr black holes with scalar hair with different ADM mass and horizon angular velocity.
+Comparisons between the disk properties for both types of black holes are presented.
+The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
+
 Future work: Non-constant angular momentum case, Proca hair, shadows of the system HBH+disk.
 
-\begin{acknowledgements}
-
-\end{acknowledgements}
-
-\bibliographystyle{apsrev4-1}
-\bibliography{references.bib}
+%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%%%%%%%%%%%%%%%%
+
+This work has been supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P), by the FCT (Portugal) IF programme, by the CIDMA (FCT) 
+strategic project UID/MAT/04106/2013 and by  the  European  Union's  Horizon  2020  research  and  innovation  (RISE) programmes H2020-MSCA-RISE-2015 Grant No.~StronGrHEP-690904 and H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740.
+The authors would like to acknowledge networking support by the COST Action CA16104.
 
@@
 
-\section{Finding $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$}\label{ang_mom_appendix}
-\sg{I figured this out, but now I am not really sure if this is interesting enough to be an appendix by itself. Maybe more like a comment in the main text.}
-We start by considering the lagrangian of a stationary and axisymmetric spacetime
+\section{Finding $l_{\mathrm{mb}}$ and $r_{\mathrm{mb}}$}
+\label{ang_mom_appendix}
+
+We start by considering the Lagrangian of a stationary and axisymmetric spacetime
 \begin{equation}
@@
 
+\bibliographystyle{apsrev4-1}
+\bibliography{references.bib}
+
 \end{document}

### 2018-11-12 paper_prd.tex
some work

--- 2018-11-08 paper_prd.tex
@@
 \caption{List of models of KBHsSH used in this work.
-From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, and the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$.
+From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$ and the sphericity of the horizon $\mathfrak{s}$.
 \tf{Mention the last column.}}
@@
 The models have been selected to span all regions of interest in the parameter space.
-Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH, while model VII corresponds to a hairy Kerr BH with almost all the mass and angular momentum stored in the scalar field.
+Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH (a $94.7\%$ of the total mass and a $87.2\%$ of the total angular momentum of the spacetime are stored in the BH), while model VII corresponds to a hairy Kerr BH with almost all the mass and angular momentum stored in the scalar field (a $98.15\%$ of the total mass and a $99.76\%$ of the total angular momentum of the spacetime are stored in the scalar field).
 It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than unity) in terms of both ADM or horizon quantities.
@@
 \begin{equation}\label{eq:final}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0,
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma -1}\rho^{\Gamma -1}\right) + \frac{q}{q-1}K_{\rm m}(\mathcal{L}\rho h)^{q-1}=0,
 \end{equation}
@@
 \begin{equation}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) = 0.
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma -1}\rho^{\Gamma -1}\right) = 0.
 \end{equation}
@@
 \begin{equation}
-W - W_{\mathrm{in}} + \frac{\Gamma K}{\Gamma +1}w^{\Gamma -1}.
+W - W_{\mathrm{in}} + \frac{\Gamma K}{\Gamma -1}w^{\Gamma -1}.
 \end{equation}
@@
 \label{eq:to_solve_K}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho_{\mathrm{c}}^{\Gamma -1}\right) 
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma -1}\rho_{\mathrm{c}}^{\Gamma -1}\right) 
 \\
@@
 \label{eq:to_solve_rho}
-W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma +1}\rho^{\Gamma -1}\right) 
+W - W_{\mathrm{in}} + \ln \left(1 + \frac{\Gamma K}{\Gamma -1}\rho^{\Gamma -1}\right) 
 \\

### 2018-11-12 paper_prd.tex
Some work on section 2.

@@
 In this investigation we focus on disks with a constant distribution of specific angular momentum.
-In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz78} (but see also~\cite{Fishbone76}).
+In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}).
 In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
 The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
-
-%Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow.
-Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts.
-Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks.
 
@@
 \caption{List of models of KBHsSH used in this work.
-From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$ and the sphericity of the horizon $\mathfrak{s}$.
-\tf{Mention the last column.}}
+From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$, and the sphericity of the horizon, $\mathfrak{s}$.}
 \label{models_list}      
@@
 The models have been selected to span all regions of interest in the parameter space.
-Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH (a $94.7\%$ of the total mass and a $87.2\%$ of the total angular momentum of the spacetime are stored in the BH), while model VII corresponds to a hairy Kerr BH with almost all the mass and angular momentum stored in the scalar field (a $98.15\%$ of the total mass and a $99.76\%$ of the total angular momentum of the spacetime are stored in the scalar field).
+Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH (namely, $94.7\%$ of the total mass and $87.2\%$ of the total angular momentum of the spacetime are stored in the BH), while model VII corresponds to a hairy Kerr BH with almost all the mass (98.15\%) and angular momentum (99.76\%) stored in the scalar field.
 It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than unity) in terms of both ADM or horizon quantities.
 This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds the speed of light.
-For comparison, we also show in the last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
-\tf{Further description of the table.
-Something must be said about the coordinates.}.
-In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+For comparison, we also show in the second-to-last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
+\tf{Description of the sphericity.} In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
 \tf{This figure has to be redone.}

### 2018-11-12 paper_prd.tex
More work.

@@
 While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimetral coordinate $R$ is not always so.
-Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III.
-\tf{Check.}
+Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III (cf.~Table~\ref{models_list}, $\mathfrak{s}=1.489$).
 

### 2018-11-12 paper_prd.tex
Work on Tables II and III.
Work on the conclusions.

@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $2.74$ & $3.48 \times 10^{-11}$ & $0.206$ & $0.89$ & $0.91$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $2.74$ & $3.48 \times 10^{-11}$ & $2.06 \times 10^{-1}$ & $0.89$ & $0.91$\\ 
 \hline  
@@
 \hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $3.70$ & $7.83 \times 10^{-11}$ & $0.408$ & $0.76$ & $0.78$ \\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $3.70$ & $7.83 \times 10^{-11}$ & $4.08\times 10^{-1}$ & $0.76$ & $0.78$ \\ 
 \hline   
@@
 \hline 
- &  &  &  &  & $1$ & $1.51$ & $1.40$ & $1.78 \times 10^{-1}$ & $0.132$ & $0.78$ & $0.87$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $4.26$ & $1.18 \times 10^{-10}$ & $0.579$ & $0.67$ & $0.69$ \\ 
+ &  &  &  &  & $1$ & $1.51$ & $1.40$ & $1.78 \times 10^{-1}$ & $1.32\times 10^{-1}$ & $0.78$ & $0.87$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $4.26$ & $1.18 \times 10^{-10}$ & $5.79\times 10^{-1}$ & $0.67$ & $0.69$ \\ 
 \hline   
@@
 \hline 
- &  &  &  &  & $1$ & $1.66$ & $1.39$ & $2.28 \times 10^{-1}$ & $0.169$ & $0.72$ & $0.86$ \\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $4.54$ & $1.57 \times 10^{-10}$ & $0.740$ & $0.55$ & $0.59$ \\ 
-\hline 
-VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.00$ & $6.10 \times 10^{-1}$ & $6.459 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
-\hline 
- &  &  &  &  & $1$ & $2.25$ & $1.64$ & $5.10 \times 10^{-1}$ & $0.322$ & $0.43$ & $0.62$\\ 
+ &  &  &  &  & $1$ & $1.66$ & $1.39$ & $2.28 \times 10^{-1}$ & $1.69\times 10^{-1}$ & $0.72$ & $0.86$ \\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $4.54$ & $1.57 \times 10^{-10}$ & $7.40\times 10^{-1}$ & $0.55$ & $0.59$ \\ 
+\hline 
+VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.00$ & $6.10 \times 10^{-1}$ & $6.46 \times 10^{-11}$ & $1.10$ & $1.25$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $2.25$ & $1.64$ & $5.10 \times 10^{-1}$ & $3.22\times 10^{-1}$ & $0.43$ & $0.62$\\ 
 \hline 
@@
 \hline           
-$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.0$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
+$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
- \hline 
- $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.0$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
+ \hline 
+ $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
-\hline  
-$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.0$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
+\hline  
+$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
  \hline 
@@
  \hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
- \hline 
-$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.0$ & $0.134$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.29$ & $1.51$ & $0.110$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.0$ & $6.17$ & $1.22 \times 10^{-10}$ & $0.491$ & $2.0021$ & $2.0030$ \\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
+ \hline 
+$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
+\hline 
+ &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
+\hline 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
 \hline   
@@
 
-Testing the no-hair hypothesis of BHs will become increasingly more precise in the next few years as new observational data is collected in both the gravitational wave channel and in the electromagnetic channel.
-Astrophysical BHs are commonly surrounded by accretion disks, both at stellar-mass scales or at supermassive scales.
-In the former case,  stellar-mass BHs surrounded by thick discs (or tori) are broadly accepted as natural end results of catastrophic events involving compact objects, namely binary neutron star mergers and black hole neutron star mergers.
-These systems are traditionally described using the paradigmatic BHs of general relativity, where the spacetime metric is given by the Kerr metric solely described by the BH mass and spin.
-Upcoming observational campaigns may, however, provide data to discriminate those canonical BH solutions from exotic alternatives as, e.g., those in which the BHs are endowed with scalar or vector (Proca) hair, recently obtained by XXX.
-
-In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronised scalar hair and have built stationary models of magnetized thick disks (or tori)  around them.
+Astrophysical BHs are commonly surrounded by accretion disks, either at stellar-mass scales or at supermassive scales.
+In the former case,  stellar-mass BHs surrounded by thick discs (or tori) are broadly accepted as natural end results of catastrophic events involving the coalescence and merger of compact objects, namely binary neutron stars and BH-neutron star systems (see e.g.~\cite{FaberRasio2012,Paschalidis:2016agf,Rezzolla:2017} and references therein).
+These systems are traditionally described using the paradigmatic BHs of general relativity, where the spacetime metric is given by the Kerr metric, solely characterized by the BH mass and spin.
+Upcoming observational campaigns may, however, provide data to discriminate those canonical BH solutions from exotic alternatives as, e.g.~those in which the BHs are endowed with scalar or vector (Proca) hair, recently obtained by~\cite{Herdeiro:2014a,Herdeiro:2016}.
+It is conceivable that testing the no-hair hypothesis of BHs will become increasingly more precise in the next few years as new observational data is collected in both the gravitational-wave channel and in the electromagnetic channel.
+
+In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronised scalar hair and have built stationary models of magnetized tori around them.
 Those disks are assumed to be not self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
 In addition, and for simplicity purpose, the distribution of the specific angular momentum in the disks has been assumed to be constant.
-The models have been constructed building on existing approaches presented by~\cite{Komissarov:2006} and~\cite{Gimeno-Soler:2017}.
-An important generalization of this work compared to the methodology presented in previous works has to do with the fluid model: while the mater EOS is still rather simplistic (a polytropic EOS) the models are thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
-That leads to interesting differences with respect to the findings reported in~\cite{Gimeno-Soler:2017} for the purely Kerr BH case.
-
-%HERE
-
-We have studied the dependence of the morphology and properties of the accretion tori on the type of black hole considered, from purely Kerr black holes with varying degrees of spin parameter, namely from a Schwarzschild black hole to a nearly extremal Kerr case,  to Kerr black holes with scalar hair with different ADM mass and horizon angular velocity.
-Comparisons between the disk properties for both types of black holes are presented.
-The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
-
-Future work: Non-constant angular momentum case, Proca hair, shadows of the system HBH+disk.
+The models have been constructed building on existing approaches presented in~\cite{Komissarov:2006} and~\cite{Gimeno-Soler:2017}.
+An important generalization of the present work compared to the methodology presented in previous works has had to do with the fluid model: while the mater EOS is still rather simplistic (a polytropic EOS) the models are allowed to be thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
+That has led to interesting differences with respect to the findings reported in~\cite{Gimeno-Soler:2017} for the purely Kerr BH case.
+
+We have studied the dependence of the morphology and properties of the accretion tori on the type of BH system considered, from purely Kerr BHs with varying degrees of spin parameter (namely from a Schwarzschild BH to a nearly extremal Kerr case)  to KBHsSH with different ADM mass and horizon angular velocity.
+Comparisons between the disk properties for both types of BHs have been presented.
+The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and can be used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk (first attempted by~\cite{Vincent:2016}).
+In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
+The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
 
@@
 
-This work has been supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P), by the FCT (Portugal) IF programme, by the CIDMA (FCT) 
-strategic project UID/MAT/04106/2013 and by  the  European  Union's  Horizon  2020  research  and  innovation  (RISE) programmes H2020-MSCA-RISE-2015 Grant No.~StronGrHEP-690904 and H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740.
+This work has been supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P), by the FCT (Portugal) IF programme, by the CIDMA (FCT) strategic project UID/MAT/04106/2013 and by  the  European  Union's  Horizon  2020  research  and  innovation  (RISE) programmes H2020-MSCA-RISE-2015 Grant No.~StronGrHEP-690904 and H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740.
 The authors would like to acknowledge networking support by the COST Action CA16104.

### 2018-11-12 paper_prd.tex
Changing disc to disk, and ise to ize throughout.

@@
 We do not make this assumption here.
-To better understand the differences between these two approaches, we consider their behaviour in two limiting cases, namely the non-magnetised case and the extremely magnetised case.
+To better understand the differences between these two approaches, we consider their behaviour in two limiting cases, namely the non-magnetized case and the extremely magnetized case.
 
@@
 \caption{Size of the disks.
-Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
+Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
 From left to right we show model I, IV, and VII, respectively.}
@@
 
-For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time around we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
+For the extremely magnetized case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time around we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
 This yields the same result for both equations
@@
 In addition, we could consider the expression for the specific enthalpy in terms of the density $h = 1 + \frac{K\Gamma\rho^{\Gamma-1}}{\Gamma - 1}$ to 
-see that we will have $h \rightarrow 1$. This shows that, for the extremely magnetised limit, the two approaches coincide.
-
-Taking into account these two limits we can obtain the range of validity of the $h \simeq 1$ approximation: As magnetised disks exist between the two considered cases, for disks with a sufficiently small value of the potential well, $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$, the $h \simeq 1$ approximation is valid.
-On the contrary, if the value of $\Delta W$ is large enough, the approximation does not hold even for disks with a fairly low value of magnetisation.
+see that we will have $h \rightarrow 1$. This shows that, for the extremely magnetized limit, the two approaches coincide.
+
+Taking into account these two limits we can obtain the range of validity of the $h \simeq 1$ approximation: As magnetized disks exist between the two considered cases, for disks with a sufficiently small value of the potential well, $\Delta W \equiv W_{\mathrm{in}} - W_{\mathrm{c}}$, the $h \simeq 1$ approximation is valid.
+On the contrary, if the value of $\Delta W$ is large enough, the approximation does not hold even for disks with a fairly low value of magnetization.
 
@@
 %\end{equation}
-where we have used the definition of magnetic pressure and the definition of the magnetisation parameter $\beta$.
+where we have used the definition of magnetic pressure and the definition of the magnetization parameter $\beta$.
 Using their corresponding definitions, we can also compute $h_{\mathrm{c}}$, $p_{\mathrm{c}}$, $p_{\mathrm{m_c}}$ and the constant of the magnetic EOS $K_{\rm m}$.
@@
 The size of the disks can be best quantified by plotting the radial profiles of the rest-mass density on the equatorial plane.
-This is shown in Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetisation parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
+This is shown in Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetization parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
 From this figure we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller they become.
-We also note the presence of an extended region of high density in the unmagnetized model VII  (the mildly-magnetised case also shows this feature but to a lesser extent).
+We also note the presence of an extended region of high density in the unmagnetized model VII  (the mildly-magnetized case also shows this feature but to a lesser extent).
 This could be related to the existence of an extra gravitational well due to the scalar field distribution that overlaps with the matter distribution of the disk (as can be seen in the right panel of Fig.~\ref{comparison_mass_density} below).
@@
 As a result, the maximum values of the fluid quantities for disks around KBHsSH are significantly larger than in the Kerr BH case.
-In both cases, these values increase as $|\Delta W|$ increases, irrespective of the magnetisation, as shown in Table~\ref{HBH_disk_parameters}.
+In both cases, these values increase as $|\Delta W|$ increases, irrespective of the magnetization, as shown in Table~\ref{HBH_disk_parameters}.
 
@@
 \begin{table*}[t]
-\caption{Disc parameters and values of their relevant physical magnitudes for the KBH case.
+\caption{Disk parameters and values of their relevant physical magnitudes for the KBH case.
 For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
@@
 \caption{Angular velocity at the centre for the different models computed.
-In the first column, we present the angular velocity at the disc centre for the different KBHsSH models.
-In the second column, we present the angular velocity at the disc centre for a KBH with the same ADM quantities.\sg{to fill with the Kerr case values.}}
+In the first column, we present the angular velocity at the disk centre for the different KBHsSH models.
+In the second column, we present the angular velocity at the disk centre for a KBH with the same ADM quantities.\sg{to fill with the Kerr case values.}}
 \label{angular_velocity_table}      
@@
 \begin{table}
-\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+\caption{Central density of the disk for the different models, considering a disk with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
 In the first column, we present the value of the central density for the different KBHsSH models.
@@
 
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetisation parameter at the center ($10^{10}$, top row, and $10^{-10}$, bottom row).
-This figure shows that, for non-magnetised disks, the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
-This trend disappears with increasing magnetisation, as the disk moves closer to the horizon in such case.
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetization parameter at the center ($10^{10}$, top row, and $10^{-10}$, bottom row).
+This figure shows that, for non-magnetized disks, the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
+This trend disappears with increasing magnetization, as the disk moves closer to the horizon in such case.
 
@@
 
-For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+For the sake of comparison we build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
 Our numerical approach can handle BH spins as large as $|a-1|=10^{-10}$ \tf{Check} but such extreme cases do not add further relevant information to our discussion.
@@
 %%%%%%%%%%%%%%%%%%
-\subsection{Magnetisation profiles}
+\subsection{Magnetization profiles}
 %%%%%%%%%%%%%%%%%%
@@
 The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to our sequence of Kerr BHs with increasing spin parameter.
-For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetisation) and also higher values for $\rho_{\mathrm{max}}$ (high magnetisation).
+For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
 However, there are quantitative differences between the two cases.
@@
 At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
-As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximation to be valid in the non-magnetised regime.
-Now we can see that, in the KBHsSH case, this approximation is not valid even for mildly-magnetised discs.
+As we mentioned previously, we need a small value of $\Delta W$ for the $h \simeq 1$ approximation to be valid in the non-magnetized regime.
+Now we can see that, in the KBHsSH case, this approximation is not valid even for mildly-magnetized disks.
 
@@
 
-\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the discs.
+\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the disks.
 For this case only, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
@@
 This maximum mass should be such as our models ADM mass would be $\sim 2.5 M_{\odot}$.
-Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetisations and their Kerr ADM equivalents).
+Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetizations and their Kerr ADM equivalents).
 Finally, we compute the cgs central densities with the formula (From the book of Rezzolla \emph{Relativistic Hydrodynamics})}
@@
 Astrophysical BHs are commonly surrounded by accretion disks, either at stellar-mass scales or at supermassive scales.
-In the former case,  stellar-mass BHs surrounded by thick discs (or tori) are broadly accepted as natural end results of catastrophic events involving the coalescence and merger of compact objects, namely binary neutron stars and BH-neutron star systems (see e.g.~\cite{FaberRasio2012,Paschalidis:2016agf,Rezzolla:2017} and references therein).
+In the former case,  stellar-mass BHs surrounded by thick disks (or tori) are broadly accepted as natural end results of catastrophic events involving the coalescence and merger of compact objects, namely binary neutron stars and BH-neutron star systems (see e.g.~\cite{FaberRasio2012,Paschalidis:2016agf,Rezzolla:2017} and references therein).
 These systems are traditionally described using the paradigmatic BHs of general relativity, where the spacetime metric is given by the Kerr metric, solely characterized by the BH mass and spin.

### 2018-11-14 paper_prd.tex
work on the draft

--- 2018-11-12 paper_prd.tex
@@
 \label{radial_profiles_HBH}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
+\hspace{-0.6cm}
+\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
+\hspace{-0.6cm}
+\caption{Size of the disks.
+Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBH models.
+From left to right we show three different cases with the same ADM quantities as the KBHsSH model I, IV, and VII, respectively.}
+\label{radial_profiles_KBH}
 \end{figure*}
@@
 \tf{Using yellow is a bad choice as it cannot be seen, especially on print.
-Please change the colour of the yellow dots to some other colour or symbol.}}
+Please change the colour of the yellow dots to some other colour or symbol.}\sg{I increased the size of the dots a and added a black edge.}}
 \label{comparison_HBH_Kerr_dens_enth}
@@
 Right panel: A sequence of KBHs with increasing spin parameter.
-\tf{Change the $r$ to $R$ in the vertical labels.}}
+\tf{Change the $r$ to $R$ in the vertical labels.} \sg{Done}}
 \label{comparison_HBH_Kerr_r_m_max}
@@
 \centering          
-\begin{tabular}{c c c c c  c c c c c c c}
+\begin{tabular}{c c c c c c  c c c c c c c}
 \hline\hline       
- $a$ & $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
-\hline           
-$0$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
- \hline 
- $0.5$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
-\hline  
-$0.9$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
- \hline 
- &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
- \hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
- \hline 
-$0.9999$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
-\hline 
- &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
-\hline 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
+ $a$ & $\mathfrak{s}$ &  $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\
+\hline           
+$0$ & & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
+ \hline 
+ &  &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\ 
+ \hline 
+ &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\ 
+ \hline 
+ $0.5$ & & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
+ \hline 
+ &  &  & &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\ 
+ \hline  
+ &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\ 
+\hline  
+$0.9$ &  & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
+ \hline 
+ &  &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\ 
+ \hline 
+ &  &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\ 
+ \hline 
+$0.9999$ &  & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
+\hline 
+ &  &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\ 
+\hline 
+ &  &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
 \hline   
@@
 
-\begin{table}
-\caption{Angular velocity at the centre for the different models computed.
-In the first column, we present the angular velocity at the disc centre for the different KBHsSH models.
-In the second column, we present the angular velocity at the disc centre for a KBH with the same ADM quantities.\sg{to fill with the Kerr case values.}}
-\label{angular_velocity_table}      
-\centering          
-\begin{tabular}{c c c }
-\hline\hline       
- Model & $\Omega_{\mathrm{c}}$ & $\Omega_{\mathrm{ADM_c}}$ \\ 
-\hline           
-I & $0.493$ & $-$ \\ 
- \hline 
-II & $0.424$ & $--$ \\
- \hline 
-III & $0.521$ & $-$ \\ 
- \hline 
-IV & $0.427$ & $-$ \\ 
- \hline 
-V & $0.394$ & $-$ \\ 
- \hline 
-VI & $0.350$ & $-$ \\ 
- \hline 
-VII & $0.330$ & $-$ \\ 
-\hline      
-\end{tabular}
-\end{table}
-
-\begin{table}
+\begin{table*}[t]
 \caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
@@
 \centering          
-\begin{tabular}{c c c c }
+\begin{tabular}{c c c c c c c c c}
 \hline\hline       
- Model & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{ADM_c}}$ \\ 
-\hline           
-I & $10^{10}$ & $0.002051$ & $-$ \\ 
- \hline 
- & $1$ & $0.00434$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.00531$ & $-$ \\ 
- \hline 
-II & $10^{10}$ & $0.00150$ & $-$ \\ 
- \hline 
- & $1$ & $0.00427$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.00582$ & $-$ \\ 
- \hline 
-III & $10^{10}$ & $0.00304$ & $-$ \\ 
- \hline 
- & $1$ & $0.00840$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.0108$ & $-$ \\ 
- \hline 
-IV & $10^{10}$ & $0.00407$ & $-$ \\ 
- \hline 
- & $1$ & $0.00897$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.0110$ & $-$ \\ 
- \hline 
-V & $10^{10}$ & $0.00577$ & $-$ \\ 
- \hline 
- & $1$ & $0.0104$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.0121$ & $-$ \\ 
- \hline 
-VI & $10^{10}$ & $0.00762$ & $-$ \\ 
- \hline 
- & $1$ & $0.0116$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.0131$ & $-$ \\ 
- \hline 
-VII & $10^{10}$ & $0.0129$ & $-$ \\ 
- \hline 
- & $1$ & $0.0162$ & $-$ \\ 
- \hline 
- & $10^{-10}$ & $0.01701$ & $-$ \\ 
+ Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}} (\mathrm{g} \dot cm^{-3})$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}(\mathrm{g} \dot cm^{-3})$ & $\mathfrak{s}_{\mathrm{ADM}}$ \\
+\hline           
+I & $0.493$ & $10^{10}$ & $6.818 \times 10^{-4}$ & & $0.854$ & $3.752 \times 10^{-3}$ &   & $1.589$ \\ 
+ \hline 
+ & & $1$ & $2.185 \times 10^{-3}$ & & & $7.942 \times 10^{-3}$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $3.227 \times 10^{-3}$ & & & $7.641 \times 10^{-3}$ & & \\ 
+ \hline 
+II & $0.424$ & $10^{10}$ & $3.216 \times 10^{-4}$ & & $-$ & $-$ & & $-$ \\ 
+ \hline 
+ & & $1$ & $1.651 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $3.026 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+III & $0.521$ & $10^{10}$ & $8.120 \times 10^{-4}$ & & $0.163$ & $-$ & & $1.278$ \\ 
+ \hline 
+ & & $1$ & $3.497 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $5.452 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+IV & $0.427$ & $10^{10}$ & $1.197 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
+ \hline 
+ & & $1$ & $3.421 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $5.135 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+V & $0.394$ & $10^{10}$ & $1.792 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
+ \hline 
+ & & $1$ & $3.883 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $5.435 \times 10^{-3} $ & & & $-$ & & \\ 
+ \hline 
+VI & $0.350$ & $10^{10}$ & $2.348 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
+ \hline 
+ & & $1$ & $4.106 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $5.685 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+VII & $0.330$ & $10^{10}$ & $3.737 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
+ \hline 
+ & & $1$ & $5.356 \times 10^{-3}$ & & & $-$ & & \\ 
+ \hline 
+ & & $10^{-10}$ & $7.598 \times 10^{-3}$ & & & $-$ & & \\ 
  \hline     
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
-Our numerical approach can handle BH spins as large as $|a-1|=10^{-10}$ \tf{Check} but such extreme cases do not add further relevant information to our discussion.
+Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ \sg{Done}\tf{Check} but such extreme cases do not add further relevant information to our discussion.
 Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
@@
 
-\sg{Compare the radial profiles.}
+In Fig~\ref{radial_profiles_KBH}, we show three KBH models with the same ADM mass and angular momentum as the cases shown in Fig.~\ref{radial_profiles_HBH}.
+The first case corresponds to a near-extremal KBH ($a = 0.9987$) and the other two have a similar value for spin parameter ($0.8489$ and $0.8941$ respectively).
+Direct comparison between this models and the KBHsSH ones, draws out very interesting features of these models.
+It can be seen that, for model I, the disc in the Kerr case is considerably smaller than its hairy counterpart...
+
 \sg{Describe and compare the angular velocity at the centre.}
@@
 This implies that, while the $w = \rho h \simeq \rho$ approximation (employed in~\cite{Komissarov:2006,Gimeno-Soler:2017}) is valid for magnetized disks ($\beta_{\mathrm{m_c}} \sim 1$) around Kerr BHs for values of the spin parameter as high as $a \sim 0.99$, that is not the case for disks around KBHsSH.
-We note that for the most extreme spin value we can build, $a=XXX$, the maximum enthalpy is $h_{\rm max}=XXX$.
-\tf{Complete.}
+We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
+\tf{Complete.} \sg{Done}
 %Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).

### 2018-11-14 paper_prd.tex

@@
 This yields the same result for both equations
+
 \begin{equation}
@@
 In the second column, we present the central density for a KBH with the same ADM quantities.\sg{To fill with the Kerr case values.}}
+
 \label{central_density_table}      
@@
 \tf{Complete.} \sg{Done}
+
 %Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).

### 2018-11-16 paper_prd.tex
work on the draft

@@
  \hline 
-VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.747$ & $0.088$ & $0.9477$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
+VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.747$ & $0.088$ & $0.8644$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
  \hline 
@@
 For comparison, we also show in the second-to-last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
-\tf{Description of the sphericity.} In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in  the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+In the last column, we also include the horizon sphericity of the KBHsSH, defined in~\cite{Delgado:2018} as the quotient of the equatorial and polar proper lengths of the event horizon
+\begin{equation}
+\mathfrak{s} = \frac{L_{\mathrm{e}}}{L_{\mathrm{p}}} = \frac{\int^{2\pi}_{0} \mathrm{d}\phi e^{F_2(r_{\mathrm{H}}, \pi/2)} r_{\mathrm{H}}}{2\int^{\pi}_{0} \mathrm{d} \theta e^{F_1(r_{\mathrm{H}}, \theta)} r_{\mathrm{H}}}.
+\end{equation}
+ \tf{Description of the sphericity.} \sg{Done} In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
 \tf{This figure has to be redone.}
@@
 \sg{It may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots).
-But I think this should go in the results section.} \tf{I agree with mentioning this in the results section.}
+But I think this should go in the results section.} \tf{I agree with mentioning this in the results section.} \sg{Added.}
 
@@
 I & $0.934$ & $-0.188$ & $0.81$ & $1.14$ & $10^{10}$ & $1.21$ & $1.00$ & $5.16 \times 10^{-2}$ & $5.50 \times 10^{-12}$ & $1.14$ & $1.26$\\
- \hline 
+
  &  &  &  &  & $1$ & $1.10$ & $1.17$ & $3.11 \times 10^{-2}$ & $2.68 \times 10^{-2}$ & $1.01$ & $1.06$\\
- \hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $1.90$ & $1.10 \times 10^{-11}$ & $7.80 \times 10^{-2}$ & $0.93$ & $0.96$\\
- \hline 
+
 II & $0.933$ & $-0.205$ & $0.75$ & $1.18$ & $10^{10}$ & $1.23$ & $1.00$ & $5.69 \times 10^{-2}$ & $6.14 \times 10^{-12}$ & $1.18$ & $1.36$\\
- \hline 
+
  &  &  &  &  & $1$ & $1.12$ & $1.19$ & $3.50 \times 10^{-2}$ & $2.97 \times 10^{-2}$ & $1.00$ & $1.07$\\
- \hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $2.01$ & $1.30 \times 10^{-11}$ & $8.99 \times 10^{-2}$ & $0.91$ & $0.94$ \\
- \hline 
+
 III & $1.060$ & $-0.362$ & $0.84$ & $1.07$ & $10^{10}$ & $1.44$ & $1.00$ & $1.09 \times 10^{-1}$ & $1.21 \times 10^{-11}$ & $1.07$ & $1.22$\\
- \hline 
+
  &  &  &  &  & $1$ & $1.23$ & $1.28$ & $7.22 \times 10^{-2}$ & $5.76 \times 10^{-2}$ & $0.95$ & $0.99$ \\
- \hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $2.74$ & $3.48 \times 10^{-11}$ & $2.06 \times 10^{-1}$ & $0.89$ & $0.91$\\
-\hline  
+
 IV & $1.160$ & $-0.547$ & $0.67$ & $1.06$ & $10^{10}$ & $1.72$ & $1.00$ & $1.82\times 10^{-1}$ & $2.09 \times 10^{-11}$ & $1.06$ & $1.34$ \\
-\hline 
+
  &  &  &  &  & $1$ & $1.38$ & $1.37$ & $1.29 \times 10^{-1}$ & $9.76 \times 10^{-2}$ & $0.85$ & $0.91$\\
-\hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $3.70$ & $7.83 \times 10^{-11}$ & $4.08\times 10^{-1}$ & $0.76$ & $0.78$ \\
-\hline   
+
 V & $1.200$ & $-0.685$ & $0.58$ & $1.07$ & $10^{10}$ & $1.98$ & $1.00$ & $2.46 \times 10^{-1}$ & $2.76 \times 10^{-11}$ & $1.07$ & $1.31$\\
-\hline 
+
  &  &  &  &  & $1$ & $1.51$ & $1.40$ & $1.78 \times 10^{-1}$ & $1.32\times 10^{-1}$ & $0.78$ & $0.87$ \\
-\hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $4.26$ & $1.18 \times 10^{-10}$ & $5.79\times 10^{-1}$ & $0.67$ & $0.69$ \\
-\hline   
+
 VI & $1.200$ & $-0.832$ & $0.43$ & $1.12$ & $10^{10}$ & $2.30$ & $1.00$ & $3.24 \times 10^{-1}$ & $3.52 \times 10^{-11}$ & $1.12$ & $1.32$ \\
-\hline 
+
  &  &  &  &  & $1$ & $1.66$ & $1.39$ & $2.28 \times 10^{-1}$ & $1.69\times 10^{-1}$ & $0.72$ & $0.86$ \\
-\hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $4.54$ & $1.57 \times 10^{-10}$ & $7.40\times 10^{-1}$ & $0.55$ & $0.59$ \\
-\hline 
+
 VII & $0.920$ & $-1.236$ & $0.18$ & $1.10$ & $10^{-10}$ & $3.44$ & $1.00$ & $6.10 \times 10^{-1}$ & $6.46 \times 10^{-11}$ & $1.10$ & $1.25$ \\
-\hline 
+
  &  &  &  &  & $1$ & $2.25$ & $1.64$ & $5.10 \times 10^{-1}$ & $3.22\times 10^{-1}$ & $0.43$ & $0.62$\\
-\hline 
+
  &  &  &  &  & $10^{-10}$ & $1.00$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
-\hline 
+\hline\hline
 \end{tabular}
@@
 The most salient feature of the morphologies shown in Figs.~\ref{models_peri_I} and~\ref{models_peri_II}, when comparing to those displayed in Figs.~\ref{models_I} and~\ref{models_II}, is the deformation of the disks in their innermost regions.
-In general, the deformations become larger the higher the BH spin and the closer the disk is to the horizon.
-Model III is the one showing the largest deformation, as $R_{\rm in}-R_{\rm H}$ attains the smallest value for this model.
-\tf{Check.} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate.
+In general, the deformations become larger the higher the horizon sphericity $\mathfrak{s}$ and the closer the disk is to the horizon.
+Model III is the one showing the largest deformation, as $(R_{\rm in}-R_{\rm H}/R_{\rm H}$ attains the smallest value for this model.
+\tf{Check.} \sg{Done} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate.
 While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimetral coordinate $R$ is not always so.
 Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III (cf.~Table~\ref{models_list}, $\mathfrak{s}=1.489$).
+Also, an interesting property of the perimeteral coordinates is that.
+for the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum.
+But for the KBHsSH cases, $2M_{\mathrm{H}} \leq R_{\mathrm{H}} \geq 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
+\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.}
 
 \sg{Discuss.
-I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \neq R_{\mathrm{H}} \neq 2M_{\mathrm{ADM}}$.
+I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \leq R_{\mathrm{H}} \geq 2M_{\mathrm{ADM}}$.
 I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass).
 I suppose this could help us to compare different models.
-In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you please include some of this information in here?}
+In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you please include some of this information in here?} \sg{Done}
 
@@
 \hline           
-$0$ & & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\ 
- \hline 
+$0$ & $1$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\
+
  &  &  &  &  &  & $1$ & $1.02$ & $1.11$ & $6.29 \times 10^{-3}$ & $5.69 \times 10^{-3}$ & $8.81$ & $9.52$\\
- \hline 
+
  &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.48$ & $1.83 \times 10^{-12}$ & $1.48 \times 10^{-2}$ & $7.70$ & $8.14$\\
- \hline 
- $0.5$ & & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\ 
- \hline 
+
+ $0.5$ & $1.053$ & $3.41$ & $-6.35 \times 10^{-2}$ & $2.99$ & $7.12$ & $10^{10}$ & $1.07$ & $1.00$ & $1.64 \times 10^{-2}$ & $1.72 \times 10^{-12}$ & $7.19$ & $8.14$\\
+
  &  &  & &  &  & $1$ & $1.03$ & $1.12$ & $9.43 \times 10^{-3}$ & $8.47 \times 10^{-3}$ & $6.05$ & $6.53$ \\
- \hline  
+
  &  &  & &  &  & $10^{-10}$ & $1.00$ & $1.53$ & $2.81 \times 10^{-12}$ & $2.23 \times 10^{-2}$ & $5.29$ & $5.59$\\
-\hline  
-$0.9$ &  & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\ 
- \hline 
+
+$0.9$ & $1.276$ & $2.63$ & $-0.129$ & $2.18$ & $3.78$ & $10^{10}$ & $1.14$ & $1.00$ & $1.64 \times 10^{-2}$ & $3.65 \times 10^{-12}$ & $3.78$ & $4.23$\\
+
  &  &  &  &  &  & $1$ & $1.07$ & $1.14$ & $2.03 \times 10^{-2}$ & $1.78 \times 10^{-2}$ & $3.25$ & $3.47$\\
- \hline 
+
  &  &  &  &  &  & $10^{-10}$ & $1.00$ & $1.70$ & $6.54 \times 10^{-12}$ & $4.92 \times 10^{-2}$ & $2.92$ & $3.04$ \\
- \hline 
-$0.9999$ &  & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\ 
-\hline 
+
+$0.9999$ & $1.629$ & $2.02$ & $-0.429$ & $2.00015$ & $2.034$ & $10^{10}$ & $1.54$ & $1.00$ & $1.34 \times 10^{-1}$ & $1.61 \times 10^{-11}$ & $2.034$ & $2.094$ \\
+
  &  &  &  &  &  & $1$ & $1.29$ & $1.51$ & $1.10 \times 10^{-1}$ & $7.52 \times 10^{-2}$ & $2.0075$ & $2.014$\\
-\hline 
+
  &  &  &  &  &  & $10^{-10}$ & $1.00$ & $6.17$ & $1.22 \times 10^{-10}$ & $4.91 \times 10^{-1}$ & $2.0021$ & $2.0030$ \\ 
-\hline   
+\hline\hline
 \end{tabular}
@@
 \begin{table*}[t]
-\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total}} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
 In the first column, we present the value of the central density for the different KBHsSH models.
-In the second column, we present the central density for a KBH with the same ADM quantities.\sg{To fill with the Kerr case values.}}
-
-\label{central_density_table}      
+In the second column, we present the central density for a KBH with the same ADM quantities.\sg{complete caption}}
+
+\label{density_table}      
 \centering          
@@
 \hline\hline       
- Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}} (\mathrm{g} \dot cm^{-3})$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}(\mathrm{g} \dot cm^{-3})$ & $\mathfrak{s}_{\mathrm{ADM}}$ \\
+ Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}} (\mathrm{g} \cdot \rm{cm}^{-3})$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}(\mathrm{g} \cdot \rm{cm}^{-3})$ & $\mathfrak{s}_{\mathrm{ADM}}$ \\
 \hline           
-I & $0.493$ & $10^{10}$ & $6.818 \times 10^{-4}$ & & $0.854$ & $3.752 \times 10^{-3}$ &   & $1.589$ \\ 
- \hline 
- & & $1$ & $2.185 \times 10^{-3}$ & & & $7.942 \times 10^{-3}$ & & \\ 
- \hline 
- & & $10^{-10}$ & $3.227 \times 10^{-3}$ & & & $7.641 \times 10^{-3}$ & & \\ 
- \hline 
-II & $0.424$ & $10^{10}$ & $3.216 \times 10^{-4}$ & & $-$ & $-$ & & $-$ \\ 
- \hline 
- & & $1$ & $1.651 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $3.026 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
-III & $0.521$ & $10^{10}$ & $8.120 \times 10^{-4}$ & & $0.163$ & $-$ & & $1.278$ \\ 
- \hline 
- & & $1$ & $3.497 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $5.452 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
-IV & $0.427$ & $10^{10}$ & $1.197 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
- \hline 
- & & $1$ & $3.421 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $5.135 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
-V & $0.394$ & $10^{10}$ & $1.792 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
- \hline 
- & & $1$ & $3.883 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $5.435 \times 10^{-3} $ & & & $-$ & & \\ 
- \hline 
-VI & $0.350$ & $10^{10}$ & $2.348 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
- \hline 
- & & $1$ & $4.106 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $5.685 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
-VII & $0.330$ & $10^{10}$ & $3.737 \times 10^{-3}$ & & $-$ & $-$ & & \\ 
- \hline 
- & & $1$ & $5.356 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline 
- & & $10^{-10}$ & $7.598 \times 10^{-3}$ & & & $-$ & & \\ 
- \hline     
+I & $0.493$ & $10^{10}$ & $6.818 \times 10^{-4}$ & $1.739 \times 10^{13}$ & $0.854$ & $3.752 \times 10^{-3}$ &  $9.567 \times 10^{13}$ & $1.589$ \\
+
+ & & $1$ & $2.185 \times 10^{-3}$ & $5.503 \times 10^{13}$ & & $7.942 \times 10^{-3}$ & $2.025 \times 10^{14}$ & \\
+
+ & & $10^{-10}$ & $3.227 \times 10^{-3}$ & $8.229 \times 10^{13}$ & & $7.641 \times 10^{-3}$ & $1.948 \times 10^{14}$ & \\
+
+II & $0.424$ & $10^{10}$ & $3.216 \times 10^{-4}$ & $8.201 \times 10^{12}$ & $-$ & $-$ & $-$ & $-$ \\
+
+ & & $1$ & $1.651 \times 10^{-3}$ & $4.210 \times 10^{13}$ & $-$ & $-$ & $-$ & $-$ \\
+
+ & & $10^{-10}$ & $3.026 \times 10^{-3}$ & $7.716 \times 10^{13}$ & $-$ & $-$ & $-$ & $-$ \\
+
+III & $0.521$ & $10^{10}$ & $8.120 \times 10^{-4}$ & $2.071 \times 10^{13}$ & $0.163$ & $6.683 \times 10^{-5}$ & $1.704 \times 10^{12}$ & $1.278$ \\
+
+ & & $1$ & $3.497 \times 10^{-3}$ & $8.917 \times 10^{13}$ & & $2.075 \times 10^{-4}$ & $5.291 \times 10^{12}$ & \\
+
+ & & $10^{-10}$ & $5.452 \times 10^{-3}$ & $1.390 \times 10^{14}$ & & $3.265 \times 10^{-4}$ & $8.325 \times 10^{12}$ & \\
+
+IV & $0.427$ & $10^{10}$ & $1.197 \times 10^{-3}$ & $3.052 \times 10^{13}$ & $0.113$ & $3.001 \times 10^{-5}$ & $7.652 \times 10^{11}$ & $1.219$ \\
+
+ & & $1$ & $3.421 \times 10^{-3}$ & $8.723 \times 10^{13}$ & & $9.512 \times 10^{-5}$ & $2.425 \times 10^{12}$ & \\
+
+ & & $10^{-10}$ & $5.135 \times 10^{-3}$ & $1.309 \times 10^{14}$ & & $1.533 \times 10^{-4}$ & $3.909 \times 10^{12}$ & \\
+
+V & $0.394$ & $10^{10}$ & $1.792 \times 10^{-3}$ & $4.569 \times 10^{13}$ & $0.115$ & $3.152 \times 10^{-5}$ & $8.037 \times 10^{11}$ & $1.227$\\
+
+ & & $1$ & $3.883 \times 10^{-3}$ & $9.901 \times 10^{13}$ & & $9.942 \times 10^{-5}$ & $2.535 \times 10^{12}$ & \\
+
+ & & $10^{-10}$ & $5.435 \times 10^{-3} $ & $1.386 \times 10^{14}$ & & $1.596 \times 10^{-4}$ & $4.070 \times 10^{12}$ & \\
+
+VI & $0.350$ & $10^{10}$ & $2.348 \times 10^{-3}$ & $5.987 \times 10^{13}$ & $0.117$ & $3.232 \times 10^{-5}$ & $8.241 \times 10^{11}$ & $1.234$\\
+
+ & & $1$ & $4.106 \times 10^{-3}$ & $1.047 \times 10^{14}$ & & $1.019 \times 10^{-4}$ & $2.598 \times 10^{12}$ & \\
+
+ & & $10^{-10}$ & $5.685 \times 10^{-3}$ & $1.450 \times 10^{14}$ & & $1.632 \times 10^{-4}$ & $4.161 \times 10^{12}$ & \\
+
+VII & $0.330$ & $10^{10}$ & $3.737 \times 10^{-3}$ & $9.529 \times 10^{13}$ & $0.129$ & $4.114 \times 10^{-5}$ & $1.049 \times 10^{12}$ & $1.268$\\
+
+ & & $1$ & $5.356 \times 10^{-3}$ & $1.366 \times 10^{14}$ & & $1.280 \times 10^{-4}$ & $3.264 \times 10^{12}$ & \\
+
+ & & $10^{-10}$ & $7.598 \times 10^{-3}$ & $1.937 \times 10^{14}$ & & $2.021 \times 10^{-4}$ & $5.153 \times 10^{12}$ & \\ 
+ \hline\hline   
 \end{tabular}
@@
 For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
-Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ \sg{Done}\tf{Check} but such extreme cases do not add further relevant information to our discussion.
+Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid.
+For higher values of the spin parameter, we would need to increase our resolution (specially the $\theta$ resolution for the highly magnetised case)\sg{Done}\tf{Check} but such extreme cases do not add further relevant information to our discussion.
 Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
 As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$.
-It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.
+It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$ (note that, as we mentioned before in the Kerr case, the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the spin $a$).
+Regarding the physical quantities, we can see that, even for highly rotating KBHs, the maximum values for the $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case.
+This is not a surprise, as these quantities are related to the value of $|\Delta W|$.
+Also, as in the case of KBHsSH, we observe a higher distorsion of the shape of the disc in the near-horizon region with increasing sphericity $\mathfrak{s}$ (and spin, in this particular case).
 \tf{Describe further the table and the figures}.
-\tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.}
+\tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.} \sg{Done}
 
 Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
+In particular, we can see the well-known behaviour of these models, as the disc reduces its size and tends to attach to the horizon as the spin parameter increases.
+This cannot be particularly be seen in figure~\ref{models_Kerr}, as the radial coordinate expands the near-horizon region and, while it is well suited to do the computations, this is not the case for visualization.
+However, using perimeteral coordinates (figure~\ref{models_Kerr_peri}), we can see the disc attaching to the horizon and the subsequent deformation clearly.
+\sg{complete}
 
@@
 The first case corresponds to a near-extremal KBH ($a = 0.9987$) and the other two have a similar value for spin parameter ($0.8489$ and $0.8941$ respectively).
-Direct comparison between this models and the KBHsSH ones, draws out very interesting features of these models.
-It can be seen that, for model I, the disc in the Kerr case is considerably smaller than its hairy counterpart...
-
-\sg{Describe and compare the angular velocity at the centre.}
+Direct comparison between these models and the KBHsSH ones, draws out very interesting features of these models.
+It can be seen that, for model I, the disc in the Kerr case is considerably smaller than its hairy counterpart.
+In this case, the scalar field has little effect on the morphology of the disc (as its gravitational field is small), but its effect is noted in a reduction of the value of the sphericity (see Table~\ref{density_table}), effectively reducing the effects of the black hole spin in the disc (i.e.~increasing its shape).
+As the mass and angular momentum stored in the scalar field increase, the gravitational field of the scalar field affects the radial morphology of the disc, altering its shape and reducing its extent.
+Note that both model IV and model VII have lesser radial extent than its KBH counterparts, even though model VII has a lower value of the sphericity.
+
+In Table~\ref{density_table}, we also present the value of the angular velocity at the disc centre (both for the KBHsSH case and for their KBH counterparts).
+It can be seen that, with the exception of the first case, the values of the angular velocity of the Kerr cases are lower than \sg{I need to think a bit about this.}
 
@@
 %%%%%%%%%%%%%%%%%%
+
+Even though the models we have computed are non self-gravitating, for the sake of astrophysical relevance, we computed the accretion torus mass for the different KBHsSH models and also, for comparison, the torus mass for seven models of Kerr BHs, each one with the same ADM quantities as their KBHsSH counterparts.
+For this particular section, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
+Also, to avoid complications due to the infinite size of our models, we have chosen the total potential well as the $90\%$ of its maximum possible value.
+This is in agreement with the torus masses found as the final state of binary neutron stars mergers (see, for instance~\cite{Rezzolla:2010}).
+\sg{I think we should check and include more references.} As we have fixed the value of the mass of the torus, now we have to compute the new value of the central density for each model.
+In the fourth (KBHSH) and seventh (Kerr) columns of table~\ref{density_table} we report the resulting central densities we found.
+Now, in order to compare our results with the end-product of a binary neutron star merger, we need to convert our result to cgs units.
+To this end, we first need to choose a mass for the scalar field $\mu$ (as the maximum ADM mass of KBHsSH are related to $\mu$).
+To compute the maximum ADM mass with the followimg equation (see~\cite{Delgado:2018} and references therein)
+\begin{equation}
+M^{max}_{ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{GeV}{\mu}\right) \mathrm{GeV}\,
+\end{equation}
+for a value of $\alpha_{\mathrm{BS}} = 1.315$.
+Using a value of the mass of $\mu = 2.087 \times 10^{-11} \mathrm{eV}$ gives us the following values for the ADM mass of our models, from model I to VII ($2.043$, $3.100$, $3.923$, $4.592$, $4.627$, $4.720$, $4.799$) in units of the mass of the sun $M_{\odot}$.
+Note that (as is mentioned in~\cite{Ramazanoglu:2016}) the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
+\sg{not sure about this last comment, but I think something should be told about $\mu$.}
+
+In columns five (KBHSH) to eight (Kerr) of table~\ref{density_table}, we report the values of the central density in cgs units we have found for each model.
+The found values are between  $\sim 10^{11}$ and $\sim 10^{14} \mathrm{g} \cdot \mathrm{cm}^{-3}$.
+This great range is due to the great difference in the disc size for the different models, specially between the Kerr and KBHsSH cases).
+Comparing these values to the ones in the avalaible literature (see~\cite{Rezzolla:2010} \sg{we need more references.}) we can see that, considering that our assumptions are quite unrealistic, they are within a reasonable margin of the central densities found in discs as the end-product of numerical simulations of a binary neutron star merger.
+Changing the rotation law and the EOS to a more realistic one is expected to improve the accuracy of our results.
 

### 2018-11-17 paper_prd.tex

@@
 Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
-We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
+We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a = J/M$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
 
@@
 \begin{equation}\label{eq:diff_ver}
-\partial_i(|\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
+\partial_i(\ln |u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
 \end{equation}
@@
 In general, the deformations become larger the higher the horizon sphericity $\mathfrak{s}$ and the closer the disk is to the horizon.
-Model III is the one showing the largest deformation, as $(R_{\rm in}-R_{\rm H}/R_{\rm H}$ attains the smallest value for this model.
+Model III is the one showing the largest deformation, as $R_{\rm in}-R_{\rm H}/R_{\rm H}$ attains the smallest value for this model.
 \tf{Check.} \sg{Done} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate.
@@
 Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III (cf.~Table~\ref{models_list}, $\mathfrak{s}=1.489$).
-Also, an interesting property of the perimeteral coordinates is that.
-for the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum.
-But for the KBHsSH cases, $2M_{\mathrm{H}} \leq R_{\mathrm{H}} \geq 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
+Also, an interesting property of the perimeteral coordinates is that, for the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum.
+But for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
 \sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.}
@@
 \sg{Discuss.
-I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} \leq R_{\mathrm{H}} \geq 2M_{\mathrm{ADM}}$.
+I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$.
 I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass).

### 2018-11-18 paper_prd.tex
A little minor thing.
Some polishing. More to follow.

@@
-%-----------------------------------------------------------------------
-%
-% filename = nube.tex
-%
-% First version: February 2012
-% Last revision: April 2012
-%
-%-----------------------------------------------------------------------
-
 \documentclass[twocolumn,aps,showpacs,showkeys,prd,superscriptaddress,byrevtex, amsmath]{revtex4-1}
@@
 It is therefore an intriguing open possibility if the very long baseline interferometric observations of BH candidates in Sgr A* and M87 envisaged by the EHT may constrain the astrophysical significance of HBHs.
-
-The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}.
-Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein).
-In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}.
-Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
-In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
-Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
-In this investigation we focus on disks with a constant distribution of specific angular momentum.
-In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}).
-In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
-The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
-
-The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH.
-Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks.
-Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties.
-Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
-Geometrized units ($G=c=1$) are used throughout.
-
-%%%%%%%%%%%
-\section{Framework}
-\label{framework}
-%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spacetime metric and KBHsSH models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}.
+Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein).
+In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}.
+Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
+In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
+In this investigation we focus on disks with a constant distribution of specific angular momentum.
+In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}).
+In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
+The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
+
+The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH.
+Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks.
+Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties.
+Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
+Geometrized units ($G=c=1$) are used throughout.
+
+%%%%%%%%%%%
+\section{Framework}
+\label{framework}
+%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spacetime metric and KBHsSH models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
@@
 This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds the speed of light.
-For comparison, we also show in the second-to-last column of Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
-In the last column, we also include the horizon sphericity of the KBHsSH, defined in~\cite{Delgado:2018} as the quotient of the equatorial and polar proper lengths of the event horizon
-\begin{equation}
-\mathfrak{s} = \frac{L_{\mathrm{e}}}{L_{\mathrm{p}}} = \frac{\int^{2\pi}_{0} \mathrm{d}\phi e^{F_2(r_{\mathrm{H}}, \pi/2)} r_{\mathrm{H}}}{2\int^{\pi}_{0} \mathrm{d} \theta e^{F_1(r_{\mathrm{H}}, \theta)} r_{\mathrm{H}}}.
-\end{equation}
- \tf{Description of the sphericity.} \sg{Done} In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
-\tf{This figure has to be redone.}
+For comparison, we also show in Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
+In the last column of Table~\ref{models_list} we indicate the horizon sphericity of the KBHsSH, defined in~\cite{Delgado:2018} as the quotient of the equatorial and polar proper lengths of the event horizon
+\begin{equation}
+\mathfrak{s} = \frac{L_{\mathrm{e}}}{L_{\mathrm{p}}} = \frac{\int^{2\pi}_{0} \mathrm{d}\phi \, e^{F_2(r_{\mathrm{H}}, \pi/2)} r_{\mathrm{H}}}{2\int^{\pi}_{0} \mathrm{d} \theta \, e^{F_1(r_{\mathrm{H}}, \theta)} r_{\mathrm{H}}}\,.
+\end{equation}
+In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+\tf{This figure has to be redone by Carlos.}
 
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but using the perimetral radial coordinate $R$.}
+\caption{Same as Fig.~\ref{models_I} but using the perimeteral radial coordinate $R$.}
 \label{models_peri_I}
@@
 \hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_II} but using the perimetral radial coordinate $R$.}
+\caption{Same as Fig.~\ref{models_II} but using the perimeteral radial coordinate $R$.}
 \label{models_peri_II}
@@
 
-In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimetral radial coordinate $R$, related to the radial coordinate $r$ according to $R = e^{F_2} r$.
-This perimetral coordinate represents the proper length along the azimuthal direction, which constitutes a geometrically meaningful direction since it runs along the orbits of the azimuthal Killing vector field.
-Therefore, the proper size of a full $\phi$ orbit is given by $2\pi R$, i.e.~$R$ is the perimetral radius.
+In figures~\ref{models_peri_I} and~\ref{models_peri_II} we show the same morphological distribution of Figs.~\ref{models_I} and~\ref{models_II} but using, instead, a perimeteral radial coordinate $R$, related to the radial coordinate $r$ according to $R = e^{F_2} r$.
+This perimeteral coordinate represents the proper length along the azimuthal direction, which constitutes a geometrically meaningful direction since it runs along the orbits of the azimuthal Killing vector field.
+Therefore, the proper size of a full $\phi$ orbit is given by $2\pi R$, i.e.~$R$ is the perimeteral radius.
 The most salient feature of the morphologies shown in Figs.~\ref{models_peri_I} and~\ref{models_peri_II}, when comparing to those displayed in Figs.~\ref{models_I} and~\ref{models_II}, is the deformation of the disks in their innermost regions.
 In general, the deformations become larger the higher the horizon sphericity $\mathfrak{s}$ and the closer the disk is to the horizon.
-Model III is the one showing the largest deformation, as $R_{\rm in}-R_{\rm H}/R_{\rm H}$ attains the smallest value for this model.
-\tf{Check.} \sg{Done} It is also worth noticing that the shape of the BH also changes when using the perimetral coordinate.
-While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimetral coordinate $R$ is not always so.
+Model III is the one showing the largest deformation, as $(R_{\rm in}-R_{\rm H})/R_{\rm H}$ attains the smallest value for this model.
+It is also worth noticing that the shape of the BH also changes when using the perimeteral coordinate.
+While in the $r$ coordinate the horizon is spherical (cf.~Figs.~\ref{models_I} and~\ref{models_II}) in the perimeteral coordinate $R$ is not always so.
 Moreover, the larger the value of $v_{\rm H}$, the more elliptic the horizon becomes, which in our sample corresponds to model III (cf.~Table~\ref{models_list}, $\mathfrak{s}=1.489$).
-Also, an interesting property of the perimeteral coordinates is that, for the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum.
-But for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
+
+In addition, an interesting geometrical property of the perimeteral coordinates is that, for the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum.
+However, for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
 \sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.}
@@
 %\hspace{-0.2cm}
-%\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimetral radial coordinate.
+%\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimeteral radial coordinate.
 \tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
@@
 In the first row, we show this for all of our KBHsSH models.
-In the second row, we show this for a sequence of Kerr BHs with increasing spin parameter.
-\tf{Using yellow is a bad choice as it cannot be seen, especially on print.
-Please change the colour of the yellow dots to some other colour or symbol.}\sg{I increased the size of the dots a and added a black edge.}}
+In the second row, we show this for a sequence of Kerr BHs with increasing spin parameter.}
 \label{comparison_HBH_Kerr_dens_enth}
@@
 Left panel: KBHsSH models.
-Right panel: A sequence of KBHs with increasing spin parameter.
-\tf{Change the $r$ to $R$ in the vertical labels.} \sg{Done}}
+Right panel: A sequence of KBHs with increasing spin parameter.}
 \label{comparison_HBH_Kerr_r_m_max}
@@
 \hline\hline       
- Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}} (\mathrm{g} \cdot \rm{cm}^{-3})$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}(\mathrm{g} \cdot \rm{cm}^{-3})$ & $\mathfrak{s}_{\mathrm{ADM}}$ \\
+ Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}}$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\mathfrak{s}_{\mathrm{ADM}}$
+ \\
+ & & & & $[\mathrm{g} \, \rm{cm}^{-3}]$ & & & $[\mathrm{g} \, \rm{cm}^{-3}]$ & 
+  \\ 
 \hline           
@@
 
-For the sake of comparison we build equilibrium sequences of magnetised disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+For the sake of comparison we build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
 Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid.
-For higher values of the spin parameter, we would need to increase our resolution (specially the $\theta$ resolution for the highly magnetised case)\sg{Done}\tf{Check} but such extreme cases do not add further relevant information to our discussion.
+For higher values of the spin parameter, we would need to increase our resolution (especially the resolution along the polar angle $\theta$ for the most highly magnetized case) but such extreme cases do not add further relevant information to our discussion.
 Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
@@
 \tf{Describe further the table and the figures}.
-\tf{Mention that the horizon location is constant in perimetral coordinates irrespective of $a$.} \sg{Done}
+\tf{Mention that the horizon location is constant in perimeteral coordinates irrespective of $a$.} \sg{Done}
 
@@
 
-Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimetral radius of the magnetic pressure maximum and the perimetral radius of the disk center, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the center of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimeteral radius of the magnetic pressure maximum and the perimeteral radius of the disk center, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the center of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
 The curves plotted correspond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.
@@
 \bibliographystyle{apsrev4-1}
-\bibliography{references.bib}
+\bibliography{references}
 

### 2018-11-18 paper_prd.tex
Further polishing.

@@
 
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig1_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_I_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_I__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_II_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_II_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_II__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_III_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_III_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_III__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_IV_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_IV__10.pdf}
-\hspace{-0.2cm}
-\caption{Distribution of the rest-mass density.
-From top to bottom the rows correspond to the first four models of KBHsSH (I, II, III and IV).
-From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
-Note that the range of the colour scale is not the same for all plots.}
-\label{models_I}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[scale=0.14]{figures/fig2_V_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_V_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_V__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig2_VI_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_VI_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_VI__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig2_VII_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_VII_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_VII__10.pdf}
-\hspace{-0.2cm}
-\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII).}
-\label{models_II}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig1_I_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig1_I_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig1_I__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig1_II_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig1_II_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig1_II__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig1_III_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig1_III_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig1_III__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig1_IV_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig1_IV_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig1_IV__10.pdf}
+\hspace{-0.2cm}
+\caption{Distribution of the rest-mass density.
+From top to bottom the rows correspond to the first four models of KBHsSH (I, II, III and IV).
+From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$).
+Note that the range of the colour scale is not the same for all plots.}
+\label{models_I}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[scale=0.14]{figures/fig2_V_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig2_V_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig2_V__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig2_VI_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig2_VI_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig2_VI__10.pdf}
+\\
+\includegraphics[scale=0.14]{figures/fig2_VII_10.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/fig2_VII_1.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/fig2_VII__10.pdf}
+\hspace{-0.2cm}
+\caption{Same as Fig.~\ref{models_I} but for the last three models of KBHsSH (V, VI, and VII).}
+\label{models_II}
+\end{figure*}
+
 We can also define the total energy density for the torus, $\rho_{\mathrm{T}}=-T^t_t + T^i_i$, and for the scalar field, $\rho_{\mathrm{SF}}=-(T_{\mathrm{SF}})^t_t + (T_{\mathrm{SF}})^i_i$.
@@
 \hspace{-0.6cm}
-\caption{Size of the disks.
-Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
-From left to right we show model I, IV, and VII, respectively.}
-\label{radial_profiles_HBH}
-\end{figure*}
-
-\begin{figure*}
-\centering
+\\
+\hspace{-0.6cm}
 \includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
@@
 \caption{Size of the disks.
+Top panel: Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models.
+From left to right we show model I, IV, and VII, respectively.
+Bottom panel: same as the top panel but for Kerr BHs.
+From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.}
+\label{radial_profiles_HBH}
+\end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
+%\hspace{-0.6cm}
+%\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
+%\hspace{-0.6cm}
+%\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
+%\hspace{-0.6cm}
+%\caption{Size of the disks.
 Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBH models.
 From left to right we show three different cases with the same ADM quantities as the KBHsSH model I, IV, and VII, respectively.}
-\label{radial_profiles_KBH}
-\end{figure*}
+%\label{radial_profiles_KBH}
+%\end{figure*}
 
@@
 \begin{table*}[t]
-\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH. For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.}       
+\caption{Values of the relevant physical magnitudes of our models of magnetized, equilibrium tori around KBHsSH.
+All reported radii correspond to the perimeteral coordinate.
+For all cases,  $R_{\mathrm{in}} = R_{\mathrm{mb}}$ and $l = l_{\mathrm{mb}}$.
+From left to right the columns report: the specific angular momentum, $l$, the potential at the centre of the disk, $W_{\mathrm{c}}$, the inner radius of the disk, $R_{\mathrm{in}}$, its centre, $R_{\mathrm{c}}$, the value of the magnetization parameter at the centre, $\beta_{\mathrm{m_{\mathrm{c}}}}$, the maximum specific enthalpy, $h_{\mathrm{max}}$, density,  $\rho_{\mathrm{max}}$, thermal pressure, $p_{\mathrm{max}}$, and magnetic pressure, $p_{\mathrm{m, max}}$, and the location of the maximum of the thermal pressure and magnetic pressure, $R_{\mathrm{max}}$ and $R_{\mathrm{m, max}}$, respectively.}
 \label{HBH_disk_parameters}      
@@
 The structure of the disks is similar for all values of $\beta_{\mathrm{m_c}}$ with the only quantitative differences being the location of the centre of the disk, which moves closer to the BH as the magnetization increases, and the range of variation of the isodensity contours, whose upper ends become larger with decreasing $\beta_{\mathrm{m_c}}$.
-This behaviour is in complete agreement with that found for KBHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
-For the particular case of Model VII, the maximum of the rest-mass density for the strongly magnetized case is significantly larger than for the other models and the spatial extent of the disk is significantly small.
+This behaviour is in complete agreement with that found for Kerr BHs in~\cite{Gimeno-Soler:2017} irrespective of the BH spin.
+For the particular case of Model VII, the maximum of the rest-mass density for the strongly magnetized case is significantly larger than for the other models and the spatial extent of the disk is fairly small.
 
 The size of the disks can be best quantified by plotting the radial profiles of the rest-mass density on the equatorial plane.
-This is shown in Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetization parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
-From this figure we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller they become.
+This is shown in the upper panels of Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetization parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
+(The lower panels of this figure correspond to disks around Kerr BHs and will be discussed below.) From Fig.~\ref{radial_profiles_HBH} we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller the disks become.
 We also note the presence of an extended region of high density in the unmagnetized model VII  (the mildly-magnetized case also shows this feature but to a lesser extent).
@@
 However, for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
-\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.}
-
-\sg{Discuss.
+\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.} \tf{Any comment, Carlos?}
+
+%\sg{Discuss.
 I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$.
@@
 \caption{Rest-mass density distribution.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From top to bottom the rows correspond to a sequence of Kerr BHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
 From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
@@
 \caption{Rest-mass density distribution using perimeteral coordinates.
-From top to bottom the rows correspond to a sequence of KBHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
+From top to bottom the rows correspond to a sequence of Kerr BHs with increasing spin parameter $a$ (0, 0.5, 0.9 and 0.9999).
 From left to right the columns correspond to different values of the magnetization parameter, namely non-magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{10}$), mildly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$) and strongly magnetized ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-10}$)}
@@
 Left panel: KBHsSH models.
-Right panel: A sequence of KBHs with increasing spin parameter.}
+Right panel: A sequence of Kerr BHs with increasing spin parameter.}
 \label{comparison_HBH_Kerr_r_m_max}
@@
 \begin{table*}[t]
-\caption{Disk parameters and values of their relevant physical magnitudes for the KBH case.
-For all the cases, we have $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.}
+\caption{Disk parameters and values of their relevant physical magnitudes for the Kerr BH case.
+For all models, $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.
+\tf{Complete description.}}
 \label{KBH_disk_parameters}      
@@
 
-In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetization parameter at the center ($10^{10}$, top row, and $10^{-10}$, bottom row).
+In figure~\ref{comparison_mass_density} we show the total energy density of the torus $\rho_{\mathrm{T}}$ (upper half of each image) and the total energy density of the scalar field $\rho_{\mathrm{SF}}$ (lower half) for models I, IV and VII and two  values of the magnetization parameter at the centre ($10^{10}$, top row, and $10^{-10}$, bottom row).
 This figure shows that, for non-magnetized disks, the maximum of the total energy density of the disk $\rho_{\mathrm{T}}$ is closer to the maximum of the total energy density of the scalar field $\rho_{\mathrm{SF}}$ for increasing hair.
@@
 
-For the sake of comparison we build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
 Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid.
-For higher values of the spin parameter, we would need to increase our resolution (especially the resolution along the polar angle $\theta$ for the most highly magnetized case) but such extreme cases do not add further relevant information to our discussion.
-Table~\ref{KBH_disk_parameters} reports a summary of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
+However, for higher values of the spin parameter, we would need to increase our resolution (especially the resolution along the polar angle $\theta$ for the most highly magnetized case) but such extreme cases do not add further relevant information to our discussion.
+Table~\ref{KBH_disk_parameters} reports a summary of the values of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}.
 As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$.
-It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$ (note that, as we mentioned before in the Kerr case, the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the spin $a$).
-Regarding the physical quantities, we can see that, even for highly rotating KBHs, the maximum values for the $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case.
+It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.
+(Note that, as we mentioned before, in the Kerr case the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the BH spin.)
+
+%HERE
+
+The comparison of the values of the physical quantities shows that, even for highly rotating Kerr BHs, the maximum values for $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case.
 This is not a surprise, as these quantities are related to the value of $|\Delta W|$.
@@
 
-Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimeteral radius of the magnetic pressure maximum and the perimeteral radius of the disk center, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the center of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
+Figure~\ref{comparison_HBH_Kerr_r_m_max} shows the relative variation of the quotient of the perimeteral radius of the magnetic pressure maximum and the perimeteral radius of the disk centre, $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$, with the decimal logarithm of the magnetization parameter at the centre of the disk, $\log_{10} \beta_{\mathrm{m_c}}$.
 The curves plotted correspond to the same KBHsSH and Kerr BH cases as those in figure~\ref{comparison_HBH_Kerr_dens_enth}.

### 2018-11-19 paper_prd.tex
More work.

@@
 
-In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein).
+In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and in modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein).
 Among those, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
@@
 It is therefore an intriguing open possibility if the very long baseline interferometric observations of BH candidates in Sgr A* and M87 envisaged by the EHT may constrain the astrophysical significance of HBHs.
+
+The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}.
+Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein).
+In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}.
+Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
+In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
+Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
+In this first investigation we focus on disks with a constant distribution of specific angular momentum.
+In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}).
+In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
+The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
+
+The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH.
+Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks.
+Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties and the comparison with models around Kerr BHs.
+Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
+Geometrized units ($G=c=1$) are used throughout.
+
+%%%%%%%%%%%
+\section{Framework}
+\label{framework}
+%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spacetime metric and KBHsSH models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
+The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity.
+KBHsSH solutions are obtained by using the following ansatz for the metric and the scalar field~\cite{Herdeiro:2014a}
+\begin{eqnarray}
+%\begin{split}
+\mathrm{d}s^2 &=& e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) +  e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 
+\nonumber \\ 
+&-&  e^{2F_0}N\mathrm{d}t^2\,,
+\label{metric}
+\end{eqnarray}
+\begin{eqnarray}
+\Psi = \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
+%\end{split}
+\end{eqnarray}
+with $N = 1 - r_{\rm H}/r$, where $r_{\rm H}$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
+Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
+We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a = J/M$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
+
+The stationary and axisymmetric metric ansatz is a solution to the EKG field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi (T_{\mathrm{SF}})_{ab}$ with 
+\begin{eqnarray}\label{eq:e-m_scalaf_field}
+(T_{\mathrm{SF}})_{ab} &=& \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi 
+\nonumber \\ 
+&-& g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
+\end{eqnarray}
+where $\mu$ is the mass of the scalar field and superscript $(^*)$ denotes complex conjugation.
+The interested reader is addressed to~\cite{Herdeiro:2015b} for details on the equations of motion for the scalar field $\Psi$ and the four metric functions ${W, F_0,F_1,F_2}$, along with their solution.
 
@@
 
-The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}.
-Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein).
-In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}.
-Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case.
-In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed.
-Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH.
-In this investigation we focus on disks with a constant distribution of specific angular momentum.
-In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}).
-In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.
-The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.
-
-The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH.
-Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks.
-Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties.
-Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}.
-Geometrized units ($G=c=1$) are used throughout.
-
-%%%%%%%%%%%
-\section{Framework}
-\label{framework}
-%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Spacetime metric and KBHsSH models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The models of KBHsSH we use in this study are built following the procedure described in~\cite{Herdeiro:2015b}.
-The underlying theoretical framework is the Einstein-Klein-Gordon (EKG) field theory, describing a massive complex scalar field $\Psi$ minimally coupled to Einstein gravity.
-KBHsSH solutions are obtained by using the following ansatz for the metric and the scalar field~\cite{Herdeiro:2014a}
-\begin{eqnarray}
-%\begin{split}
-\mathrm{d}s^2 &=& e^{2F_1}\left(\frac{\mathrm{d}r^2}{N} + r^2\mathrm{d}\theta^2\right) +  e^{2F_2}r^2\sin^2 \theta(\mathrm{d}\phi-W\mathrm{d}t)^2 
-\nonumber \\ 
-&-&  e^{2F_0}N\mathrm{d}t^2\,,
-\label{metric}
-\end{eqnarray}
-\begin{eqnarray}
-\Psi = \phi(r, \theta) e^{\mathrm{i}(m\varphi - \omega t)} \,,
-%\end{split}
-\end{eqnarray}
-with $N = 1 - r_{\rm H}/r$, where $r_{\rm H}$ is the radius of the event horizon of the BH, and $W$, $F_1$, $F_2$, $F_0$ are functions of $r$ and $\theta$.
-Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
-We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a = J/M$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
-
-The stationary and axisymmetric metric ansatz is a solution to the EKG field equations $R_{ab} - \frac{1}{2}R g _{ab} = 8 \pi (T_{\mathrm{SF}})_{ab}$ with 
-\begin{eqnarray}\label{eq:e-m_scalaf_field}
-(T_{\mathrm{SF}})_{ab} &=& \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi 
-\nonumber \\ 
-&-& g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
-\end{eqnarray}
-where $\mu$ is the mass of the scalar field and superscript $(^*)$ denotes complex conjugation.
-The interested reader is addressed to~\cite{Herdeiro:2015b} for details on the equations of motion for the scalar field $\Psi$ and the four metric functions ${W, F_0,F_1,F_2}$, along with their solution.
-
 Table~\ref{models_list} lists the seven KBHsSH models we use in this work.
@@
 In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}.
-This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre.
+This choice also allows for the presence of a cusp (and hence matter accretion onto the BH) and a centre.
 Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
@@
 \end{equation}
-where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits.
+where the plus sign solution corresponds to prograde orbits and the minus sign solution to retrograde orbits.
 Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
@@
 \end{equation}
-is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
+is the energy-momentum tensor of a magnetized perfect fluid, with $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$.
 The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
@@
 Bottom panel: same as the top panel but for Kerr BHs.
-From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.}
+From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.
+Note that the scale shown in the horizontal axes is different in all plots.}
 \label{radial_profiles_HBH}
@@
 An example of our grid is shown in Fig.~XXX.
-\tf{We will include this figure if it could be done and were meaningful.} \tf{Maybe we could also provide the number of the domain and number of points we need for our most extreme case with $a = 0.9999$.}
-
-\sg{It may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots).
-But I think this should go in the results section.} \tf{I agree with mentioning this in the results section.} \sg{Added.}
+\tf{We will include this figure if it could be done and were meaningful.}
 
@@
 We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}.
-The radial coordinate employed in these figures is the standard one of the spherical coordinate system.
-Figures~\ref{models_I} and~\ref{models_II} show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
+These figures show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).
 
@@
 For all models, $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$.
-\tf{Complete description.}}
+The meaning of the quantities reported is as in Table~\ref{HBH_disk_parameters}.}
 \label{KBH_disk_parameters}      
@@
 For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+These models are more general than the corresponding ones presented in~\cite{Gimeno-Soler:2017} as the $h=1$ assumption is now relaxed.
 Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid.
@@
 
-%HERE
-
 The comparison of the values of the physical quantities shows that, even for highly rotating Kerr BHs, the maximum values for $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case.
 This is not a surprise, as these quantities are related to the value of $|\Delta W|$.
-Also, as in the case of KBHsSH, we observe a higher distorsion of the shape of the disc in the near-horizon region with increasing sphericity $\mathfrak{s}$ (and spin, in this particular case).
-\tf{Describe further the table and the figures}.
-\tf{Mention that the horizon location is constant in perimeteral coordinates irrespective of $a$.} \sg{Done}
+Also, as in the case of KBHsSH, we observe a higher distortion of the shape of the disc in the near-horizon region with increasing sphericity $\mathfrak{s}$ (and spin, in this particular case).
+This is particularly noticeable when plotting the disk morphology in terms of the perimeteral coordinates (cf.~Fig.~\ref{models_Kerr_peri}).
+For the $a=0.9999$ model the disk is extremely skewed and attached to the BH horizon, particularly in the highly magnetized case in which the values reported in Table~\ref{KBH_disk_parameters} for $R_{\rm in}$ and $R_{\rm c}$ are very close to each other.
+The appearance of the solution is more disk-like when displayed in terms of the $r$ coordinate, as shown in Fig.~\ref{models_Kerr}.
+
+%HERE
 

### 2018-11-19 paper_prd.tex
Almost finished with this new round.
There are many new little things still to improve and to be taken care of by Sergio.
This paper seems not to be  unfinishable ...

@@
 Note that the scale shown in the horizontal axes is different in all plots.}
-\label{radial_profiles_HBH}
+\label{radial_profiles}
 \end{figure*}
@@
 The size of the disks can be best quantified by plotting the radial profiles of the rest-mass density on the equatorial plane.
-This is shown in the upper panels of Fig.~\ref{radial_profiles_HBH} for models I, IV and VII and for the same three values of the magnetization parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
-(The lower panels of this figure correspond to disks around Kerr BHs and will be discussed below.) From Fig.~\ref{radial_profiles_HBH} we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller the disks become.
+This is shown in the upper panels of Fig.~\ref{radial_profiles} for models I, IV and VII and for the same three values of the magnetization parameter shown in Figs.~\ref{models_I} and~\ref{models_II}.
+(The lower panels of this figure correspond to disks around Kerr BHs and will be discussed below.) From Fig.~\ref{radial_profiles} we see that model I disks are significantly larger than models IV and VII, i.e.~the hairier the models the more compact and smaller the disks become.
 We also note the presence of an extended region of high density in the unmagnetized model VII  (the mildly-magnetized case also shows this feature but to a lesser extent).
@@
 In the first column, we present the value of the central density for the different KBHsSH models.
-In the second column, we present the central density for a KBH with the same ADM quantities.\sg{complete caption}}
+In the second column, we present the central density for a KBH with the same ADM quantities.
+`g.u.' stands for geometrized units.
+\sg{complete caption}.
+\tf{Please, complete it indicating clearly what the columns report, at least the relevant ones.}}
 
@@
 \hline\hline       
- Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}}$ & $\Omega_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\rho_{\mathrm{ADM_c}}$ & $\mathfrak{s}_{\mathrm{ADM}}$
- \\
- & & & & $[\mathrm{g} \, \rm{cm}^{-3}]$ & & & $[\mathrm{g} \, \rm{cm}^{-3}]$ & 
+ Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}}$ & $\Omega^{\rm K}_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\mathfrak{s}^{\rm K}$
+ \\
+ & & & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & 
   \\ 
@@
 
-For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$.
+For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of the same mass ($M_{\mathrm{BH}} = 1$) and varying spins, from $a=0$ to $a=0.9999$.
 These models are more general than the corresponding ones presented in~\cite{Gimeno-Soler:2017} as the $h=1$ assumption is now relaxed.
@@
 As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$.
-It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$.
+It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$, i.e.~the disks reduce their size and approach the BH as the spin parameter increases.
 (Note that, as we mentioned before, in the Kerr case the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the BH spin.)
@@
 For the $a=0.9999$ model the disk is extremely skewed and attached to the BH horizon, particularly in the highly magnetized case in which the values reported in Table~\ref{KBH_disk_parameters} for $R_{\rm in}$ and $R_{\rm c}$ are very close to each other.
-The appearance of the solution is more disk-like when displayed in terms of the $r$ coordinate, as shown in Fig.~\ref{models_Kerr}.
-
-%HERE
-
-Also, in figures~\ref{models_Kerr} and~\ref{models_Kerr_peri} we show different KBH models with the same mass $M_{\mathrm{BH}} = 1$ and different values for the spin parameter($0$, $0.5$, $0.9$, $0.9999$).
-In particular, we can see the well-known behaviour of these models, as the disc reduces its size and tends to attach to the horizon as the spin parameter increases.
-This cannot be particularly be seen in figure~\ref{models_Kerr}, as the radial coordinate expands the near-horizon region and, while it is well suited to do the computations, this is not the case for visualization.
-However, using perimeteral coordinates (figure~\ref{models_Kerr_peri}), we can see the disc attaching to the horizon and the subsequent deformation clearly.
-\sg{complete}
-
-In Fig~\ref{radial_profiles_KBH}, we show three KBH models with the same ADM mass and angular momentum as the cases shown in Fig.~\ref{radial_profiles_HBH}.
-The first case corresponds to a near-extremal KBH ($a = 0.9987$) and the other two have a similar value for spin parameter ($0.8489$ and $0.8941$ respectively).
-Direct comparison between these models and the KBHsSH ones, draws out very interesting features of these models.
-It can be seen that, for model I, the disc in the Kerr case is considerably smaller than its hairy counterpart.
-In this case, the scalar field has little effect on the morphology of the disc (as its gravitational field is small), but its effect is noted in a reduction of the value of the sphericity (see Table~\ref{density_table}), effectively reducing the effects of the black hole spin in the disc (i.e.~increasing its shape).
-As the mass and angular momentum stored in the scalar field increase, the gravitational field of the scalar field affects the radial morphology of the disc, altering its shape and reducing its extent.
-Note that both model IV and model VII have lesser radial extent than its KBH counterparts, even though model VII has a lower value of the sphericity.
+The appearance of the solution is more disk-like when displayed in terms of the $r$ coordinate, as shown in Fig.~\ref{models_Kerr}, as this radial coordinate expands the near-horizon region.
+While this coordinate is well suited to do the computations, this is not the case for visualization, where the  perimeteral coordinate is preferred.
+\tf{Is this last sentence true?}
+
+To provide additional information for the comparison we show in the bottom panels of Fig.~\ref{radial_profiles} three disk models around Kerr BHs  with the same ADM mass and ADM angular momentum as the KBHsSH cases shown in the upper panels of the same figure.
+The model on the left plot corresponds to a near-extremal Kerr BH ($a=0.9987$) and the other two have a similar value for the  spin parameter ($a=0.8489$ and $a=0.8941$, for the middle and right plots, respectively).
+The comparison reveals interesting differences between these models regarding their compactness.
+The size of the disk in the Kerr case plotted on the left is considerably smaller than its hairy counterpart, KBHsSH model I.
+In this case, the presence of the scalar field has little effect on the morphology of the disk (as its gravitational field is small) but its effect is nonetheless noted in a reduction of the value of the sphericity (see Table~\ref{density_table}), effectively reducing the effect of the BH spin in the disk (i.e.~increasing its shape).
+As the mass and angular momentum stored in the scalar field increase, the gravitational field of the scalar field affects the radial morphology of the disk, altering its shape and reducing its extent.
+Note that both KBHsSH models IV and VII have lesser radial extent than its Kerr BH counterparts with the same ADM mass and angular momentum, even though model VII attains a lower value of the sphericity.
+These conclusions hold irrespective of the value of the magnetization parameter.
 
 In Table~\ref{density_table}, we also present the value of the angular velocity at the disc centre (both for the KBHsSH case and for their KBH counterparts).
-It can be seen that, with the exception of the first case, the values of the angular velocity of the Kerr cases are lower than \sg{I need to think a bit about this.}
+It can be seen that, with the exception of the first case, the values of the angular velocity of the Kerr cases are lower than \sg{I need to think a bit about this.} \tf{What is this?
+The notation for the Kerr models with the same ADM mass and angular momentum is very confusing.
+It needs to be explained.}
 
@@
 
-The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in figures~\ref{comparison_HBH_Kerr_dens_enth}.
+The dependence of the maximum specific enthalpy $h_{\mathrm{max}}$ and the maximum rest-mass density $\rho_{\mathrm{max}}$ with the magnetization parameter is shown in Fig.~\ref{comparison_HBH_Kerr_dens_enth}.
 The upper panels correspond to the KBHsSH models (I-VII) and the lower ones to our sequence of Kerr BHs with increasing spin parameter.
-For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetisation) and also higher values for $\rho_{\mathrm{max}}$ (high magnetisation).
+For both cases, an increase in $|\Delta W|$ implies monotonically  higher values for $h_{\mathrm{max}}$ (low magnetization) and also higher values for $\rho_{\mathrm{max}}$ (high magnetization).
 However, there are quantitative differences between the two cases.
@@
 We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
-\tf{Complete.} \sg{Done}
-
-%Also, for the rest-mass density we have a different behaviour: $\rho_{\mathrm{max}}$ for KBHsSH reach values only attainable by high spin parameter KBHs (between $a = 0.9$ and $a = 0.99999$ for the seven models we present here).
+\tf{Say something about the behaviour of $\rho_{\mathrm{max}}$.}
 
@@
 This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, as can be seen in the inset of the right panel of Fig.~\ref{comparison_HBH_Kerr_r_m_max}.
-However, this condition is not fulfilled for disks built around KBHsSH (see inset in the left panel).
+\tf{About the last sentence: it seems to me the condition is fulfilled completely.
+I do not see the deviation and if there was, could it be due to numerical precision when building the models?
+Have you tried to prove this analytically?} However, this condition is not fulfilled for disks built around KBHsSH (see inset in the left panel).
 At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
@@
 
-Even though the models we have computed are non self-gravitating, for the sake of astrophysical relevance, we computed the accretion torus mass for the different KBHsSH models and also, for comparison, the torus mass for seven models of Kerr BHs, each one with the same ADM quantities as their KBHsSH counterparts.
-For this particular section, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
-Also, to avoid complications due to the infinite size of our models, we have chosen the total potential well as the $90\%$ of its maximum possible value.
-This is in agreement with the torus masses found as the final state of binary neutron stars mergers (see, for instance~\cite{Rezzolla:2010}).
-\sg{I think we should check and include more references.} As we have fixed the value of the mass of the torus, now we have to compute the new value of the central density for each model.
-In the fourth (KBHSH) and seventh (Kerr) columns of table~\ref{density_table} we report the resulting central densities we found.
-Now, in order to compare our results with the end-product of a binary neutron star merger, we need to convert our result to cgs units.
-To this end, we first need to choose a mass for the scalar field $\mu$ (as the maximum ADM mass of KBHsSH are related to $\mu$).
-To compute the maximum ADM mass with the followimg equation (see~\cite{Delgado:2018} and references therein)
-\begin{equation}
-M^{max}_{ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{GeV}{\mu}\right) \mathrm{GeV}\,
+In an attempt to gauge the astrophysical relevance of our models, in this section we drop the $\rho_{\mathrm{c}} = 1$ choice we have thus far considered to build the tori and compute their masses and, instead, we assume that the mass of the tori is $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$ and ask ourselves what are the corresponding values of the central density of each model.
+The value selected for $M_{\mathrm{T}}$ is, broadly speaking, compatible with the torus masses found through numerical relativity simulations of binary neutron star mergers (see, e.g.~\cite{Rezzolla:2010, Rezzolla:2017} and references therein).
+Moreover, to avoid complications due to the infinite size of our models, we choose the total potential well as the $90\%$ of its maximum possible value.
+
+Therefore, we compute the mass of the tori around KBHsSH and, for comparison, the corresponding mass for seven disk models around Kerr BHs, each one of them with the same ADM quantities as their KBHsSH counterparts.
+The resulting values are reported in
+Table~\ref{density_table}.
+The variables corresponding to the Kerr case are indicated with a `K' superindex in this table.
+The fourth  and seventh columns of Table~\ref{density_table} indicate the resulting central densities for the KBHsSH and Kerr BH cases, respectively, in geometrized units.
+In order to compare these values with those from the end-products of binary neutron star mergers, we need to convert our results to cgs units.
+To this end, we first need to choose a mass for the scalar field $\mu$, as the maximum ADM mass of KBHsSH depends on $\mu$.
+In particular, we compute the maximum ADM mass with the following equation (see~\cite{Delgado:2018} and references therein)
+\begin{equation}
+M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{GeV}{\mu}\right) \mathrm{GeV}\,
 \end{equation}
 for a value of $\alpha_{\mathrm{BS}} = 1.315$. 
-Using a value of the mass of $\mu = 2.087 \times 10^{-11} \mathrm{eV}$ gives us the following values for the ADM mass of our models, from model I to VII ($2.043$, $3.100$, $3.923$, $4.592$, $4.627$, $4.720$, $4.799$) in units of the mass of the sun $M_{\odot}$.
-Note that (as is mentioned in~\cite{Ramazanoglu:2016}) the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
-\sg{not sure about this last comment, but I think something should be told about $\mu$.}
-
-In columns five (KBHSH) to eight (Kerr) of table~\ref{density_table}, we report the values of the central density in cgs units we have found for each model.
-The found values are between  $\sim 10^{11}$ and $\sim 10^{14} \mathrm{g} \cdot \mathrm{cm}^{-3}$.
-This great range is due to the great difference in the disc size for the different models, specially between the Kerr and KBHsSH cases).
-Comparing these values to the ones in the avalaible literature (see~\cite{Rezzolla:2010} \sg{we need more references.}) we can see that, considering that our assumptions are quite unrealistic, they are within a reasonable margin of the central densities found in discs as the end-product of numerical simulations of a binary neutron star merger.
-Changing the rotation law and the EOS to a more realistic one is expected to improve the accuracy of our results.
-
-\tf{Sergio please finish this section.}
-
-\sg{Even the models we have computed are non-self gravitating, for the sake of astrophysical relevance, we computed the mass of some of the disks.
-For this case only, we have dropped the $\rho_{\mathrm{c}} = 1$ choice and instead, we have chosen that the mass of the torus must be $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
-This is in agreement with the torus masses found as the final state of binary neutron stars mergers}
+\tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
+Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII.
+Note that, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
+\sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}
+
+In columns five and eight of Table~\ref{density_table} we report the values of the central density in cgs units for each of our models.
+The range of values is fairly broad, spanning from $\sim 10^{11}$ g cm$^{-3}$ to $\sim 10^{14}$ g cm$^{-3}$.
+This is due to the significant differences in size of the different disks, especially between the Kerr and KBHsSH cases.
+Comparing these values with those reported in the literature (see~\cite{Rezzolla:2010,Rezzolla:2017}) we conclude that, despite our assumptions, they are in the same ballpark than the central densities found in disks consistently formed through ab-initio simulations of binary neutron star mergers.
+In particular, changing the distribution of the specific angular momentum from a simplistic constant prescription to a more realistic power-law distribution,  may help improve the accuracy of our results.
+
+%HERE
 
@@
 \sg{and compare the central densities (or maximum) with known values.}
+
+\tf{Sergio, I am confused about this last paragraph.
+Is this what you have done to compute the values of the central densities reported in the previous paragraph?
+Or it is something else you want to add?
+Is equation (28) the one you have used to compute the cgs values reported in the previous paragraph?
+If so, this equation should be mentioned in that paragraph.}
 

### 2018-11-19 paper_prd.tex
Done. Sergio please take over ASAP.

@@
 Those disks are assumed to be not self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
-In addition, and for simplicity purpose, the distribution of the specific angular momentum in the disks has been assumed to be constant.
-The models have been constructed building on existing approaches presented in~\cite{Komissarov:2006} and~\cite{Gimeno-Soler:2017}.
-An important generalization of the present work compared to the methodology presented in previous works has had to do with the fluid model: while the mater EOS is still rather simplistic (a polytropic EOS) the models are allowed to be thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
+In addition, and for the sake of simplicity, the distribution of the specific angular momentum in the disks has been assumed to be constant.
+The models have been constructed building on existing approaches presented in~\cite{Komissarov:2006} and~\cite{Gimeno-Soler:2017} which dealt with (hairless) Kerr BHs.
+An important generalization of the present work compared to the methodology presented in previous works has had to do with the fluid model: while the matter EOS we use is still rather simplistic (a polytropic EOS) the models are allowed to be thermodinamically relativist, as the specific enthalpy of the fluid can adopt values significantly larger than unity.
 That has led to interesting differences with respect to the findings reported in~\cite{Gimeno-Soler:2017} for the purely Kerr BH case.

### 2018-11-21 paper_prd.tex
work on the paper

@@
 While this coordinate is well suited to do the computations, this is not the case for visualization, where the perimeteral coordinate is preferred.
-\tf{Is this last sentence true?}
+\tf{Is this last sentence true?} \sg{Yes, as we can compare directly different models as the scale is the same.}
 
@@
 The notation for the Kerr models with the same ADM mass and angular momentum is very confusing.
-It needs to be explained.}
+It needs to be explained.} \sg{I think the angular velocity does not provide us useful information at all.}
 
@@
 We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
+Also, for this case, the maximum density for the extremely magnetized case reaches a value of $\rho_{\mathrm{max}} = 97$.
 \tf{Say something about the behaviour of $\rho_{\mathrm{max}}$.}
@@
 In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / \Gamma - 1=3$.
-This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, as can be seen in the inset of the right panel of Fig.~\ref{comparison_HBH_Kerr_r_m_max}.
+This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, \sg{Suggestion: this cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max}, but for spin $a = 0.9999999$, we observe $0.1912829496$ (for $a = 0.99$ is $0,01484112535$)} as can be seen in the inset of the right panel of Fig.~\ref{comparison_HBH_Kerr_r_m_max}.
 \tf{About the last sentence: it seems to me the condition is fulfilled completely.
@@
 To this end, we first need to choose a mass for the scalar field $\mu$, as the maximum ADM mass of KBHsSH depends on $\mu$.
-In particular, we compute the maximum ADM mass with the following equation (see~\cite{Delgado:2018} and references therein)
-\begin{equation}
-M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{GeV}{\mu}\right) \mathrm{GeV}\,
-\end{equation}
-for a value of $\alpha_{\mathrm{BS}} = 1.315$. 
+In particular, we compute the maximum ADM mass with the following equation (see~\cite{Herdeiro:2015a} and references therein)
+\begin{equation}\label{eq:max_mass_HBH}
+M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{\mathrm{GeV}}{\mu}\right)\,
+\end{equation}
+for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
+The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars.
+Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.
 \tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
@@
 Note that, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
-\sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}
+\sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}.
+Finally, we use the following equation
+\begin{equation}
+\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}\,
+\end{equation}
+to compute the cgs value of the central density for the different models.
 
@@
 In particular, changing the distribution of the specific angular momentum from a simplistic constant prescription to a more realistic power-law distribution,  may help improve the accuracy of our results.
-
-%HERE
-
-\sg{I think here we should go further and do the following: First, choose a suitable maximum ADM mass for the KBHsSH (Eq~(I.1) of~\cite{Herdeiro:2016}), this implies a choice of scalar field mass $\mu$.
-This maximum mass should be such as our models ADM mass would be $\sim 2.5 M_{\odot}$.
-Next, we should compute the central density for the models we want to compare (models I, IV, VII for 3 magnetizations and their Kerr ADM equivalents).
-Finally, we compute the cgs central densities with the formula (From the book of Rezzolla \emph{Relativistic Hydrodynamics})}
-\begin{equation}
-\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}
-\end{equation}
-\sg{and compare the central densities (or maximum) with known values.}
 

### 2018-11-21 paper_prd.tex
Almost there.

@@
 I & $0.415$ & $0.172$ & $0.393$ &  $0.150$  & $0.022$ & $0.022$ & $0.200$ & $0.9987$ & $0.971$ & $0.7685$ & $0.9663$ & $1.404$\\ 
- \hline 
 II & $0.630$ & $0.403$ & $0.340$ &  $0.121$  & $0.290$ & $0.282$ & $0.221$ & $1.0140$ & $0.376$ & $0.6802$ & $0.9301$ & $1.352$ \\
- \hline 
 III & $0.797$ & $0.573$ & $0.365$ &  $0.172$  & $0.432$ & $0.401$ & $0.111$ & $0.9032$ & $1.295$ & $0.7524$ & $0.9608$ & $1.489$ \\ 
- \hline 
 IV & $0.933$ & $0.739$ & $0.234$ &  $0.114$  & $0.699$ & $0.625$ & $0.100$ & $0.8489$ & $2.082$ & $0.5635$ & $0.8554$ & $1.425$ \\ 
- \hline 
 V & $0.940$ & $0.757$ & $0.159$ &  $0.076$  & $0.781$ & $0.680$ & $0.091$ & $0.8560$ & $3.017$ & $0.4438$ & $0.7415$ & $1.357$ \\ 
- \hline 
 VI & $0.959$ & $0.795$ & $0.087$ &  $0.034$  & $0.872$ & $0.747$ & $0.088$ & $0.8644$ & $3.947$ & $0.2988$ & $0.5487$ & $1.222$ \\ 
- \hline 
 VII & $0.975$ & $0.850$ & $0.018$ &  $0.002$  & $0.957$ & $0.848$ & $0.040$ & $0.8941$ & $6.173$ & $0.0973$ & $0.1928$ & $1.039$ \\ 
@@
 To obtain our grid, we use the coordinate transformation provided in~\cite{grav_web} and interpolate the initial grid using cubic splines interpolation.
-An example of our grid is shown in Fig.~XXX.
-\tf{We will include this figure if it could be done and were meaningful.}
 
@@
 The appearance of the solution is more disk-like when displayed in terms of the $r$ coordinate, as shown in Fig.~\ref{models_Kerr}, as this radial coordinate expands the near-horizon region.
-While this coordinate is well suited to do the computations, this is not the case for visualization, where the perimeteral coordinate is preferred.
-\tf{Is this last sentence true?} \sg{Yes, as we can compare directly different models as the scale is the same.}
+While this coordinate is well suited to do the computations, this is not the case for visualization, where the perimeteral coordinate is preferred since it allows to directly compare the different models as the scale is the same.
 
@@
 
-In Table~\ref{density_table}, we also present the value of the angular velocity at the disc centre (both for the KBHsSH case and for their KBH counterparts).
-It can be seen that, with the exception of the first case, the values of the angular velocity of the Kerr cases are lower than \sg{I need to think a bit about this.} \tf{What is this?
-The notation for the Kerr models with the same ADM mass and angular momentum is very confusing.
-It needs to be explained.} \sg{I think the angular velocity does not provide us useful information at all.}
-
-% As shown in~\cite{Delgado:2018} some \sg{(compute which ones are embeddable and which are not)} of our models are in the region of the domain of existence where the event horizon is not embeddable in $\mathbb{E}^3$ then, the shaded regions depicting the horizon that we show at several of the figures are not faithful representations of the horizon geometry.
-Nevertheless, we show them for the sake of clarity.
-Also, this led us to asking ourselves if this could also happen for the shape of the accretion tori and therefore, we should be conservative when extracting information about the morphology of the disks from 2-dimensional plots.
-This idea is discussed in appendix~\ref{torus_embedding}.
-
 %%%%%%%%%%%%%%%%%%
@@
 We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
-Also, for this case, the maximum density for the extremely magnetized case reaches a value of $\rho_{\mathrm{max}} = 97$.
-\tf{Say something about the behaviour of $\rho_{\mathrm{max}}$.}
+For this case, the maximum density in the extremely magnetized limit reaches a value of $\rho_{\mathrm{max}} = 97$, significantly larger than the value displayed in the left  panel of Fig.~\ref{comparison_HBH_Kerr_dens_enth} for the $a=0.9999$ model.
 

### 2018-11-21 paper_prd.tex
some changes, more to come

@@
 \end{equation}
-for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
+\sg{for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
 The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars.
-Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.
+Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.}
 \tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
 Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII.
-Note that, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
-\sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}.
-Finally, we use the following equation
+This value of $\mu$ is within the mass range suggested by the \emph{Axiverse} of string theory (see~\cite{Arvanitaki:2010}) (a large number of scalar fields in a mass range from $10^{-33}$ eV to $10^{-10}$ eV).
+In addition, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories (Although in this work we are working with GR, for the low values of the trace of the energy-momentum tensor $T$ we are working (in comparison with the values reached for neutron stars) both theories should be indistinguishable).
+\tf{Yes, but probably is not the best reference since it is not GR.}.
+Finally, we use the following equation (from~\cite{RezzollaBook})
 \begin{equation}

### 2018-11-21 paper_prd.tex
Done. The new additions are written as comments.

--- 2018-11-21 paper_prd.tex
@@
 \caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total}} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
-In the first column, we present the value of the central density for the different KBHsSH models.
-In the second column, we present the central density for a KBH with the same ADM quantities.
-`g.u.' stands for geometrized units.
-\sg{complete caption}.
+\sg{In the third column, we present the value of the central density for the different KBHsSH models in geometrized units.
+In the fourth column, we present the value of the central density for the different KBHsSH models in cgs units.
+In the fifth and sixth columns, we present the same as in the third and fourth ones, but for a KBH with the same ADM quantities as the model displayed in the first column.
+The seventh column reports the sphericity of said KBH model.t.
+Note that `g.u.' stands for geometrized units.} .
 \tf{Please, complete it indicating clearly what the columns report, at least the relevant ones.}}
@@
 \centering          
-\begin{tabular}{c c c c c c c c c}
+\begin{tabular}{c c c c c c c}
 \hline\hline       
- Model & $\Omega_{\mathrm{c}}$ & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}}$ & $\Omega^{\rm K}_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\mathfrak{s}^{\rm K}$
- \\
- & & & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & 
+ Model  & $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $\rho_{\mathrm{c}}$ & $\rho_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\rho^{\rm K}_{\mathrm{c}}$ & $\mathfrak{s}^{\rm K}$
+ \\
+ & & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & [g.u.] & $[\mathrm{g} \, \rm{cm}^{-3}]$ & 
   \\ 
 \hline           
-I & $0.493$ & $10^{10}$ & $6.818 \times 10^{-4}$ & $1.739 \times 10^{13}$ & $0.854$ & $3.752 \times 10^{-3}$ &  $9.567 \times 10^{13}$ & $1.589$ \\
-
- & & $1$ & $2.185 \times 10^{-3}$ & $5.503 \times 10^{13}$ & & $7.942 \times 10^{-3}$ & $2.025 \times 10^{14}$ & \\
-
- & & $10^{-10}$ & $3.227 \times 10^{-3}$ & $8.229 \times 10^{13}$ & & $7.641 \times 10^{-3}$ & $1.948 \times 10^{14}$ & \\
-
-II & $0.424$ & $10^{10}$ & $3.216 \times 10^{-4}$ & $8.201 \times 10^{12}$ & $-$ & $-$ & $-$ & $-$ \\
-
- & & $1$ & $1.651 \times 10^{-3}$ & $4.210 \times 10^{13}$ & $-$ & $-$ & $-$ & $-$ \\
-
- & & $10^{-10}$ & $3.026 \times 10^{-3}$ & $7.716 \times 10^{13}$ & $-$ & $-$ & $-$ & $-$ \\
-
-III & $0.521$ & $10^{10}$ & $8.120 \times 10^{-4}$ & $2.071 \times 10^{13}$ & $0.163$ & $6.683 \times 10^{-5}$ & $1.704 \times 10^{12}$ & $1.278$ \\
-
- & & $1$ & $3.497 \times 10^{-3}$ & $8.917 \times 10^{13}$ & & $2.075 \times 10^{-4}$ & $5.291 \times 10^{12}$ & \\
-
- & & $10^{-10}$ & $5.452 \times 10^{-3}$ & $1.390 \times 10^{14}$ & & $3.265 \times 10^{-4}$ & $8.325 \times 10^{12}$ & \\
-
-IV & $0.427$ & $10^{10}$ & $1.197 \times 10^{-3}$ & $3.052 \times 10^{13}$ & $0.113$ & $3.001 \times 10^{-5}$ & $7.652 \times 10^{11}$ & $1.219$ \\
-
- & & $1$ & $3.421 \times 10^{-3}$ & $8.723 \times 10^{13}$ & & $9.512 \times 10^{-5}$ & $2.425 \times 10^{12}$ & \\
-
- & & $10^{-10}$ & $5.135 \times 10^{-3}$ & $1.309 \times 10^{14}$ & & $1.533 \times 10^{-4}$ & $3.909 \times 10^{12}$ & \\
-
-V & $0.394$ & $10^{10}$ & $1.792 \times 10^{-3}$ & $4.569 \times 10^{13}$ & $0.115$ & $3.152 \times 10^{-5}$ & $8.037 \times 10^{11}$ & $1.227$\\
-
- & & $1$ & $3.883 \times 10^{-3}$ & $9.901 \times 10^{13}$ & & $9.942 \times 10^{-5}$ & $2.535 \times 10^{12}$ & \\
-
- & & $10^{-10}$ & $5.435 \times 10^{-3} $ & $1.386 \times 10^{14}$ & & $1.596 \times 10^{-4}$ & $4.070 \times 10^{12}$ & \\
-
-VI & $0.350$ & $10^{10}$ & $2.348 \times 10^{-3}$ & $5.987 \times 10^{13}$ & $0.117$ & $3.232 \times 10^{-5}$ & $8.241 \times 10^{11}$ & $1.234$\\
-
- & & $1$ & $4.106 \times 10^{-3}$ & $1.047 \times 10^{14}$ & & $1.019 \times 10^{-4}$ & $2.598 \times 10^{12}$ & \\
-
- & & $10^{-10}$ & $5.685 \times 10^{-3}$ & $1.450 \times 10^{14}$ & & $1.632 \times 10^{-4}$ & $4.161 \times 10^{12}$ & \\
-
-VII & $0.330$ & $10^{10}$ & $3.737 \times 10^{-3}$ & $9.529 \times 10^{13}$ & $0.129$ & $4.114 \times 10^{-5}$ & $1.049 \times 10^{12}$ & $1.268$\\
-
- & & $1$ & $5.356 \times 10^{-3}$ & $1.366 \times 10^{14}$ & & $1.280 \times 10^{-4}$ & $3.264 \times 10^{12}$ & \\
-
- & & $10^{-10}$ & $7.598 \times 10^{-3}$ & $1.937 \times 10^{14}$ & & $2.021 \times 10^{-4}$ & $5.153 \times 10^{12}$ & \\ 
+I  & $10^{10}$ & $6.818 \times 10^{-4}$ & $1.739 \times 10^{13}$  & $3.752 \times 10^{-3}$ &  $9.567 \times 10^{13}$ & $1.589$ \\
+
+  & $1$ & $2.185 \times 10^{-3}$ & $5.503 \times 10^{13}$  & $7.942 \times 10^{-3}$ & $2.025 \times 10^{14}$ & \\
+
+  & $10^{-10}$ & $3.227 \times 10^{-3}$ & $8.229 \times 10^{13}$  & $7.641 \times 10^{-3}$ & $1.948 \times 10^{14}$ & \\
+
+II  & $10^{10}$ & $3.216 \times 10^{-4}$ & $8.201 \times 10^{12}$ & $-$ & $-$ & $-$ \\
+
+  & $1$ & $1.651 \times 10^{-3}$ & $4.210 \times 10^{13}$ & $-$ & $-$ & $-$ \\
+
+  & $10^{-10}$ & $3.026 \times 10^{-3}$ & $7.716 \times 10^{13}$ & $-$ & $-$ & $-$ \\
+
+III & $10^{10}$ & $8.120 \times 10^{-4}$ & $2.071 \times 10^{13}$  & $6.683 \times 10^{-5}$ & $1.704 \times 10^{12}$ & $1.278$ \\
+
+  & $1$ & $3.497 \times 10^{-3}$ & $8.917 \times 10^{13}$ & $2.075 \times 10^{-4}$ & $5.291 \times 10^{12}$ & \\
+
+  & $10^{-10}$ & $5.452 \times 10^{-3}$ & $1.390 \times 10^{14}$  & $3.265 \times 10^{-4}$ & $8.325 \times 10^{12}$ & \\
+
+IV & $10^{10}$ & $1.197 \times 10^{-3}$ & $3.052 \times 10^{13}$  & $3.001 \times 10^{-5}$ & $7.652 \times 10^{11}$ & $1.219$ \\
+
+  & $1$ & $3.421 \times 10^{-3}$ & $8.723 \times 10^{13}$  & $9.512 \times 10^{-5}$ & $2.425 \times 10^{12}$ & \\
+
+  & $10^{-10}$ & $5.135 \times 10^{-3}$ & $1.309 \times 10^{14}$ & $1.533 \times 10^{-4}$ & $3.909 \times 10^{12}$ & \\
+
+V  & $10^{10}$ & $1.792 \times 10^{-3}$ & $4.569 \times 10^{13}$  & $3.152 \times 10^{-5}$ & $8.037 \times 10^{11}$ & $1.227$\\
+
+  & $1$ & $3.883 \times 10^{-3}$ & $9.901 \times 10^{13}$  & $9.942 \times 10^{-5}$ & $2.535 \times 10^{12}$ & \\
+
+  & $10^{-10}$ & $5.435 \times 10^{-3} $ & $1.386 \times 10^{14}$  & $1.596 \times 10^{-4}$ & $4.070 \times 10^{12}$ & \\
+
+VI & $10^{10}$ & $2.348 \times 10^{-3}$ & $5.987 \times 10^{13}$  & $3.232 \times 10^{-5}$ & $8.241 \times 10^{11}$ & $1.234$\\
+
+  & $1$ & $4.106 \times 10^{-3}$ & $1.047 \times 10^{14}$  & $1.019 \times 10^{-4}$ & $2.598 \times 10^{12}$ & \\
+
+  & $10^{-10}$ & $5.685 \times 10^{-3}$ & $1.450 \times 10^{14}$ & $1.632 \times 10^{-4}$ & $4.161 \times 10^{12}$ & \\
+
+VII  & $10^{10}$ & $3.737 \times 10^{-3}$ & $9.529 \times 10^{13}$ & $4.114 \times 10^{-5}$ & $1.049 \times 10^{12}$ & $1.268$\\
+
+  & $1$ & $5.356 \times 10^{-3}$ & $1.366 \times 10^{14}$ & $1.280 \times 10^{-4}$ & $3.264 \times 10^{12}$ & \\
+
+  & $10^{-10}$ & $7.598 \times 10^{-3}$ & $1.937 \times 10^{14}$ & $2.021 \times 10^{-4}$ & $5.153 \times 10^{12}$ & \\ 
  \hline\hline   
@@
 This implies that, while the $w = \rho h \simeq \rho$ approximation (employed in~\cite{Komissarov:2006,Gimeno-Soler:2017}) is valid for magnetized disks ($\beta_{\mathrm{m_c}} \sim 1$) around Kerr BHs for values of the spin parameter as high as $a \sim 0.99$, that is not the case for disks around KBHsSH.
-We note that for the most extreme spin value we can build, $a=0.9999999$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
+We note that for the most extreme spin value we can build, $|a-1|=10^{-7}$, the maximum enthalpy for the purely hydrodynamical case is $h_{\rm max}=1.692$.
 For this case, the maximum density in the extremely magnetized limit reaches a value of $\rho_{\mathrm{max}} = 97$, significantly larger than the value displayed in the left  panel of Fig.~\ref{comparison_HBH_Kerr_dens_enth} for the $a=0.9999$ model.
@@
 In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / \Gamma - 1=3$.
-This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, \sg{Suggestion: this cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max}, but for spin $a = 0.9999999$, we observe $0.1912829496$ (for $a = 0.99$ is $0,01484112535$)} as can be seen in the inset of the right panel of Fig.~\ref{comparison_HBH_Kerr_r_m_max}.
-\tf{About the last sentence: it seems to me the condition is fulfilled completely.
+This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, \sg{this cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max}, but for spin $|a-1|=10^{-7}$, and using out ansatz radial coordinate, we observe that the deviation $r_{\mathrm{m, max}}/r_{\mathrm{c}}$, at magnetization $\beta_{\mathrm{m_{\mathrm{c}}}} = 3$, is equal to $0.9$ (in contrast, for $a = 0.9999$ its value is $0.97$).} \tf{About the last sentence: it seems to me the condition is fulfilled completely.
 I do not see the deviation and if there was, could it be due to numerical precision when building the models?
@@
 \end{equation}
-for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
+\sg{for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
 The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars.
-Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the mass for the corresponding KBHsSH.
+Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the maximum mass for the corresponding KBHsSH.}
 \tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
 Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII.
-Note that, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories.
-\sg{not sure about this last comment, but I think something should be told about $\mu$.} \tf{Yes, but probably is not the best reference since it is not GR.}.
-Finally, we use the following equation
+\sg{This value of $\mu$ is within the mass range suggested by the \emph{Axiverse} of string theory (see~\cite{Arvanitaki:2010}) (a large number of scalar fields in a mass range from $10^{-33}$ eV to $10^{-10}$ eV).
+In addition, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories (Although in this paper we are working with GR, for the low values of the trace of the energy-momentum tensor $T$ we are working (in comparison with the values reached for neutron stars) both theories should be indistinguishable).
+We should note as well that Eq.~\cite{eq:max_mass_HBH} is valid for a non self-interacting scalar hair.
+Adding self-interaction terms will produce astrophysically relevant solutions for less exotic values of the scalar field mass $\mu$ (see~\cite{Delgado:2018}).} \tf{Yes, but probably is not the best reference since it is not GR.} \sg{Once we have computed the new values of the central density, we use the following equation (from~\cite{RezzollaBook})}
 \begin{equation}
@@
 \end{equation}
-to compute the cgs value of the central density for the different models.
+\sg{to obtain the value of the central density in cgs units for the different models.}
 

### 2018-11-21 paper_prd.tex
Done. Version sent to Carlos and Eugene.

@@
 
+Table~\ref{models_list} lists the seven KBHsSH models we use in this work.
+The models have been selected to span all regions of interest in the parameter space.
+Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH (namely, $94.7\%$ of the total mass and $87.2\%$ of the total angular momentum of the spacetime are stored in the BH), while model VII corresponds to a hairy Kerr BH with almost all the mass (98.15\%) and angular momentum (99.76\%) stored in the scalar field.
+It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than unity) in terms of both ADM or horizon quantities.
+This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds the speed of light.
+For comparison, we also show in Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
+In the last column of Table~\ref{models_list} we indicate the horizon sphericity of the KBHsSH, defined in~\cite{Delgado:2018} as the quotient of the equatorial and polar proper lengths of the event horizon
+\begin{equation}
+\mathfrak{s} = \frac{L_{\mathrm{e}}}{L_{\mathrm{p}}} = \frac{\int^{2\pi}_{0} \mathrm{d}\phi \, e^{F_2(r_{\mathrm{H}}, \pi/2)} r_{\mathrm{H}}}{2\int^{\pi}_{0} \mathrm{d} \theta \, e^{F_1(r_{\mathrm{H}}, \theta)} r_{\mathrm{H}}}\,.
+\end{equation}
+In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
+\tf{This figure has to be redone by Carlos.}
+
+\begin{figure}
+\centering
+\includegraphics[scale=0.7]{figures/existence-eps-converted-to.pdf}
+\caption{Domain of existence for KBHsSH in an ADM mass versus scalar
+field frequency diagram. \tf{The figure has to be redone to label the 7 models used in this work.}}
+\label{existence}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%
-\begin{table*}
+\begin{table*}[t]
 \caption{List of models of KBHsSH used in this work.
@@
 
-Table~\ref{models_list} lists the seven KBHsSH models we use in this work.
-The models have been selected to span all regions of interest in the parameter space.
-Model I corresponds to a Kerr-like model, with almost all the mass and angular momentum stored in the BH (namely, $94.7\%$ of the total mass and $87.2\%$ of the total angular momentum of the spacetime are stored in the BH), while model VII corresponds to a hairy Kerr BH with almost all the mass (98.15\%) and angular momentum (99.76\%) stored in the scalar field.
-It is worth mentioning that some of the models violate the Kerr bound (i.e.~the normalized spin parameter is larger than unity) in terms of both ADM or horizon quantities.
-This is not a source of concern because, as shown in~\cite{Herdeiro:2015c}, the linear velocity of the horizon, $v_{\mathrm{H}}$, never exceeds the speed of light.
-For comparison, we also show in Table~\ref{models_list} the spin parameter $a_{\mathrm{H_{eq}}}$ corresponding to a Kerr BH with a horizon linear velocity $v_{\mathrm{H}}$.
-In the last column of Table~\ref{models_list} we indicate the horizon sphericity of the KBHsSH, defined in~\cite{Delgado:2018} as the quotient of the equatorial and polar proper lengths of the event horizon
-\begin{equation}
-\mathfrak{s} = \frac{L_{\mathrm{e}}}{L_{\mathrm{p}}} = \frac{\int^{2\pi}_{0} \mathrm{d}\phi \, e^{F_2(r_{\mathrm{H}}, \pi/2)} r_{\mathrm{H}}}{2\int^{\pi}_{0} \mathrm{d} \theta \, e^{F_1(r_{\mathrm{H}}, \theta)} r_{\mathrm{H}}}\,.
-\end{equation}
-In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
-\tf{This figure has to be redone by Carlos.}
-
-\begin{figure}
-\centering
-\includegraphics[scale=0.7]{figures/existence-eps-converted-to.pdf}
-\caption{Domain of existence for KBHsSH in an ADM mass versus scalar
-field frequency diagram. \tf{The figure has to be redone to label the 7 models used in this work.}}
-\label{existence}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
- &  &  &  &  & $10^{-10}$ & $1.00$ & $10.42$ & $7.03 \times 10^{-10}$ & $2.44$ & $0.28$ & $0.30$\\ 
+ &  &  &  &  & $10^{-10}$ & $1.00$ & $10.42$ & $7.03 \times 10^{-10}$ & $0.24 \times 10^{-1}$ & $0.28$ & $0.30$\\ 
 \hline\hline
@@
 \begin{table*}[t]
-\caption{Central density of the disc for the different models, considering a disc with a value of $r_{\mathrm{in}}$ such as $\Delta W = 0.9 \Delta W_{\mathrm{Total}} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}$ and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$.
-\sg{In the third column, we present the value of the central density for the different KBHsSH models in geometrized units.
-In the fourth column, we present the value of the central density for the different KBHsSH models in cgs units.
-In the fifth and sixth columns, we present the same as in the third and fourth ones, but for a KBH with the same ADM quantities as the model displayed in the first column.
-The seventh column reports the sphericity of said KBH model.t.
-Note that `g.u.' stands for geometrized units.} .
-\tf{Please, complete it indicating clearly what the columns report, at least the relevant ones.}}
+\caption{Central density for the different models.
+A value of $r_{\mathrm{in}}$ such that $\Delta W = 0.9 \Delta W_{\mathrm{Total}} \equiv W_{\mathrm{cusp}} - W_{\mathrm{c}}$ is chosen and a torus gravitational mass of $M_{\mathrm{T}} = 0.1 M_{\mathrm{ADM}}$ is assumed.
+In the third column, the value of the central density is reported in geometrized units (`g.u.') while in the fourth column this value is reported in cgs units.
+The fifth and sixth columns provide those values but for tori built around Kerr BHs with the same ADM quantities as the KBHsSH models.
+Finally, the last column reports the sphericity of the Kerr BH models.}
 
@@
 In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / \Gamma - 1=3$.
-This condition is also fulfilled for the Kerr BH case  even when $h \neq 1$, with a slight deviation for cases with very high spin parameter, \sg{this cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max}, but for spin $|a-1|=10^{-7}$, and using out ansatz radial coordinate, we observe that the deviation $r_{\mathrm{m, max}}/r_{\mathrm{c}}$, at magnetization $\beta_{\mathrm{m_{\mathrm{c}}}} = 3$, is equal to $0.9$ (in contrast, for $a = 0.9999$ its value is $0.97$).} \tf{About the last sentence: it seems to me the condition is fulfilled completely.
-I do not see the deviation and if there was, could it be due to numerical precision when building the models?
-Have you tried to prove this analytically?} However, this condition is not fulfilled for disks built around KBHsSH (see inset in the left panel).
+This condition is almost fulfilled for the Kerr BH case  even when $h \neq 1$, with a very slight deviation for cases with very high spin parameter.
+This cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max} (even in the inset) but, as an example, for $a=0.9999$, the relative difference of $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$ with the $h=1$ case is about 0.1\%.
+(We note that in the radial coordinate of the metric ansatz, the disks are not so skewed and attached to the horizon and the differences would be more visible.) On the other hand, the condition $R_{\mathrm{m, max}}=R_{\mathrm{c}}$ when $\beta_{\mathrm{m_c}}= 3$ is clearly not fulfilled (when $h\neq 1$) for disks built around KBHsSH (see inset in the left panel).
 At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
@@
 The variables corresponding to the Kerr case are indicated with a `K' superindex in this table.
-The fourth  and seventh columns of Table~\ref{density_table} indicate the resulting central densities for the KBHsSH and Kerr BH cases, respectively, in geometrized units.
+The third  and fifth columns of Table~\ref{density_table} indicate the resulting central densities for the KBHsSH and Kerr BH cases, respectively, in geometrized units.
 In order to compare these values with those from the end-products of binary neutron star mergers, we need to convert our results to cgs units.
@@
 \begin{equation}\label{eq:max_mass_HBH}
-M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{\mathrm{GeV}}{\mu}\right)\,
-\end{equation}
-\sg{for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
+M^{\rm max}_{\rm ADM} \simeq \alpha_{\mathrm{BS}} 10^{-19} M_{\odot} \left(\frac{\mathrm{GeV}}{\mu}\right)\,,
+\end{equation}
+for a value of $\alpha_{\mathrm{BS}} = 1.315$ (corresponding to a value of the azimuthal harmonic index $m = 1$).
 The constant $\alpha_{\mathrm{BS}}$ is computed numerically for rotating boson stars.
-Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star, but, as it is mentioned in~\cite{Herdeiro:2015a}, this is also the maximum mass for the corresponding KBHsSH.}
-\tf{I don't find this formula in reference~\cite{Delgado:2018}. Are you sure the formula is well written? The dimensions look strange. What is $\alpha_{\mathrm{BS}}$?}
+Note that Eq.~\eqref{eq:max_mass_HBH} corresponds to the maximum mass of a boson star but, as  mentioned in~\cite{Herdeiro:2015a}, this is also the maximum mass for the corresponding hairy BH.
 Using a value of the mass of the scalar field of $\mu = 2.087 \times 10^{-11}$ eV yields values for the ADM mass of our models that increase from 2.043 $M_{\odot}$ to 4.799 $M_{\odot}$, from model I to VII.
-\sg{This value of $\mu$ is within the mass range suggested by the \emph{Axiverse} of string theory (see~\cite{Arvanitaki:2010}) (a large number of scalar fields in a mass range from $10^{-33}$ eV to $10^{-10}$ eV).
-In addition, as is mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we have chose is compatible with the scalar field mass range allowed by the observational tests in Scalar-Tensor theories (Although in this paper we are working with GR, for the low values of the trace of the energy-momentum tensor $T$ we are working (in comparison with the values reached for neutron stars) both theories should be indistinguishable).
-We should note as well that Eq.~\cite{eq:max_mass_HBH} is valid for a non self-interacting scalar hair.
-Adding self-interaction terms will produce astrophysically relevant solutions for less exotic values of the scalar field mass $\mu$ (see~\cite{Delgado:2018}).} \tf{Yes, but probably is not the best reference since it is not GR.} \sg{Once we have computed the new values of the central density, we use the following equation (from~\cite{RezzollaBook})}
-\begin{equation}
-\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}\,
-\end{equation}
-\sg{to obtain the value of the central density in cgs units for the different models.}
-
-In columns five and eight of Table~\ref{density_table} we report the values of the central density in cgs units for each of our models.
-The range of values is fairly broad, spanning from $\sim 10^{11}$ g cm$^{-3}$ to $\sim 10^{14}$ g cm$^{-3}$.
+This value of $\mu$ is within the mass range suggested by the \emph{axiverse} of string theory (see~\cite{Arvanitaki:2010}) portraying a large number of scalar fields in a mass range from $10^{-33}$ eV to $10^{-10}$ eV.
+In addition, as mentioned in~\cite{Ramazanoglu:2016}, the value of $\mu$ we choose is compatible with the scalar-field mass range allowed by the observational tests in scalar-tensor theories of gravity.
+Although in this paper we are working within general relativity, for the low values of the trace of the energy-momentum tensor of our models (in comparison with the values reached for neutron stars) both theories should be indistinguishable.
+We should note as well that Eq.~(\ref{eq:max_mass_HBH}) is valid for non self-interacting scalar hair.
+Adding self-interaction terms would produce astrophysically relevant solutions for less extreme values of the scalar-field mass $\mu$~\cite{Delgado:2018}.
+
+Once we compute the new values of the central density in geometrized units, we use the following equation~\cite{RezzollaBook}
+\begin{equation}
+\rho_{\mathrm{cgs}} = 6.17714 \times 10^{17} \left(\frac{G}{c^2}\right)\left(\frac{M_{\odot}}{M}\right)^2 \rho_{\mathrm{geo}}\,,
+\end{equation}
+to obtain the value of the central density in cgs units for the different models.
+These values are reported in columns four and six of Table~\ref{density_table}.
+The range of values is fairly broad, spanning from $\sim10^{11}$ g cm$^{-3}$ to $\sim10^{14}$ g cm$^{-3}$.
 This is due to the significant differences in size of the different disks, especially between the Kerr and KBHsSH cases.
 Comparing these values with those reported in the literature (see~\cite{Rezzolla:2010,Rezzolla:2017}) we conclude that, despite our assumptions, they are in the same ballpark than the central densities found in disks consistently formed through ab-initio simulations of binary neutron star mergers.
-In particular, changing the distribution of the specific angular momentum from a simplistic constant prescription to a more realistic power-law distribution, may help improve the accuracy of our results.
-
-\tf{Sergio, I am confused about this last paragraph.
-Is this what you have done to compute the values of the central densities reported in the previous paragraph?
-Or it is something else you want to add?
-Is equation (28) the one you have used to compute the cgs values reported in the previous paragraph?
-If so, this equation should be mentioned in that paragraph.}
+In particular, changing the distribution of the specific angular momentum from our simplistic constant prescription to a more realistic power-law distribution, may help improve the accuracy of our results.
 
@@
 In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronised scalar hair and have built stationary models of magnetized tori around them.
-Those disks are assumed to be not self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
+Those disks are assumed to be non-self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
 In addition, and for the sake of simplicity, the distribution of the specific angular momentum in the disks has been assumed to be constant.

### 2018-11-25 paper_prd.tex
Add files via upload

@@
 \newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
+\newcommand{\ch}[1]{\textcolor{cyan}{CH: #1}}
 
@@
 \author{Carlos Herdeiro}
-\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
-3810-183 Aveiro, Portugal}
+\affiliation{Centro de Astrof\'\i sica e Gravita\c c\~ao - CENTRA, Departamento de F\'\i sica,
+Instituto Superior T\'ecnico - IST, Universidade de Lisboa - UL, Avenida
+Rovisco Pais 1, 1049-001, Portugal}
 
 \author{Eugen Radu}
-\affiliation{Departamento de F\'{\i}sica da Universidade de Aveiro and CIDMA, Campus de Santiago, 
-3810-183 Aveiro, Portugal}
+\affiliation{School of Theoretical Physics, Dublin Institute for Advanced Studies, 
+ 10 Burlington Road, Dublin 4, Ireland and 
+CIDMA, Universidade de Aveiro,
+Campus de Santiago, 3810-183 Aveiro, Portugal}
 
@@
 On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH in spherical  symmetry).
-On the other hand, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, rendering HBHs as {\it effectively} stable.
+On the other hand, even though the hairy BHs themselves are (like Kerr BHs) afflicted by superradiant instabilities~\cite{Herdeiro:2014b,Ganchev:2018}, these instabilities are weaker than for Kerr and, at least in some regions of parameter space, are inefficient for astrophysical time scales, making the hairy BHs {\it effectively} stable against superradiance~\cite{Degollado:2018}.
 
@@
 Moreover, $\omega$ is the scalar field frequency and $m$ is the azimuthal harmonic index.
-We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, where $a = J/M$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
+We note that the radial coordinate $r$ is related to the Boyer-Lindquist radial coordinate $r_{\rm BL}$ by $r=r_{\rm BL}-a^2/r_{\rm H,BL}$, in the Kerr limit, where $a = J/M$ stands for the spin of the BH and $r_{\rm H,BL}$ is the location of the horizon in Boyer-Lindquist coordinates.
 
@@
 (T_{\mathrm{SF}})_{ab} &=& \partial_a \Psi^* \partial_b \Psi + \partial_b \Psi^* \partial_a \Psi 
-\nonumber \\ 
-&-& g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right),
+ \\ 
+&-& g_{ab} \left(\frac{1}{2} g^{cd}(\partial_c \Psi^* \partial_d \Psi + \partial_d \Psi^* \partial_c \Psi) + \mu^2 \Psi^* \Psi \right), \nonumber
 \end{eqnarray}
@@
 In addition to the information provided in Table~\ref{models_list}, Figure~\ref{existence} plots the location of our models in the domain of existence of KBHsSH in an ADM mass versus scalar field frequency diagram.
-\tf{This figure has to be redone by Carlos.}
 
@@
 \centering
-\includegraphics[scale=0.7]{figures/existence-eps-converted-to.pdf}
-\caption{Domain of existence for KBHsSH in an ADM mass versus scalar
-field frequency diagram. \tf{The figure has to be redone to label the 7 models used in this work.}}
+\includegraphics[scale=0.43]{figures/existence-new.pdf}
+\caption{Domain of existence for KBHsSH (shaded blue area) in an ADM mass versus scalar
+field frequency diagram. The seven solutions to be studied herein are highlighted in this diagram.}
 \label{existence}
@@
 \caption{List of models of KBHsSH used in this work.
-From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$, and the sphericity of the horizon, $\mathfrak{s}$.}
+From left to right the columns report the name of the model, the ADM mass, $M_{\mathrm{ADM}}$, the ADM angular momentum, $J_{\mathrm{ADM}}$, the horizon mass, $M_{\mathrm{H}}$, the horizon angular momentum, $J_{\mathrm{H}}$, the mass of the scalar field, $M_{\mathrm{SF}}$, the angular momentum of the scalar field, $J_{\mathrm{SF}}$, the radius of the event horizon, $r_{\mathrm{H}}$, the values of the normalized spin parameter for the ADM quantities, $a_{\mathrm{ADM}}$, and for the BH horizon quantities, $a_{\mathrm{H}}$, the horizon linear velocity, $v_{\mathrm{H}}$, the spin parameter corresponding to a Kerr BH with a linear velocity equal to $v_{\mathrm{H}}$, $a_{\mathrm{H_{eq}}}$, and the sphericity of the horizon, $\mathfrak{s}$.
+Here $\mu=1$.}
 \label{models_list}      
@@
 The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
-We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
+\ch{The marginally bound orbit is not stable, right?
+So this is what is called the ICO, not ISCO, in the literature?} We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
 
@@
 \end{eqnarray}
+\ch{Careful with $\omega$ vs. $w$. I think in these expressions should be $\omega$. Please check.}
 Using these expressions, we can compute the total gravitational mass of the torus and the scalar field as the following expression
@@
 From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.
-Note that the scale shown in the horizontal axes is different in all plots.}
+Note that the scale shown in the horizontal axes is different in all plots.
+\ch{Please change the line style (one dotted, one dashed and one solid, in each plot, for clarity in black and white.
+The structure near the origin would be clearer if the r coordinate would be in a log plot.}}
 \label{radial_profiles}
@@
 However, for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
-\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.} \tf{Any comment, Carlos?}
+%\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.} \tf{Any comment, Carlos?}
 
@@
 
-This work has been supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P), by the FCT (Portugal) IF programme, by the CIDMA (FCT) strategic project UID/MAT/04106/2013 and by  the  European  Union's  Horizon  2020  research  and  innovation  (RISE) programmes H2020-MSCA-RISE-2015 Grant No.~StronGrHEP-690904 and H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740.
+This work has been supported by the Spanish MINECO (grant AYA2015-66899-C2-1-P), by the FCT (Portugal) IF programme, by the FCT grant PTDC/FIS-OUT/28407/2017, by  CIDMA (FCT) strategic project UID/MAT/04106/2013, by CENTRA (FCT) strategic project UID/FIS/00099/2013 and by  the  European  Union's  Horizon  2020  research  and  innovation  (RISE) programmes H2020-MSCA-RISE-2015 Grant No.~StronGrHEP-690904 and H2020-MSCA-RISE-2017 Grant No.~FunFiCO-777740.
+E.R.
+gratefully acknowledges the support of DIAS.
 The authors would like to acknowledge networking support by the COST Action CA16104.
@@
 \begin{equation}
-L = \frac{1}{2}\left(g_{tt} (\dot{t})^2 + 2 g_{t\phi} \dot{t}\dot{\phi} + g_{rr} (\dot{r})^2 + g_{\theta\theta} (\dot{\theta})^2 + g_{\phi\phi} (\dot{\phi})^2\right)\,
+\mathcal{L} = \frac{1}{2}\left[g_{tt} (\dot{t})^2 + 2 g_{t\phi} \dot{t}\dot{\phi} + g_{rr} (\dot{r})^2 + g_{\theta\theta} (\dot{\theta})^2 + g_{\phi\phi} (\dot{\phi})^2\right]\ ,
 \end{equation}
@@
 \begin{eqnarray}\label{eq:momenta}
-p_t = \frac{\partial L}{\partial \dot{t}} = -E
-\\
-p_{\phi} = \frac{\partial L}{\partial \dot{\phi}} = L\,
+p_t = \frac{\partial L}{\partial \dot{t}} = -E \ ,
+\\
+p_{\phi} = \frac{\partial L}{\partial \dot{\phi}} = L\ ,
 \end{eqnarray}
@@
 
-If we assume motion in the equatiorial plane (i.e.~$\theta = \pi/2$, $\dot{\theta} = 0$) we can write the relativistic four-momentum (of a massive particle) normalisation as
+If we assume motion in the equatorial plane (i.e.~$\theta = \pi/2$, $\dot{\theta} = 0$) we can write the relativistic four-momentum (of a massive particle) normalisation as
 \begin{equation}\label{eq:momenta_normalisation}
-p_{t}p^t + p_{r}p^r + p_{\phi}p^{\phi} = -m^2\,
+p_{t}p^t + p_{r}p^r + p_{\phi}p^{\phi} = -m^2\ ,
 \end{equation}
@@
 \begin{eqnarray}
-p^{t} = \frac{g_{\phi\phi}E + g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}
-\\
-p^{\phi} = -\frac{g_{tt}L+g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\,
+p^{t} = \frac{g_{\phi\phi}E + g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}} \ ,
+\\
+p^{\phi} = -\frac{g_{tt}L+g_{t\phi}}{g_{t\phi}^2-g_{tt}g_{\phi\phi}}\ ,
 \end{eqnarray}
-now, we can replace these expressions into Eq.~\eqref{eq:momenta_normalisation} and write the expressión for the radial velocity $\dot{r}$
+replace these expressions into Eq.~\eqref{eq:momenta_normalisation} and write the expression for the radial velocity $\dot{r}$
 \begin{equation}\label{eq:radial_velocity}
@@
 \begin{equation}
-g_{t\phi}^2-g_{tt}g_{\phi\phi} = g_{\phi\phi}e^2+2 g_{t\phi}le+g_{tt}l^2\,
+g_{t\phi}^2-g_{tt}g_{\phi\phi} = g_{\phi\phi}e^2+2 g_{t\phi}le+g_{tt}l^2\ ,
 \end{equation}
@@
 which corresponds to Eq.~\eqref{eq:mb_ang_mom}.
-It is well-known that in black hole spacetimes there is an innermost circular marginally bound orbit for test particles.
+It is well-known that in BH spacetimes there is an innermost circular marginally bound orbit for test particles.
 Naturally, a marginally bound particle at the innermost circular orbit has to have the smallest possible value of the specific angular momentum (i.e.~a minimum of Eq.~\eqref{eq:bound_ang_mom}).

### 2018-11-26 paper_prd.tex
answer to Carlos and Eugen's comments

@@
 04.70.Bw, 
-04.40.Nr, 
+04.40.-b, 
 04.25.dg
+95.30.Qd
 }
@@
 For prograde motion, the function has a minimum outside the event horizon.
-The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
-\ch{The marginally bound orbit is not stable, right?
-So this is what is called the ICO, not ISCO, in the literature?} We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
+The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$ \sg{(also known as ICO (innermost circular orbit) in the literature)}, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
+We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
 
@@
 \\
-\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{-2 F_0} w (w-m W)}{N} - \mu^2\right) \phi^2.
+\rho_{\mathrm{SF}} &=&  2 \left(\frac{2 e^{-2 F_0} \omega (\omega-m W)}{N} - \mu^2\right) \phi^2.
 \end{eqnarray}
-\ch{Careful with $\omega$ vs. $w$. I think in these expressions should be $\omega$. Please check.}
+
 Using these expressions, we can compute the total gravitational mass of the torus and the scalar field as the following expression
@@
 \centering
-\includegraphics[scale=0.37]{figures/radial_log_rho_model_I.pdf}
+\includegraphics[scale=0.22]{figures/radial_log_rho_model_I.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.37]{figures/radial_log_rho_model_IV.pdf}
+\includegraphics[scale=0.22]{figures/radial_log_rho_model_IV.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.37]{figures/radial_log_rho_model_VII.pdf}
+\includegraphics[scale=0.22]{figures/radial_log_rho_model_VII.pdf}
 \hspace{-0.6cm}
@@
 \hspace{-0.6cm}
-\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
+\includegraphics[scale=0.22]{figures/log_radial_log_rho_I_ADM.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
+\includegraphics[scale=0.22]{figures/log_radial_log_rho_IV_ADM.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
+\includegraphics[scale=0.22]{figures/log_radial_log_rho_VII_ADM.pdf}
 \hspace{-0.6cm}
@@
 From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.
-Note that the scale shown in the horizontal axes is different in all plots.
-\ch{Please change the line style (one dotted, one dashed and one solid, in each plot, for clarity in black and white.
-The structure near the origin would be clearer if the r coordinate would be in a log plot.}}
+Note that the scale shown in the horizontal axes is different in all plots.}
 \label{radial_profiles}
@@
 From the discussion in the preceding section it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
+In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, \sg{the harmonic azimuthal index to $m = 1$}, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
 Thus, we leave the magnetization at the centre, $\beta_{\mathrm{m_c}}$, as the only free parameter for each model of KBHsSH.

### 2018-11-26 paper_prd.tex
Final version addressing Carlos and Eugen comments.

@@
 For prograde motion, the function has a minimum outside the event horizon.
-The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$ \sg{(also known as ICO (innermost circular orbit) in the literature)}, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
+The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$ (also known as ICO, innermost circular orbit, in the literature), and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point.
 We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.
@@
 From the discussion in the preceding section it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, \sg{the harmonic azimuthal index to $m = 1$}, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
+In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, the harmonic azimuthal index to $m = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
 Thus, we leave the magnetization at the centre, $\beta_{\mathrm{m_c}}$, as the only free parameter for each model of KBHsSH.

### 2018-11-26 paper_prd.tex
small typo

@@
 From the discussion in the preceding section it becomes apparent that the number of parameters defining the disk models is fairly large.
-In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, the harmonic azimuthal index to $m = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
+In order to reduce the sample, in this work we set the mass of the scalar field to $\mu = 1$, the  azimuthal harmonic index to $m = 1$, the exponents of the polytropic EOS to $q = \Gamma = 4/3$, the density at the centre of the disk to $\rho_{\mathrm{c}} = 1$, the specific angular momentum to $l = l_{\mathrm{mb}}$ and the inner radius of the disk to $r_{\mathrm{in}} = r_{\mathrm{mb}}$.
 Thus, we leave the magnetization at the centre, $\beta_{\mathrm{m_c}}$, as the only free parameter for each model of KBHsSH.

### 2018-11-28 paper_prd.tex
Polishing the source file (removing commented stuff).

@@
 
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
-%\hspace{-0.6cm}
-%\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
-%\hspace{-0.6cm}
-%\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
-%\hspace{-0.6cm}
-%\caption{Size of the disks.
-Effects of the magnetisation on the radial profiles of the logarithm of the density at the equatorial plane for different KBH models.
-From left to right we show three different cases with the same ADM quantities as the KBHsSH model I, IV, and VII, respectively.}
-%\label{radial_profiles_KBH}
-%\end{figure*}
-
 For the extremely magnetised case, we consider again Eq.~\eqref{eq:final} and Eq.~(20) of~\cite{Gimeno-Soler:2017}, but this time around we take $\beta_{\mathrm{m_c}} \rightarrow 0$ ($K \rightarrow 0$).
@@
 First of all, we compute the polytropic constant $K$ by evaluating Eq.~\eqref{eq:final} at the centre
-%\begin{equation}
 \begin{multline}
@@
 \end{multline}
-%\end{equation}
 where we have used the definition of magnetic pressure and the definition of the magnetization parameter $\beta$.
@@
 For points with $W(r, \theta) > 0$ we set $\rho = p = p_{\mathrm{m}} = 0$ and for points with $W_{\mathrm{c}} < W(r, \theta) < 0$, we write Eq.~\eqref{eq:final} as
-%\begin{equation}
 \begin{multline}
@@
 \end{multline}
-%\end{equation}
 to compute the rest-mass density $\rho$ of said point.
@@
 However, for the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$, and the quotient $R_{\mathrm{H}}/ 2M_{\mathrm{H}}$ increases as more mass and angular momentum is stored in the scalar field.
-%\sg{It is possible that the angular momentum does not change anything, but we cannot know, as we do not have two different models with the same value of the BH mass.} \tf{Any comment, Carlos?}
-
-%\sg{Discuss.
-I find that the 2D morphology in perimeteral coordinates might not be very useful, but I found an interesting property of these coordinates: For the Kerr metric, $R_{\mathrm{H}} = 2M$ irrespective of the value of the angular momentum (For the KBHsSH cases, $2M_{\mathrm{H}} < R_{\mathrm{H}} < 2M_{\mathrm{ADM}}$.
-I don't know if there are any kind of dependence on the angular momentum, as we don't two cases with the same value of the mass).
-I suppose this could help us to compare different models.
-In fact, the differences in the morphology close to the equatorial plane in the near horizon region are actually related to the value of the angular momentum (we can see a relationship between the morphological differences and the equivalent spin parameter $a_{\mathrm{eq}}$).} \tf{Could you please include some of this information in here?} \sg{Done}
 
@@
 In both cases, these values increase as $|\Delta W|$ increases, irrespective of the magnetization, as shown in Table~\ref{HBH_disk_parameters}.
-
-%\begin{figure*}
-%\centering
-%\includegraphics[scale=0.12]{figures/fig6_I_10.pdf}
-%\hspace{-0.4cm}
-%\includegraphics[scale=0.12]{figures/fig6_IV_10.pdf}
-%\hspace{-0.4cm}
-%\includegraphics[scale=0.12]{figures/fig6_VII_10.pdf}
-%\hspace{-0.2cm}
-%\\
-%\includegraphics[scale=0.12]{figures/fig6_I__10.pdf}
-%\hspace{-0.4cm}
-%\includegraphics[scale=0.12]{figures/fig6_IV__10.pdf}
-%\hspace{-0.4cm}
-%\includegraphics[scale=0.12]{figures/fig6_VII__10.pdf}
-%\hspace{-0.2cm}
-%\caption{Same as Fig.~\ref{comparison_mass_density} but using the perimeteral radial coordinate.
-\tf{Same comment as in the previous figure regarding the vertical range, in this case $[-1.5,1.5]$ for all models.} \sg{Done}}
-%\label{comparison_mass_density_peri}
-%\end{figure*}
 
@@
 \begin{appendix}
-% \section{Embedding of the accretion torus in $\mathbb{E}^3$}\label{torus_embedding}
-% Following the same reasoning as in~\cite{Delgado:2018}, we write the 2-metric for the surface of a torus as 
-% \begin{equation}\label{eq:torus_prev_metric}
-% \mathrm{d}\sigma^2 = \frac{e^{2 F_1}}{N}\mathrm{d}r^2+ e^{2 F_1}r^2\mathrm{d}\theta^2+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
-% \end{equation}
-% and the condition $r = r(\theta)$ for the surface of the torus.
-The location of the surface of the torus $r(\theta)$ can be obtained integrating $r' = \frac{\mathrm{d}r}{\mathrm{d}\theta} = -\frac{\partial_{\theta}W}{\partial_{r}W}$ (equation (24) of~\citep{Gimeno-Soler:2017}).
-Using this, we can write equation~\eqref{eq:torus_prev_metric} as
-% \begin{equation}\label{eq:torus_metric}
-% \mathrm{d}\sigma^2 = e^{2 F_1} \mathrm{d}\theta^2\left(\frac{r'^2}{N} +r^2\right)+e^{2 F_2} r^2 \sin^2\theta \mathrm{d}\phi^2,
-% \end{equation}
-% with the prime $'$ denoting partial differentiation with respect to $\theta$.
-Then, we try the embedding in $\mathbb{E}^3$ with the Cartesian metric $\mathrm{d}\sigma^2 = \mathrm{d}X^2 + \mathrm{d}Y^2 + \mathrm{d}Z^2$ and the embedding functions:
-% \begin{equation}
-% X + \mathrm{i}Y = f(\theta)e^{\mathrm{i}\phi},  \;\;\; Z = g(\theta),
-% \end{equation}
-% then
-% \begin{equation}
-% f = e^{2 F_2} r^2 \sin^2\theta, \;\;\; f'^2 + g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right),
-% \end{equation}
-% so we can write $g'^2$ as
-% \begin{equation}\label{eq:embedding_existance}
-% g'^2 = e^{2 F_1}\left(\frac{r'^2}{N} +r^2\right) - e^{2 F_2} (F_2'r \sin \theta + r' \sin \theta + r \cos \theta)^2.
-% \end{equation}
-% This result tells us that the r.h.s. of~\eqref{eq:embedding_existance} must be $\geq 0$ in order to the embedding function to exist.
-
-% \begin{figure*}
-% \centering
-% \includegraphics[scale=0.2]{figures/embedding.pdf}
-% \hspace{0.5cm}
-% \caption{Rest-mass density distribution for model VII with $r_{\mathrm{in}} = 0.08$ and $\beta_{\mathrm{m_c}} = 10^{10}$ (up) and the scalar field amplitude distribution $\phi$ (down).
-The isocontours are blue when the r.h.s.
-of equation~\eqref{eq:embedding_existance} is $> 0$ and red when is $\leq 0$.}
-% \label{embedding_VII}
-% \end{figure*}
 

### 2019-01-17 paper_revised.tex
added revised version

--- 2018-11-28 paper_prd.tex
@@
 \usepackage{units}
-\usepackage{slashbox}
 \usepackage{aas_macros}
@@
 Testing the true nature of black holes -- the no-hair hypothesis -- will become increasingly more precise in the next few years as new observational data is collected in both the gravitational wave channel and the electromagnetic channel.
-In this paper we consider numerically generated spacetimes of Kerr black holes with synchronised scalar hair and build stationary models of magnetized thick disks (or tori)  around them.
+In this paper we consider numerically generated spacetimes of Kerr black holes with synchronized scalar hair and build stationary models of magnetized thick disks (or tori) around them.
 Our approach assumes that the disks are not self-gravitating, they obey a polytropic equation of state, the distribution of their specific angular momentum is constant, and they are marginally stable, i.e.~the disks completely fill their Roche lobe.
@@
 Comparisons between the disk properties for both types of black holes are presented.
-The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
+The sequences of magnetized, equilibrium disks models discussed in this study \sg{are morphologically and thermodynamically different to their Kerr counterparts and we expect significant differences to appear when} used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
 \end{abstract}
@@
 In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and in modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein).
-Among those, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
+Among those, Kerr BHs with synchronized hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions.
 The physical conditions and stability properties of these classes of {\it hairy} BHs  (HBHs) have been recently investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.
@@
 \centering
-\includegraphics[scale=0.43]{figures/existence-new.pdf}
+\includegraphics[scale=0.43]{figures/1.pdf}
 \caption{Domain of existence for KBHsSH (shaded blue area) in an ADM mass versus scalar
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig1_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_I_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_I__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_II_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_II_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_II__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_III_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_III_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_III__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig1_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig1_IV_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig1_IV__10.pdf}
+\includegraphics[scale=0.14]{figures/2a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/2b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/2c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/2d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/2e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/2f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/2g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/2h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/2i.pdf}
+\\
+\includegraphics[scale=0.14]{figures/2j.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/2k.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/2l.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig2_V_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_V_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_V__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig2_VI_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_VI_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_VI__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig2_VII_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig2_VII_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig2_VII__10.pdf}
+\includegraphics[scale=0.14]{figures/3a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/3b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/3c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/3d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/3e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/3f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/3g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/3h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/3i.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.22]{figures/radial_log_rho_model_I.pdf}
+\includegraphics[scale=0.22]{figures/4a.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.22]{figures/radial_log_rho_model_IV.pdf}
+\includegraphics[scale=0.22]{figures/4b.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.22]{figures/radial_log_rho_model_VII.pdf}
+\includegraphics[scale=0.22]{figures/4c.pdf}
 \hspace{-0.6cm}
@@
 \hspace{-0.6cm}
-\includegraphics[scale=0.22]{figures/log_radial_log_rho_I_ADM.pdf}
+\includegraphics[scale=0.22]{figures/4d.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.22]{figures/log_radial_log_rho_IV_ADM.pdf}
+\includegraphics[scale=0.22]{figures/4e.pdf}
 \hspace{-0.6cm}
-\includegraphics[scale=0.22]{figures/log_radial_log_rho_VII_ADM.pdf}
+\includegraphics[scale=0.22]{figures/4f.pdf}
 \hspace{-0.6cm}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig3_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_I_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_I__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_II_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_II_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_II__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_III_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_III_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_III__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig3_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig3_IV_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig3_IV__10.pdf}
+\includegraphics[scale=0.14]{figures/5a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/5b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/5c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/5d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/5e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/5f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/5g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/5h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/5i.pdf}
+\\
+\includegraphics[scale=0.14]{figures/5j.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/5k.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/5l.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig4_V_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_V_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_V__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig4_VI_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_VI_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_VI__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig4_VII_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig4_VII_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig4_VII__10.pdf}
+\includegraphics[scale=0.14]{figures/6a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/6b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/6c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/6d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/6e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/6f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/6g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/6h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/6i.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.1267]{figures/fig5_I_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.1267]{figures/fig5_VII_10.pdf}
-\hspace{-0.2cm}
-\\
-\includegraphics[scale=0.1267]{figures/fig5_I__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.12]{figures/fig5_IV__10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.1267]{figures/fig5_VII__10.pdf}
+\includegraphics[scale=0.1267]{figures/7a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/7b.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.1267]{figures/7c.pdf}
+\hspace{-0.2cm}
+\\
+\includegraphics[scale=0.1267]{figures/7d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.12]{figures/7e.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.1267]{figures/7f.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig9_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig9_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig9_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig9_09999__10.pdf}
+\includegraphics[scale=0.14]{figures/8a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/8b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/8c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/8d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/8e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/8f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/8g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/8h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/8i.pdf}
+\\
+\includegraphics[scale=0.14]{figures/8j.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/8k.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/8l.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.14]{figures/fig10_0_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_0_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_0__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_05_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_05_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_05__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09__10.pdf}
-\\
-\includegraphics[scale=0.14]{figures/fig10_09999_10.pdf}
-\hspace{-0.3cm}
-\includegraphics[scale=0.14]{figures/fig10_09999_1.pdf}
-\hspace{-0.2cm}
-\includegraphics[scale=0.14]{figures/fig10_09999__10.pdf}
+\includegraphics[scale=0.14]{figures/9a.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/9b.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/9c.pdf}
+\\
+\includegraphics[scale=0.14]{figures/9d.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/9e.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/9f.pdf}
+\\
+\includegraphics[scale=0.14]{figures/9g.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/9h.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/9i.pdf}
+\\
+\includegraphics[scale=0.14]{figures/9j.pdf}
+\hspace{-0.3cm}
+\includegraphics[scale=0.14]{figures/9k.pdf}
+\hspace{-0.2cm}
+\includegraphics[scale=0.14]{figures/9l.pdf}
 \hspace{-0.2cm}
@@
 \centering
-\includegraphics[scale=0.2]{figures/fig7_HBH_dens.eps}
+\includegraphics[scale=0.2]{figures/10a.pdf}
 \hspace{-0.cm}
-\includegraphics[scale=0.2]{figures/fig7_HBH_enth.eps}
+\includegraphics[scale=0.2]{figures/10b.pdf}
 \hspace{-0.cm}
 \\
-\includegraphics[scale=0.2]{figures/fig7_Kerr_dens.eps}
+\includegraphics[scale=0.2]{figures/10c.pdf}
 \hspace{-0.cm}
-\includegraphics[scale=0.2]{figures/fig7_Kerr_enth.eps}
+\includegraphics[scale=0.2]{figures/10d.pdf}
 \hspace{-0.cm}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{figures/fig8_HBH.eps}
+\includegraphics[width=0.4\textwidth]{figures/11a.pdf}
 \hspace{0.5cm}
-\includegraphics[width=0.4\textwidth]{figures/fig8_Kerr.eps}
+\includegraphics[width=0.4\textwidth]{figures/11b.pdf}
 \hspace{0.5cm}
@@
 For all cases, the radial location of the magnetic pressure maximum decreases with decreasing $\beta_{\mathrm{m_c}}$.
-In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / \Gamma - 1=3$.
+In~\cite{Gimeno-Soler:2017} we proved that for $h=1$ disk models in stationary and axisymmetric BH spacetimes, the location of the maximum of the magnetic pressure is identical for all models when $\beta_{\mathrm{m_c}}\equiv 1 / (\Gamma - 1) = 3$.
 This condition is almost fulfilled for the Kerr BH case even when $h \neq 1$, with a very slight deviation for cases with very high spin parameter.
 This cannot be seen clearly in Fig.~\ref{comparison_HBH_Kerr_r_m_max} (even in the inset) but, as an example, for $a=0.9999$, the relative difference of $(R_{\mathrm{m, max}}-R_{\mathrm{c}})/R_{\mathrm{c}}$ with the $h=1$ case is about 0.1\%.
-(We note that in the radial coordinate of the metric ansatz, the disks are not so skewed and attached to the horizon and the differences would be more visible.) On the other hand, the condition $R_{\mathrm{m, max}}=R_{\mathrm{c}}$ when $\beta_{\mathrm{m_c}}= 3$ is clearly not fulfilled (when $h\neq 1$) for disks built around KBHsSH (see inset in the left panel).
+(We note that in the radial coordinate of the metric ansatz, the disks are not so skewed and attached to the horizon and the differences would be more visible.) On the other hand, the condition $R_{\mathrm{m, max}}=R_{\mathrm{c}}$ when $\beta_{\mathrm{m_c}}= 3$ is clearly not fulfilled (when $h \neq 1$) for disks built around KBHsSH (see inset in the left panel).
 At this point, it is relevant to remember that some of the KBHsSH models violate the Kerr bound in terms of the potential.
@@
 
-In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronised scalar hair and have built stationary models of magnetized tori around them.
+In this paper we have considered numerically generated spacetimes of Kerr BHs with synchronized scalar hair and have built stationary models of magnetized tori around them.
 Those disks are assumed to be non-self-gravitating, to obey a polytropic equation of state, and to be marginally stable, i.e.~the disks completely fill their Roche lobe.
@@
 The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and can be used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk (first attempted by~\cite{Vincent:2016}).
+\sg{In particular, the morphological and thermodynamical differences we observe when compararing these solutions with disks around Kerr BHs (i.e.~larger vertical size of the disks, a bigger high density central region and a more relativistic fluid) are expected to yield significantly different results when their shadows are computed.
+Moreover, the stability properties of such disks under perturbations are expected to be affected by the presence of the gravitational well produced by the scalar hair}.
 In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed.

### 2019-01-17 paper_revised.tex
Added Carlos' suggestion

@@
 Comparisons between the disk properties for both types of black holes are presented.
-The sequences of magnetized, equilibrium disks models discussed in this study \sg{are morphologically and thermodynamically different to their Kerr counterparts and we expect significant differences to appear when} used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
+The sequences of magnetized, equilibrium disks models discussed in this study \sg{are morphologically and thermodynamically diffferent - e.g., having a larger vertical size of the disks, a bigger high density central region and a more relativistic fluid - than their Kerr counterparts and we expect significant differences to appear when} used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
 \end{abstract}

### 2019-01-18 paper_revised.tex
Polishing the new text in the revised version.

--- 2019-01-17 paper_revised.tex
@@
 Comparisons between the disk properties for both types of black holes are presented.
-The sequences of magnetized, equilibrium disks models discussed in this study \sg{are morphologically and thermodynamically different to their Kerr counterparts and we expect significant differences to appear when} used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.
+{\bf The sequences of magnetized, equilibrium disks around Kerr black holes with scalar hair discussed in this study are morphologically and thermodynamically different than their Kerr black hole counterparts, namely their vertical size is larger, the high-density central region is more extended, and the fluid is more relativistic.
+Therefore, we expect significant differences to appear when these sequences are used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk.}
 \end{abstract}
@@
 The sequences of magnetized, equilibrium disks models discussed in this study can be used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and can be used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.~shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk (first attempted by~\cite{Vincent:2016}).
-\sg{In particular, the morphological and thermodynamical differences we observe when compararing these solutions with disks around Kerr BHs (i.e.~larger vertical size of the disks, a bigger high density central region and a more relativistic fluid) are expected to yield significantly different results when their shadows are computed.
+{\bf In particular, the morphological and thermodynamical differences we observe when comparing the solutions for KBHsSH with those for disks around Kerr BHs (i.e.~a larger vertical size of the disks, a more extended high-density central region, and a more relativistic fluid) are expected to yield significantly different results when their shadows are computed.
 Moreover, the stability properties of such disks under perturbations are expected to be affected by the presence of the gravitational well produced by the scalar hair}.

### 2019-01-18 referee_response.txt
first version of the response

Dear PRD Editor,

Thank you for sending us the report of the referee, whom we thank for
carefully reading our manuscript and providing very useful feedback. We 
have made changes addressing the issues raised in the report, 
which are listed below together with our response. The changes made in 
the manuscript are highlighted in boldface, to facilitate identification. 
We hope that with these amendments the paper will be considered 
acceptable for publication on Physical Review D.

       Best wishes,

       The authors

> ----------------------------------------------------------------------
> Report of the Referee -- DY12222/Gimeno-Soler
> ----------------------------------------------------------------------

> The paper describes an interesting and potentially important problem
> concerning the structure of accretion disks around exotic black holes
> modified by the presence of a gravitationally strong scalar field. The
> authors focus on the semi-analytic models of magneto-static tori,
> which under some conditions may capture properties of such disks, and
> build a grid of models exploring the parameter space. This is a
> meticulous work of good quality, which I am happy to recommend for
> publication in Physics.Rev.D.

> There is however one issue I would like the authors to address. The
> first question one would expect to be answered in such a paper is how
> strong, robust and unmistakable the effects attributable to the scalar
> field are. Is there a smoking gun, so to speak? Unfortunately the
> authors avoid addressing this question both in the Abstract and in the
> Conclusions, which is rather puzzling.

We agree with the referee about this questions, and therefore we have added this paragraph to the abstract:

"The sequences of magnetized, equilibrium disks around Kerr black holes with scalar hair discussed in this study are morphologically and thermodynam- ically different than their Kerr black hole counterparts, namely their vertical size is larger, the high-density central region is more extended, and the fluid is more relativistic. Therefore, we expect significant differences to appear when these sequences are used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e. shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk."

and this piece of text in the conclusions:

"In particular, the morphological and thermodynamical differences we observe when comparing the solutions for KBHsSH with those for disks around Kerr BHs (i.e. a larger vertical size of the disks, a more extended high-density central region, and a more relativistic fluid) are expected to yield significantly different results when their shadows are computed. Moreover, the stability properties of such disks under perturbations are expected to be affected by the presence of the gravitational well produced by the scalar hair."

### 2019-01-18 referee_response.txt
Final version of the response to the referee.

@@
 Thank you for sending us the report of the referee, whom we thank for
-carefully reading our manuscript and providing very useful feedback. We 
-have made changes addressing the issues raised in the report, 
-which are listed below together with our response. The changes made in 
+carefully reading our manuscript and recommending publication. Following 
+the recommendation of the referee, we have made a few changes in the 
+abstract and in the conclusions to address his/her request to point 
+out the effects attributable to the scalar field. The changes made in 
 the manuscript are highlighted in boldface, to facilitate identification.
-We hope that with these amendments the paper will be considered 
-acceptable for publication on Physical Review D.
 
@@
 
-We agree with the referee about this questions, and therefore we have added this paragraph to the abstract:
+We agree with the referee and therefore we have added the following 
+text to the abstract and conclusions:
 
-"The sequences of magnetized, equilibrium disks around Kerr black holes with scalar hair discussed in this study are morphologically and thermodynam- ically different than their Kerr black hole counterparts, namely their vertical size is larger, the high-density central region is more extended, and the fluid is more relativistic.
-Therefore, we expect significant differences to appear when these sequences are used as initial data for numerical relativity codes to investigate their dynamical (non-linear) stability and used in tandem with ray-tracing codes to obtain synthetic images of black holes (i.e.
-shadows) in astrophysically relevant situations where the light source is provided by an emitting accretion disk."
+Abstract:
 
-and this piece of text in the conclusions:
+"The sequences of magnetized, equilibrium disks around Kerr black holes 
+with scalar hair discussed in this study are morphologically and 
+thermodynamically different than their Kerr black hole counterparts, 
+namely their vertical size is larger, the high-density central region 
+is more extended, and the fluid is more relativistic. Therefore, we 
+expect significant differences to appear when these sequences are 
+used as initial data for numerical relativity codes to investigate 
+their dynamical (non-linear) stability and used in tandem with 
+ray-tracing codes to obtain synthetic images of black holes (i.e. 
+shadows) in astrophysically relevant situations where the light 
+source is provided by an emitting accretion disk."
 
-"In particular, the morphological and thermodynamical differences we observe when comparing the solutions for KBHsSH with those for disks around Kerr BHs (i.e.
-a larger vertical size of the disks, a more extended high-density central region, and a more relativistic fluid) are expected to yield significantly different results when their shadows are computed.
-Moreover, the stability properties of such disks under perturbations are expected to be affected by the presence of the gravitational well produced by the scalar hair."
+Conclusions:
+
+"In particular, the morphological and thermodynamical differences we 
+observe when comparing the solutions for KBHsSH with those for disks 
+around Kerr BHs (i.e. a larger vertical size of the disks, a more 
+extended high-density central region, and a more relativistic fluid) 
+are expected to yield significantly different results when their 
+shadows are computed. Moreover, the stability properties of such disks 
+under perturbations are expected to be affected by the presence of the 
+gravitational well produced by the scalar hair."
